### 2015-01-21 ms.tex
changing working title and adding @benmontet

%
%  RULES OF THE GAME
%
%  * 80 characters
%  * line breaks at the ends of sentences
%  * eqnarrys ONLY
%  * that is all.
%

\documentclass[12pt,preprint]{aastex}

\pdfoutput=1

\usepackage{color,hyperref}
\definecolor{linkcolor}{rgb}{0,0,0.5}
\hypersetup{colorlinks=true,linkcolor=linkcolor,citecolor=linkcolor,
            filecolor=linkcolor,urlcolor=linkcolor}
\usepackage{url}
\usepackage{amssymb,amsmath}
\usepackage{subfigure}

\newcommand{\project}[1]{\emph{#1}}
\newcommand{\kepler}{\project{Kepler}}
\newcommand{\KT}{\project{K2}}
\newcommand{\terra}{\project{TERRA}}
\newcommand{\license}{MIT License}
\newcommand{\projectname}{\project{KETU}}

\newcommand{\paper}{\textsl{Article}}

\newcommand{\foreign}[1]{\emph{#1}}
\newcommand{\etal}{\foreign{et\,al.}}
\newcommand{\etc}{\foreign{etc.}}
\newcommand{\True}{\foreign{True}}
\newcommand{\Truth}{\foreign{Truth}}

\newcommand{\figref}[1]{\ref{fig:#1}}
\newcommand{\Fig}[1]{Figure~\figref{#1}}
\newcommand{\fig}[1]{\Fig{#1}}
\newcommand{\figlabel}[1]{\label{fig:#1}}
\newcommand{\Tab}[1]{Table~\ref{tab:#1}}
\newcommand{\tab}[1]{\Tab{#1}}
\newcommand{\tablabel}[1]{\label{tab:#1}}
\newcommand{\Eq}[1]{Equation~(\ref{eq:#1})}
\newcommand{\eq}[1]{\Eq{#1}}
\newcommand{\eqalt}[1]{Equation~\ref{eq:#1}}
\newcommand{\eqlabel}[1]{\label{eq:#1}}
\newcommand{\Sect}[1]{Section~\ref{sect:#1}}
\newcommand{\sect}[1]{\Sect{#1}}
\newcommand{\sectalt}[1]{\ref{sect:#1}}
\newcommand{\App}[1]{Appendix~\ref{sect:#1}}
\newcommand{\app}[1]{\App{#1}}
\newcommand{\sectlabel}[1]{\label{sect:#1}}

\newcommand{\T}{\ensuremath{\mathrm{T}}}
\newcommand{\dd}{\ensuremath{\,\mathrm{d}}}
\newcommand{\bvec}[1]{{\ensuremath{\boldsymbol{#1}}}}
\newcommand{\appropto}{\mathrel{\vcenter{
  \offinterlineskip\halign{\hfil$##$\cr
    \propto\cr\noalign{\kern2pt}\sim\cr\noalign{\kern-2pt}}}}}
\newcommand{\densityunit}{{\ensuremath{\mathrm{nat}^{-2}}}}

% TO DOS
\newcommand{\todo}[3]{{\color{#2} \emph{#1} TODO: #3}}
\newcommand{\dfmtodo}[1]{\todo{DFM}{red}{#1}}
\newcommand{\hoggtodo}[1]{\todo{HOGG}{blue}{#1}}

\begin{document}

\title{%
    \projectname:
    A systematic search for transits in \KT\ data
}

\newcommand{\nyu}{2}
\newcommand{\caltech}{3}
\newcommand{\cfa}{4}
\newcommand{\mpia}{5}
\newcommand{\cds}{6}
\newcommand{\mpis}{7}
\author{%
    Daniel~Foreman-Mackey\altaffilmark{1,\nyu},
    Benjamin~T.~Montet\altaffilmark{\caltech,\cfa},
    David~W.~Hogg\altaffilmark{\nyu,\mpia,\cds},
    Bernhard~Sch\"olkopf\altaffilmark{\mpis},
    Dun~Wang\altaffilmark{\nyu},
    \etal
}
\altaffiltext{1}         {To whom correspondence should be addressed:
                          \url{danfm@nyu.edu}}
\altaffiltext{\nyu}      {Center for Cosmology and Particle Physics,
                          Department of Physics, New York University,
                          4 Washington Place, New York, NY, 10003, USA}
\altaffiltext{\caltech}  {California Institute of Technology, Pasadena, CA,
                          91125, USA}
\altaffiltext{\cfa}      {Harvard-Smithsonian Center for Astrophysics,
                          Cambridge, MA 02138, USA}
\altaffiltext{\mpia}     {Max-Planck-Institut f\"ur Astronomie,
                          K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\altaffiltext{\cds}      {Center for Data Science,
                          New York University,
                          4 Washington Place, New York, NY, 10003, USA}
\altaffiltext{\mpis}     {Max Planck Institute for Intelligent Systems
                          Spemannstrasse 38, 72076 T\"ubingen, Germany}

\begin{abstract}

The photometry from the \KT\ extension of NASA's \kepler\ mission is wrought
with systematic effects due to the relative imprecision of the telescope
pointing.
We present a method for searching these light curves by simultaneously
fitting for these systematics and the transit signals of interest.
This method is more computationally expensive than standard search algorithms
but we demonstrate that it can be efficiently implemented and used to
discover transit signals in the existing dataset.
We apply this method to the full Campaign 1 dataset and report a list of XXX
planet candidates transiting YYY stars.

\end{abstract}

\keywords{%
methods: data analysis
---
methods: statistical
---
catalogs
---
planetary systems
---
stars: statistics
}

\section{Introduction}

\section{Photometry}

The starting point for analysis is the raw pixel data.
We download the full set of XXX target pixel files for \KT's Campaign 1 from
MAST\footnote{\url{https://archive.stsci.edu/k2/}}.
Then, we extract photometry using fixed circular apertures of varying sizes
centered on the mean position of the brightest star (on average) in each
frame.
The centroids and initial flux estimates were measured using
\project{simplexy}, a component of the \project{Astrometry.net} pipeline
\citep{astrometry}.
For each time series, we used 20 circular apertures ranging in radius from 0.5
to 10 pixels and---following \citet{vanderberg-a}---chose the aperture size
that resulted in the smallest CDPP \dfmtodo{CITE CDPP} with a 6 hour
window.\footnote{Note that although we chose a specific aperture, photometry
for every aperture size is available online at \dfmtodo{some URL}.}

Most methods for analyzing \KT\ data---and \kepler\ data, for that
matter---involves some sort of pre-processing or ``de-trending'' step.
For example, \citet{vanderberg-a} measure the centroid motion for each star
and regress out any signal in their aperture photometry that can be fit by
this motion.
Similarly, \citet{crossfield} iteratively construct a robust Gaussian Process
model for the photometry as a function of the measured centroids and de-trend
using the mean prediction from that model.
In our analysis, we don't do any further preprocessing of the light curves
because, as we describe in the next section, we simultaneously fit for the
trends and the transit signals that we are searching for.

One key realization that is also exploited by the official \kepler\ pipeline
is that the systematic trends due to pointing shifts and other instrumental
effects are shared---with different signs and weights---by all the stars on
the detector.
To exploit this fact, the \project{PDC} component of the \kepler\ pipeline
removes any trends from the light curves that can be fit using a linear
combination of a small number of ``eigen-light curves'' (ELCs) found by
running Principal Component Analysis (PCA) on a set of light curves
\citep{map-pdc1, map-pdc2}.
Similarly, we ran PCA (as implemented by the \project{scikit-learn} project
\citealt{sklearn}) on the full set of Campaign 1 light curves to determine a
basis of representative ELCs.
We chose to keep the top 200 components---many more than are normally
used---for our model described in the following section.
\dfmtodo{do we want to plot some of these light curves here?}

\section{Joint transit \& variability model}

The key insight in our transit search method that sets it apart from the
other standard procedures is that no de-trending is necessary.
Instead, we can fit for the noise (or trends) and signal simultaneously.
This is theoretically appealing because it will be more sensitive to low
signal-to-noise transits.
The main reason for this is that the signal is not exactly orthogonal to the
systematics and the de-trending will over-fit causing the signal to be
distorted and weaker.
In order to reduce this effect, most procedures use a very rigid model for
the trends.
For \KT, this has been implemented by asserting that the centroids contain
all of the information needed to describe the trends.
In the \kepler\ pipeline, this is implemented by only allowing a small number
of PCA components to contribute to the fit.

Physically, the motivation for our model---and the PDC model---is that every
star on the detector should be affected by same set of systematic effects.
These are due to things like pointing jitter, temperature variations, and
other sources of PSF modulation and each one will be imprinted in the light
curves of many stars with varying amplitudes and signs.
Therefore, while it is hard to write down a physical generative model for the
systematics, building a data-driven model might be possible.
This intuition is also exploited by other methods that model the systematics
using only empirical centroids \citep{vanderberg-a, crossfield} but out more
flexible model should capture the systematic effects more robustly but there
is a risk of over-fitting.

To avoid over-fitting in our pipeline, we simultaneously fit for the transit
signal and the trends using a rigid model for the signal and a relatively
flexible model for the noise.
Specifically, we model the light curve as being generated by linear
combination of the 200 basis light curves and a ``box'' transit model at a
given period and phase.
Formally, this can be written for the light curve of the $k$-th star as
\begin{eqnarray}\eqlabel{linear-model}
\bvec{f}_k &=& \bvec{A}\,\bvec{w}_k + \mathrm{noise}
\end{eqnarray}
where
\begin{eqnarray}
\bvec{f}_k &=& \left (\begin{array}{cccc}
    f_{k,1} & f_{k,2} & \cdots & f_{k,N}
\end{array}\right )^\T
\end{eqnarray}
is the list aperture fluxes for star $k$ observed at $N$ times
\begin{eqnarray}
\bvec{t} &=& \left (\begin{array}{cccc}
    t_{1} & t_{2} & \cdots & t_{N}
\end{array}\right )^\T \quad.
\end{eqnarray}
In \eq{linear-model}, the design matrix is given by
\begin{eqnarray}
\bvec{A} &=& \left (\begin{array}{cccccc}
    x_{1,1} & x_{2,1} & \cdots & x_{J,1} & 1 & m_\bvec{\theta}(t_1) \\
    x_{1,2} & x_{2,2} & \cdots & x_{J,2} & 1 & m_\bvec{\theta}(t_2) \\
    && \vdots &&&\\
    x_{1,N} & x_{2,N} & \cdots & x_{J,N} & 1 & m_\bvec{\theta}(t_N)
\end{array}\right )
\end{eqnarray}
where the $x_{j,n}$ are the basis ELCs---with the index $j$ running over
components and the index $n$ running over time---and $m_\bvec{\theta}(t)$ is
the transit model
\begin{eqnarray}
m_\bvec{\theta}(t) &=& \left\{\begin{array}{cl}
-1 & \mathrm{if\,}t\,\mathrm{in\,transit} \\
0 & \mathrm{otherwise}
\end{array}\right.
\end{eqnarray}
parameterized by a period, phase, and transit duration (these parameters are
denoted by \bvec{\theta}).

Assuming that the uncertainties on $\bvec{f}_k$ are Gaussian and constant,
the maximum likelihood solution for \bvec{w} is
\begin{eqnarray}
{\bvec{w}_k}^* &\gets& \left( \bvec{A}^\T\,\bvec{A} \right)^{-1}\,
                       \bvec{A}^\T\,\bvec{f}_k
\end{eqnarray}
and the marginalized likelihood function for the transit depth is a Gaussian
with the mean given by the last element of ${\bvec{w}_k}^*$ and the variance
given by the lower-right element of the matrix
\begin{eqnarray}
{\bvec{\delta w}_k}^2 &\gets& {\sigma_k}^2 \,
            \left( \bvec{A}^\T\,\bvec{A} \right)^{-1}
\end{eqnarray}
where $\sigma_k$ is the uncertainty on $\bvec{f}_k$.
The amplitude of this Gaussian is given by
\begin{eqnarray}\eqlabel{depth-likelihood}
\mathcal{L}_k &=& \frac{1}{(2\,\pi\,{\sigma_k}^2)^{N/2}}\,\exp\left(
-\frac{1}{2\,{\sigma_k}^2}\,
\left| \bvec{f}_k - \bvec{A}\,{\bvec{w}_k}^* \right|^2
\right)
\end{eqnarray}
evaluated at the maximum likelihood value ${\bvec{w}_k}^*$.

Remember that the likelihood defined in \eq{depth-likelihood} is a function of
the parameters \bvec{\theta} (the period, phase, and duration of the planet).
In principle, this means that a transit search can proceed by building a dense
3D grid of \bvec{\theta} values and evaluating the likelihood of the data
$\mathcal{L}_k$ using \eq{depth-likelihood} at each point in the grid.

Then points in this space with likelihoods greater than some minimum value
could then be accepted as candidates for vetting.
This is similar (\dfmtodo{what is the exact comparison?}) to the standard
procedure of accepting candidates above some signal-to-noise threshold.
We find, however, that the procedure described in the following section is
much less sensitive to false alarms.

\section{Search pipeline}

\paragraph{Initial ``one-dimensional'' search}

\paragraph{Period \& phase search}

\paragraph{Machine vetting}

\paragraph{Hand vetting}

\section{Results}

\section{Discussion}

\acknowledgments
It is a pleasure to thank
\ldots\
for helpful contributions to the ideas and code presented here.
This project was partially supported by the NSF (grant AST-0908357), NASA
(grant NNX08AJ48G), and the Moore--Sloan Data Science Environment at NYU.
This research made use of the NASA \project{Astrophysics Data System}.

\newcommand{\arxiv}[1]{\href{http://arxiv.org/abs/#1}{arXiv:#1}}
\begin{thebibliography}{}\raggedright

\bibitem[Crossfield \etal(2015)]{crossfield}
Crossfield, I.~J.~M., Petigura, E., Schlieder, J., \etal\ 2015,
\arxiv{1501.03798}

\bibitem[Lang \etal(2010)]{astrometry}
Lang, D., Hogg, D.~W., Mierle, K., Blanton, M., \& Roweis, S.\ 2010, \aj, 139,
1782

\bibitem[Pedregosa \etal(2011)]{sklearn}
Pedregosa, F., Varoquaux, G., Gramfort, A., \etal\ 2011, JMLR, 12, 2825

\bibitem[Smith \etal(2012)]{map-pdc2}
Smith,~J.~C., Stumpe,~M.~C., Van Cleve,~J.~E., \etal\ 2012,
\pasp, 124, 1000

\bibitem[Stumpe \etal(2012)]{map-pdc1}
Stumpe,~M.~C., Smith,~J.~C., Van Cleve,~J.~E., \etal\ 2012,
\pasp, 124, 985

\bibitem[Vanderburg \& Johnson(2014a)]{vanderberg-a}
Vanderburg, A., \& Johnson, J.~A.\ 2014, \pasp, 126, 948

\bibitem[Vanderburg \etal(2014b)]{vanderburg-b}
Vanderburg, A., Montet, B.~T., Johnson, J.~A., \etal\ 2014, \arxiv{1412.5674}

\end{thebibliography}

\clearpage

% \begin{figure}[p]
% \begin{center}
% \includegraphics[width=\textwidth]{path/to/figure.pdf}
% \end{center}
% \caption{%
% A CAPTION.
% \figlabel{the-figure-label}}
% \end{figure}

\end{document}

### 2015-01-27 ms.tex
moving math to appendix

@@
 
-The photometry from the \KT\ extension of NASA's \kepler\ mission is wrought
-with systematic effects due to the relative imprecision of the telescope
-pointing.
-We present a method for searching these light curves by simultaneously
-fitting for these systematics and the transit signals of interest.
+The photometry from the \KT\ extension of NASA's \kepler\ mission is
+afflicted by systematic effects caused by the relative imprecision of the
+telescope pointing, and possibly other spacecraft effects.
+We present a method for searching these light curves for evidence of
+exoplanets by simultaneously fitting for these systematics and the
+transit signals of interest.
 This method is more computationally expensive than standard search algorithms
@@
 planet candidates transiting YYY stars.
+We also present a list of probably astrophysical false positives, and
+the results of some follow-up spectroscopic data on a few of the
+planet candidates
+The most interesting systems are JJJ and HHH.
 
@@
 One key realization that is also exploited by the official \kepler\ pipeline
-is that the systematic trends due to pointing shifts and other instrumental
+is that the systematic trends caused by pointing shifts and other instrumental
 effects are shared---with different signs and weights---by all the stars on
@@
 star on the detector should be affected by same set of systematic effects.
-These are due to things like pointing jitter, temperature variations, and
+These are caused by things like pointing jitter, temperature variations, and
 other sources of PSF modulation and each one will be imprinted in the light
@@
 given period and phase.
+
+Then points in this space with likelihoods greater than some minimum value
+could then be accepted as candidates for vetting.
+This is similar (\dfmtodo{what is the exact comparison?}) to the standard
+procedure of accepting candidates above some signal-to-noise threshold.
+We find, however, that the procedure described in the following section is
+much less sensitive to false alarms.
+
+\section{Search pipeline}
+
+\paragraph{Initial ``one-dimensional'' search}
+
+\paragraph{Period \& phase search}
+
+\paragraph{Machine vetting}
+
+\paragraph{Hand vetting}
+
+\section{Results}
+
+\section{Discussion}
+
+\acknowledgments
+It is a pleasure to thank
+\ldots\
+for helpful contributions to the ideas and code presented here.
+This project was partially supported by the NSF (grant AST-0908357), NASA
+(grant NNX08AJ48G), and the Moore--Sloan Data Science Environment at NYU.
+This research made use of the NASA \project{Astrophysics Data System}.
+
+\newcommand{\arxiv}[1]{\href{http://arxiv.org/abs/#1}{arXiv:#1}}
+\begin{thebibliography}{}\raggedright
+
+\bibitem[Crossfield \etal(2015)]{crossfield}
+Crossfield, I.~J.~M., Petigura, E., Schlieder, J., \etal\ 2015,
+\arxiv{1501.03798}
+
+\bibitem[Lang \etal(2010)]{astrometry}
+Lang, D., Hogg, D.~W., Mierle, K., Blanton, M., \& Roweis, S.\ 2010, \aj, 139,
+1782
+
+\bibitem[Pedregosa \etal(2011)]{sklearn}
+Pedregosa, F., Varoquaux, G., Gramfort, A., \etal\ 2011, JMLR, 12, 2825
+
+\bibitem[Smith \etal(2012)]{map-pdc2}
+Smith,~J.~C., Stumpe,~M.~C., Van Cleve,~J.~E., \etal\ 2012,
+\pasp, 124, 1000
+
+\bibitem[Stumpe \etal(2012)]{map-pdc1}
+Stumpe,~M.~C., Smith,~J.~C., Van Cleve,~J.~E., \etal\ 2012,
+\pasp, 124, 985
+
+\bibitem[Vanderburg \& Johnson(2014a)]{vanderberg-a}
+Vanderburg, A., \& Johnson, J.~A.\ 2014, \pasp, 126, 948
+
+\bibitem[Vanderburg \etal(2014b)]{vanderburg-b}
+Vanderburg, A., Montet, B.~T., Johnson, J.~A., \etal\ 2014, \arxiv{1412.5674}
+
+\end{thebibliography}
+
+\clearpage
+\appendix
+
+\section{Mathematical model}\sectlabel{math}
+
 Formally, this can be written for the light curve of the $k$-th star as
@@
 
-Then points in this space with likelihoods greater than some minimum value
-could then be accepted as candidates for vetting.
-This is similar (\dfmtodo{what is the exact comparison?}) to the standard
-procedure of accepting candidates above some signal-to-noise threshold.
-We find, however, that the procedure described in the following section is
-much less sensitive to false alarms.
-
-\section{Search pipeline}
-
-\paragraph{Initial ``one-dimensional'' search}
-
-\paragraph{Period \& phase search}
-
-\paragraph{Machine vetting}
-
-\paragraph{Hand vetting}
-
-\section{Results}
-
-\section{Discussion}
-
-\acknowledgments
-It is a pleasure to thank
-\ldots\
-for helpful contributions to the ideas and code presented here.
-This project was partially supported by the NSF (grant AST-0908357), NASA
-(grant NNX08AJ48G), and the Moore--Sloan Data Science Environment at NYU.
-This research made use of the NASA \project{Astrophysics Data System}.
-
-\newcommand{\arxiv}[1]{\href{http://arxiv.org/abs/#1}{arXiv:#1}}
-\begin{thebibliography}{}\raggedright
-
-\bibitem[Crossfield \etal(2015)]{crossfield}
-Crossfield, I.~J.~M., Petigura, E., Schlieder, J., \etal\ 2015,
-\arxiv{1501.03798}
-
-\bibitem[Lang \etal(2010)]{astrometry}
-Lang, D., Hogg, D.~W., Mierle, K., Blanton, M., \& Roweis, S.\ 2010, \aj, 139,
-1782
-
-\bibitem[Pedregosa \etal(2011)]{sklearn}
-Pedregosa, F., Varoquaux, G., Gramfort, A., \etal\ 2011, JMLR, 12, 2825
-
-\bibitem[Smith \etal(2012)]{map-pdc2}
-Smith,~J.~C., Stumpe,~M.~C., Van Cleve,~J.~E., \etal\ 2012,
-\pasp, 124, 1000
-
-\bibitem[Stumpe \etal(2012)]{map-pdc1}
-Stumpe,~M.~C., Smith,~J.~C., Van Cleve,~J.~E., \etal\ 2012,
-\pasp, 124, 985
-
-\bibitem[Vanderburg \& Johnson(2014a)]{vanderberg-a}
-Vanderburg, A., \& Johnson, J.~A.\ 2014, \pasp, 126, 948
-
-\bibitem[Vanderburg \etal(2014b)]{vanderburg-b}
-Vanderburg, A., Montet, B.~T., Johnson, J.~A., \etal\ 2014, \arxiv{1412.5674}
-
-\end{thebibliography}
-
 \clearpage

### 2015-01-27 ms.tex
nothing

@@
 basis of representative ELCs.
-We chose to keep the top 200 components---many more than are normally
+We chose to use the top 150 components---many more than are normally
 used---for our model described in the following section.
-\dfmtodo{do we want to plot some of these light curves here?}
+\Fig{pca} shows the top few ELCs.
 
@@
 is a risk of over-fitting.
+\Fig{corr} shows the application of this model to a light curve with no known
+transit signals.
 
@@
 Specifically, we model the light curve as being generated by linear
-combination of the 200 basis light curves and a ``box'' transit model at a
+combination of the 150 basis light curves and a ``box'' transit model at a
 given period and phase.
-
-Then points in this space with likelihoods greater than some minimum value
-could then be accepted as candidates for vetting.
-This is similar (\dfmtodo{what is the exact comparison?}) to the standard
-procedure of accepting candidates above some signal-to-noise threshold.
-We find, however, that the procedure described in the following section is
-much less sensitive to false alarms.
 
@@
 
-\paragraph{Initial ``one-dimensional'' search}
+In theory, search could proceed by evaluating the model described above on a
+fine grid three-dimensional grid in period, phase, and duration.
+In practice, this is computationally intractable for any grids of the
+required size.
+Instead, we can compute the values on this grid approximately, but at very
+high precision, using a two-step procedure that is much more computationally
+efficient.
+The first step, called the {\bf linear search}, involves hypothesizing a
+single transit on a two-dimensional grid in duration and transit time.
+The second step, the {\bf periodic search} uses a lookup table built on the
+results of the linear search to compute the likelihood for the periodic model.
+Finally, the peaks in the likelihood space are passed along for machine and
+hand vetting.
 
-\paragraph{Period \& phase search}
+\paragraph{Linear search}
+
+The linear search involves hypothesizing a transit signal on a
+two-dimensional grid in transit time and duration.
+For each point in the grid, we use the model described in the previous
+section to evaluate \emph{the likelihood function} of the transit depth.
+Because the model is linear, the likelihood function for the depth
+(marginalized over the model of the systematics) is a Gaussian:
+\begin{eqnarray}
+\ln \mathcal{L} (d) &\propto& \mathcal{N} ()
+\end{eqnarray}
+
+\paragraph{Periodic search}
 
@@
 
-% \begin{figure}[p]
-% \begin{center}
-% \includegraphics[width=\textwidth]{path/to/figure.pdf}
-% \end{center}
-% \caption{%
-% A CAPTION.
-% \figlabel{the-figure-label}}
-% \end{figure}
+\begin{figure}[p]
+\begin{center}
+\includegraphics{figures/pca.pdf}
+\end{center}
+\caption{%
+A CAPTION.
+\figlabel{pca}}
+\end{figure}
+
+\begin{figure}[p]
+\begin{center}
+\includegraphics{figures/corr.pdf}
+\end{center}
+\caption{%
+A CAPTION.
+\figlabel{corr}}
+\end{figure}
 

### 2015-01-28 ms.tex
CDS address
intro text

@@
 %  * eqnarrys ONLY
+%  * ``light curve'' not ``light-curve'' or ``lightcurve''
 %  * that is all.
@@
 
-\newcommand{\project}[1]{\emph{#1}}
+\newcommand{\project}[1]{\textsl{#1}} % hogg say
 \newcommand{\kepler}{\project{Kepler}}
 \newcommand{\KT}{\project{K2}}
+\newcommand{\tess}{\project{TESS}}
 \newcommand{\terra}{\project{TERRA}}
@@
                           New York University,
-                          4 Washington Place, New York, NY, 10003, USA}
+                          726 Broadway, 7th Floor, New York, NY, 10003, USA}
 \altaffiltext{\mpis}     {Max Planck Institute for Intelligent Systems
@@
 \section{Introduction}
+
+The \kepler\ Mission (cite something) has been incredibly succesful at
+finding periodic transits (eclipses) in the light curves (time-series
+photometry) of stars.
+Many of its most important discoveries are long-period planets that
+make transits with tiny amplitudes and short durations.
+The Mission has demonstrated that it is possible to routinely measure
+signals in stellar light curves at the part-in-$10^5$ level, at least
+for quiet and apparently bright stars.
+
+At this level of precision, many effects come in to play in a stellar
+light curve.
+Even in a space observatory like the \kepler\ Satellite, there are
+hardware and optics variations that affect simple photometric
+measurements at a level greater than part-in-$10^5$.
+One of the most serious of these is spacecraft pointing:
+If the detector flat-field is not known \emph{exquisitely}, then the
+tiny changes to the relative illumination of pixels caused by a star's
+motion in the focal plane (or caused by motion of the focal-plane
+boresight or orientation relative to the celestial sphere) will lead
+to changes in the measured or inferred brightness of the star.
+That is, good photometry relies on either a near-perfect flat-field
+and pointing model, or else data-analysis techniques that are
+insensitive to such variations.
+In this \paper\ we present an example of the latter---a
+data-analysis technique for exoplanet search and characterization that
+is insensitive to spacecraft-induced (or, in general,
+hardware-induced) trends in the light curves.
+
+The \KT\ Mission (cite something) is a follow-on to the primary
+\kepler\ Mission.
+The primary mission came to an end with the failure of a critical
+reaction wheel, rendering the spacecraft less able to maintain precise
+pointing.
+Because of the degraded spacecraft orientation systems, the new
+\KT\ data will in general exhibit far greater pointing
+variations---and far greater pointing-induced variations in
+photometry---than the original \kepler\ data.
+This makes good data-analysis techniques all the more valuable.
+
+...simultaneous fitting of systematics and transit signals is a way of
+searching for (and measuring) exoplanet signals independent of the
+systematics, provided that the systematics lie in the domain of the
+model.
+
+...we are not the first to search the \KT\ data (cite Crossfield, etc),
+and we build on ideas from \kepler\ searches (cite Petigura and
+\kepler).
+
+...The future is \tess (cite something); everything we do here is
+highly relevant to that important mission!
 

### 2015-01-28 ms.tex
outline text

@@
 
+...put in a warning here about \foreign{a priori} ``fit and subtract''
+or ``correction'' of light curves.  These methods are very sensitive
+to over-fitting in general, so either the investigator must
+artificially restrict the model freedom or else do clever
+data-censoring methods to avoid it (cite Dun AAS and in prep here).
+
+...DFM: DOES THIS METHOD MARGINALIZE OUT THE SYSTEMATICS?  (It could,
+right, because the mean and variance of the Gaussian likelihood are
+analytic (though maybe expensive).)  If we \emph{do} marginalize (or
+maybe either way), we need to emphasize here the difference between
+simultaneously \emph{estimating} the signal and the noise as opposed
+to simultaneously \emph{fitting} the signal and the noise and
+marginalization out of the latter.  Key idea: Don't come to a
+conclusion about (estimate) anything you don't care about, if you can
+possibly avoid it!
+
 ...we are not the first to search the \KT\ data (cite Crossfield, etc),
@@
 
-...The future is \tess (cite something); everything we do here is
+...our goals are to find new exoplanets, to generate targets for
+ground-based and space-based (JWST, even) follow-up, and to understand
+the full population of exoplanets.  We (as a community) have made
+progress on all these fronts, but there is much more to do.
+
+...The future is \tess\ (cite something); everything we do here is
 highly relevant to that important mission!

### 2015-01-29 ms.tex
a few more figures
adding smoe words abount linear and periodic search

@@
 \newcommand{\license}{MIT License}
-\newcommand{\projectname}{\project{KETU}}
+\newcommand{\projectname}{\project{ketu}}
 
@@
 
+% Notation for this paper.
+\newcommand{\flux}{{\ensuremath{f}}}
+\newcommand{\ferr}{{\ensuremath{\sigma_\flux}}}
+\newcommand{\attime}{{\ensuremath{t}}}
+\newcommand{\basis}{{\bvec{A}}}
+\newcommand{\weights}{{\bvec{w}}}
+
+\newcommand{\period}{{\ensuremath{P}}}
+\newcommand{\phase}{{\ensuremath{T^0}}}
+\newcommand{\duration}{{\ensuremath{D}}}
+\newcommand{\depth}{{\ensuremath{Z}}}
+\newcommand{\transittime}{{\ensuremath{T}}}
+
 \begin{document}
@@
 \title{%
-    \projectname:
-    A systematic search for transits in \KT\ data
+    A systematic search for transiting planets using \KT
 }
@@
 In theory, search could proceed by evaluating the model described above on a
-fine grid three-dimensional grid in period, phase, and duration.
+fine three-dimensional grid in period, phase, and duration.
 In practice, this is computationally intractable for any grids of the
@@
 efficient.
-The first step, called the {\bf linear search}, involves hypothesizing a
-single transit on a two-dimensional grid in duration and transit time.
-The second step, the {\bf periodic search} uses a lookup table built on the
-results of the linear search to compute the likelihood for the periodic model.
-Finally, the peaks in the likelihood space are passed along for machine and
-hand vetting.
+
+The specific quantity that we will be searching is the likelihood for the
+light curve of star $n$ given a set of transit parameters:
+\begin{eqnarray}
+p(\{\flux\}_n\,|\,\period,\,\phase,\,\duration,\,\depth) \quad.
+\end{eqnarray}
+We will make the simplifying assumption that each transit is independent
+because it will be approximately satisfied for all but the shortest periods
+and it leads to a huge computational advantage.
+Under this assumption, this likelihood function can be rewritten as
+\begin{eqnarray}\eqlabel{indtran}
+p(\{\flux\}_n\,|\,\period,\,\phase,\,\duration,\,\depth) &\approx&
+\prod_{m=1}^{M(\period,\,\phase)}
+    p(\{\flux\}_n\,|\,\transittime_m(\period,\,\phase),\,\duration,\,
+                    \depth)
+\end{eqnarray}
+where $\transittime_m(\period,\,\phase)$ is the time of the $m$-th
+transit given the period $\period$ and reference time $\phase$.
+\Eq{indtran} can be efficiently computed for many periods and phases if we
+first compute a set of likelihood functions for single transits on a fine grid
+in $\transittime_l$
+\begin{eqnarray}\eqlabel{singletransit}
+\left \{ p(\{\flux\}_n\,|\,\transittime_l,\,\duration_k,\,\depth)
+\right\}_{l=1,\,k=1}^{L,\,K}
+\end{eqnarray}
+then use these results as a lookup table.
+
+In the remainder of this section, we give more details about each step of the
+search procedure but in summary, it breaks into three main steps: linear
+search, periodic search, and vetting.
+In the {\bf linear search} step, we evaluate the likelihood function in
+\eq{singletransit} on a two-dimensional grid, coarse in transit duration
+$\duration_k$ and fine in transit time $\transittime_m$.
+Then in the {\bf periodic search} step, we use this two-dimensional grid to
+approximately evaluate the likelihood (\eqalt{indtran}) for a
+three-dimensional grid of periodic signals.
+Then, we run a peak detection algorithm on this grid that discards peaks that
+share transits with a shorter period candidate and signals with substantially
+varying transit depths.
+These transit candidates are then passed along for machine and human {\bf
+vetting}.
 
@@
 Because the model is linear, the likelihood function for the depth
-(marginalized over the model of the systematics) is a Gaussian:
-\begin{eqnarray}
-\ln \mathcal{L} (d) &\propto& \mathcal{N} ()
-\end{eqnarray}
+(marginalized over the model of the systematics) is a Gaussian with
+analytic amplitude $L$, mean $\bar{\depth}$, and variance
+$\delta\bar{\depth}^2$ derived in \app{math}.
+Therefore in the linear search, we save these three numbers for a
+two-dimensional grid in transit time \transittime\ and duration \duration.
+The transit time grid spans the duration of Campaign 1 with half hour spacing
+and we choose to only test three durations: 1.2, 2.4, and 4.8 hours.
+\Fig{linear} shows the mean transit depth $\bar{\depth}$ as a function of
+transit time \transittime\ for a light curve with an injected transit signal
+with transits at the times indicated by the vertical green bars.
+The computational complexity of this step is $\mathcal{O}(M\,K^3)$ where $M$
+is the number of points in the grid and $K$ is the number of data points.
 
 \paragraph{Periodic search}
+
+In the period search step, we use the lookup table generated by the linear
+search to compute the likelihood from \eq{indtran} on a three dimensional
+grid in period \period, reference time \phase, and duration \duration.
+At each point, we compute the likelihood of a model where the transit depth
+varies between transits and the ``correct'' simpler model where the transit
+depth is constant.
+The variable depth likelihood is simply the product of amplitudes from the
+initial search
+\begin{eqnarray}
+p_\mathrm{var}(\{\flux\}_n\,|\,\period,\,\phase,\,\duration) &=&
+\prod_{m=1}^{M(\period,\,\phase)} L_m \quad,
+\end{eqnarray}
+and the constant depth model is
+\begin{eqnarray}
+p_\mathrm{const}(\{\flux\}_n\,|\,\period,\,\phase,\,\duration) &=&
+\prod_{m=1}^{M(\period,\,\phase)}
+    \frac{L_m}{\sqrt{2\,\pi\,{\delta\bar{\depth}_m}^2}}\,\exp \left(
+        -\frac{[\depth - \bar{\depth}_m]^2}{2\,{\delta\bar{\depth}_m}^2}
+    \right)
+\end{eqnarray}
+where the maximum likelihood depth is
+\begin{eqnarray}
+\depth &=& {\sigma_\depth}^2\,\sum_{m=1}^{M(\period,\,\phase)}
+    \frac{\bar{\depth}_m}{{\delta\bar{\depth}_m}^2}
+\end{eqnarray}
+and
+\begin{eqnarray}
+\frac{1}{{\sigma_\depth}^2} &=& \sum_{m=1}^{M(\period,\,\phase)}
+    \frac{1}{{\delta\bar{\depth}_m}^2} \quad.
+\end{eqnarray}
 
@@
 \caption{%
-A CAPTION.
+The top 10 eigen light curves (ELCs) generated by running principal component
+analysis on all the aperture photometry from Campaign 1.
 \figlabel{pca}}
@@
 \caption{%
-A CAPTION.
+A demonstration of the ELC fit to the aperture photometry for EPIC 201374602.
+\emph{Top:} The black points show the aperture photometry and the green line
+is the maximum likelihood linear combination of ELCs.
+The estimated 6-hour precision of the raw photometry is 264 ppm.
+\emph{Bottom:} The points show the residuals of the data away from the ELC
+prediction.
+The 6-hour precision of this light curve is 31 ppm.
 \figlabel{corr}}
@@
 
+\begin{figure}[p]
+\begin{center}
+\includegraphics{figures/linear.pdf}
+\end{center}
+\caption{%
+The estimated transit depth as a function of transit time as computed in a
+linear search.
+This light curve has an injected signal with transits at the times indicated
+with green vertical lines.
+\figlabel{linear}}
+\end{figure}
+
+\begin{figure}[p]
+\begin{center}
+\includegraphics{figures/periodic.pdf}
+\end{center}
+\caption{%
+The periodogram for the same signal as in \fig{linear}.
+This plot was generated by the periodic search procedure.
+The true period is indicated by the vertical green line.
+\figlabel{periodic}}
+\end{figure}
+
+\begin{figure}[p]
+\begin{center}
+\includegraphics{figures/depth_s2n.pdf}
+\end{center}
+\caption{%
+The signal-to-noise of the transit depth as a function of period for the same
+signal as in \fig{periodic}.
+The correct injected period is indicated by the vertical green line.
+\figlabel{depth-s2n}}
+\end{figure}
+
 \end{document}

### 2015-02-02 ms.tex
a few words about model selection

@@
 
+\newcommand{\BIC}{{\ensuremath{\mathrm{BIC}}}}
+\newcommand{\TIC}{{\ensuremath{\mathrm{TIC}}}}
 \newcommand{\T}{\ensuremath{\mathrm{T}}}
@@
 \end{eqnarray}
-and
+and the uncertainty on this depth is given by
 \begin{eqnarray}
@@
 
+In general, the variable depth model will \emph{always} get a higher
+likelihood because it is more flexible.
+Therefore, to compare these two models, we use the Bayesian Information
+Criterion (BIC).
+The traditional definition of the BIC is
+\begin{eqnarray}
+-\frac{1}{2}\,\BIC_\cdot &=&
+    \ln p_\cdot(\{\flux\}_n\,|\,\period,\,\phase,\,\duration)
+    - \frac{J}{2} \ln N
+\end{eqnarray}
+where the likelihood function is maximized, $J$ is an estimate of the model
+complexity and $N$ is the effective sample size.
+To emphasize that $J$ and $N$ are tuning parameters of the method, we
+redefine the BIC as the TIC
+\begin{eqnarray}
+\TIC_\cdot &=&
+    \ln p_\cdot(\{\flux\}_n\,|\,\period,\,\phase,\,\duration) - \alpha
+\end{eqnarray}
+and we choose $\alpha$ heuristically.
+For the K2 Campaign 1 dataset, we find that $\alpha \sim 1250$ leads to robust
+recovery of injected signals while still being fairly insensitive to false
+signals.
+
+To limit memory consumption, in the periodic search, we actually profile (or
+maximize) over \phase\ subject to the constraint that $\TIC_\mathrm{const} >
+\TIC_\mathrm{var}$.
+
 \paragraph{Machine vetting}
+
+To generate an initial candidate list, we start by .
 

### 2015-02-05 ms.tex
Hand vetting notes

@@
 
+There are many instrumental or astrophysical effects that can mimic a transit
+signal in time series photometry.
+For the primary \kepler\ mission, the noise induced by instrumental artifacts
+on transit timescales was significantly smaller than transit depths for 
+all but the smallest planets.
+With \KT\ this is no longer the case.
+The motion of the instrument causes a drift in the pointing of approximately
+$1''$ per hour, causing variations in the flat field to dominate the 
+photometric signal.
+
+As a result, artifacts in the data induced by pointing jitter can ...
+
+If the properties of the noise in the data can be fully understood and 
+modeled, such artifacts can be separated from true astrophysical events.
+Our model, however, makes no assumptions about the properties of the noise
+other than that it is correlated across many stars on the detector.
+Therefore, our model can occassionally be fooled by instrumental artifacts
+that a more sophisticated method, or the human eye, can easily separate 
+from true astrophysical signals.
+
+To this end, we (euphamism for look at by eye) each system to identify the
+most promising candidates.
+
+\paragraph{False positives}
+
 \section{Results}

### 2015-02-05 ms.tex
False positive words

@@
 To this end, we (euphamism for look at by eye) each system to identify the
-most promising candidates.
+most promising, likely astrophysical signals.
 
-\paragraph{False positives}
+\paragraph{Astrophysical false positives}
+
+A major problem with any transit search is the potential confusion between
+transiting planets and eclipsing binaries.
+Ground-based surveys before \kepler\ often had a false-positive rate 
+of 30-40\%. (because of shit?)
+In the primary \kepler\ mission, this number was significantly lower:
+the false positive rate was only 5-10\% \citep{morton11}.
+Such improvement was enabled by the relatively small pixels, stable 
+pointing, and high precision of \kepler.
+In \kepler\ data, false positives can be reliably separated from 
+planet candidates by looking for differences in the position of the 
+centroid of light during transit events with respect to the 
+out-of-transit data (e.g. citation), variations in the depth of
+alternating transits (e.g. citation), and evidence for ellipsoidal
+variations between transits (e.g. citation).
+
+In \KT, we will not be able to rely on any of these techniques to
+characterize systems \textit{en masse}. 
+There are typically only a handful of transits, meaning differences
+between ``odd'' and ``even'' transits must be large to create
+a significant difference.
+Searching for ellipsoidal varaitions is hindered by the short time
+baseline and the increased photometric uncertainty in \KT\ data.
+Searching for centroid variations is also more difficult in \KT:
+to measure a centroid offset, one must know where the centroid is
+supposed to be.
+Predicting a centroid position is trivial with \kepler\ data due to the 
+remarkably stable pointing of the instrument. 
+With \KT\ this is only possible if one understands the pointing of the 
+spacecraft at a specific time.
+In theory, this is possible: the spacecraft is a rigid body, and by measuring
+the mean motion of stars across the detector over time, the 
+Euler angles can be inferred at all times.
+However, properly measuring positions of stars is a difficult problem:
+the centroid depends sensitively on the (unknown) flat field, which must
+be simultaneously inferred.
+Therefore, false positives caused by background eclipsing binaries which could
+be identified as such by \kepler\ data alone will be much more difficult to 
+distinguish in \KT\ data, making high-contrast adaptive optics images of 
+planet candidates an essential follow-up tool.
 

### 2015-02-05 ms.tex
discussion

@@
 
+\paragraph{Maybe this goes in results}
+
+We include posterior distributions of planet candidate properties, available at
+\dfmtodo{thisurl}. 
+These distributions are specifically \emph{NOT} marginalized over stellar 
+properties.
+In this work, we are agnostic about fundamental properties of the host star.
+In fact, the only assumptions we make are that the star targeted by the \KT\ 
+team is truly the planet host, and that there is no dilution by other stars in
+any aperture. 
+As a result, these posterior distributions reflect the maximum possible 
+uncertainty in parameters such as the planet radius which depend sensitively 
+on properties of the host star.
+
+To use our distributions to characterize individual systems, one
+
 \acknowledgments
@@
 (grant NNX08AJ48G), and the Moore--Sloan Data Science Environment at NYU.
+B.T.M. is supported by the National Science Foundation Graduate Research 
+Fellowship under Grant No. DGE‐1144469.
 This research made use of the NASA \project{Astrophysics Data System}.

### 2015-02-06 ms.tex
Words throughout.

@@
 Many of its most important discoveries are long-period planets that
-make transits with tiny amplitudes and short durations.
+make transits with tiny amplitudes and short durations relative to the
+planet's orbital period.
 The Mission has demonstrated that it is possible to routinely measure
@@
 
-The \KT\ Mission (cite something) is a follow-on to the primary
+The \KT\ Mission (cite something-Howell 14) is a follow-on to the primary
 \kepler\ Mission.
@@
 to 10 pixels and---following \citet{vanderberg-a}---chose the aperture size
-that resulted in the smallest CDPP \dfmtodo{CITE CDPP} with a 6 hour
+that resulted in the smallest CDPP \dfmtodo{CITE CDPP-Jessie Christiansen,
+Jon Jenkins, et al 2012} with a 6 hour
 window.\footnote{Note that although we chose a specific aperture, photometry
@@
 
-To use our distributions to characterize individual systems, one
+To use these distributions to characterize the properties of specific systems,
+one should weight our samples by inferred stellar properties.
 

### 2015-02-06 ms.tex
Working on intro

@@
 finding periodic transits (eclipses) in the light curves (time-series
-photometry) of stars.
-Many of its most important discoveries are long-period planets that
-make transits with tiny amplitudes and short durations relative to the
-planet's orbital period.
+photometry) of stars (cite something).
 The Mission has demonstrated that it is possible to routinely measure
-signals in stellar light curves at the part-in-$10^5$ level, at least
-for quiet and apparently bright stars.
+signals in stellar light curves at the part-in-$10^5$ level.
+Results from the primary mission include the detection of planet
+transits with depths as small as (XX) parts per million (cite Barclay).
 
-At this level of precision, many effects come in to play in a stellar
-light curve.
-Even in a space observatory like the \kepler\ Satellite, there are
-hardware and optics variations that affect simple photometric
-measurements at a level greater than part-in-$10^5$.
+The noise floor for \kepler\ data is often quoted as 15 parts per million per
+six hours of observations (cite someone- Gilliland 11?). 
+Although they generally do not influence the ability to search for transiting
+planets, larger systematic (noise shits) exist on different timescales. 
 One of the most serious of these is spacecraft pointing:
-If the detector flat-field is not known \emph{exquisitely}, then the
+If the detector flat-field is not known \emph{exquisitely}, then
 tiny changes to the relative illumination of pixels caused by a star's
@@
 to changes in the measured or inferred brightness of the star.
-That is, good photometry relies on either a near-perfect flat-field
-and pointing model, or else data-analysis techniques that are
+
+The pointing of \kepler\ was stable at the (LEVEL) level (citation) throughout
+the primary mission. 
+This primary mission came to an end with the failure of a critical
+reaction wheel, rendering the spacecraft less able to maintain precise
+pointing.
+The \KT\ Mission (cite something-Howell 14) is a follow-on to the primary
+\kepler\ Mission, observing approximately a dozen fields near the ecliptic
+plane, each for 75 days at a time.
+Because of the degraded spacecraft orientation systems, the new
+\KT\ data will in general exhibit far greater pointing
+variations---and far greater pointing-induced variations in
+photometry---than the original \kepler\ data.
+This makes good data-analysis techniques extremely valuable.
+
+Good photometry relies on either a near-perfect flat-field
+and pointing model or data-analysis techniques that are
 insensitive to such variations.
+The flat-field for \kepler\ was measured on the ground before the launch of 
+the spacecraft, but (blah blah it sucks for describing the FF now).
+Inference of the flat field is challenging because of the nature of the
+spacecraft's observations: point sources are observed with relatively limited
+spacecraft motion, and only a few percent of the data are actually stored and
+downloaded to Earth.
+Therefore, much of the effort in \KT\
+
 In this \paper\ we present an example of the latter---a
@@
 hardware-induced) trends in the light curves.
-
-The \KT\ Mission (cite something-Howell 14) is a follow-on to the primary
-\kepler\ Mission.
-The primary mission came to an end with the failure of a critical
-reaction wheel, rendering the spacecraft less able to maintain precise
-pointing.
-Because of the degraded spacecraft orientation systems, the new
-\KT\ data will in general exhibit far greater pointing
-variations---and far greater pointing-induced variations in
-photometry---than the original \kepler\ data.
-This makes good data-analysis techniques all the more valuable.
 

### 2015-02-06 ms.tex
adding tables and a few words about injections

--- 2015-02-06 ms.tex
@@
 \usepackage{subfigure}
+\usepackage{booktabs}
 
@@
 
+\section{Performance}
+
+To test the performance of our method, we conducted a suite of XXXX injection
+and recovery tests.
+For each test, we inject the signal from a realistic planetary system into the
+raw aperture photometry and passed it through the full pipeline.
+These synthetic systems have periods and radius ratios drawn uniformly in
+\dfmtodo{some range} and uniformly distributed impact parameters and phases.
+The eccentricities are drawn from a beta distribution with \dfmtodo{some
+parameters; cite Kipping} and the multiplicity is set to match the observed
+multiplicity distribution in the KOI catalog \dfmtodo{cite}.
+MA limb darkening, exposure time integration, etc.
+
+After running these light curves with injections through the full pipeline, if
+the resulting period and phase of the recovered signal were within YYYY of the
+true injected values, we deemed the injection a success.
+Figure ZZZZ shows the fraction of recovered signals as a function of the
+physical parameters of the injection and the magnitude of the star.
+As expected, the shallower transits at longer periods are recovered less
+robustly.
+
 \section{Results}
+
+\subsection{Planet candidates}
+
+\subsection{Probable binaries}
 
@@
 
+\begin{figure}[p]
+\begin{center}
+\includegraphics[width=\textwidth]{figures/completeness.pdf}
+\end{center}
+\caption{%
+\figlabel{completeness}}
+\end{figure}
+
+\begin{table}[p]
+\begin{center}
+\small
+\include{tab-cand}
+\end{center}
+\caption{%
+Candidates
+\tablabel{cand}}
+\end{table}
+
+\begin{table}[p]
+\begin{center}
+\include{tab-eb}
+\end{center}
+\caption{%
+Probable binaries.
+\tablabel{eb}}
+\end{table}
+
 \end{document}

### 2015-02-06 ms.tex
More intro

--- 2015-02-06 ms.tex
@@
 downloaded to Earth.
-Therefore, much of the effort in \KT\
+Therefore, much of the effort in \KT\ is focused on the potential of the latter.
 
-In this \paper\ we present an example of the latter---a
+Previous studies have developed methods to work with \KT\ data. 
+\citet{vanderburg-a} extract aperture photometry from the pixel data
+and decorrelate with image centroid position, producing light curves for each
+star that are ``corrected'' for the spacecraft motion. 
+These data have produced the first confirmed planet found with 
+\KT\ \citep{vanderburg-b}. 
+\citet{crossfield} iteratively construct a robust Gaussian Process
+model for the photometry as a function of the measured centroids and de-trend
+using the mean prediction from that model.
+
+In both of these cases, the authors follow a standard procedure when working 
+with \kepler\ data: ``correcting'' the light curve as a step before the search
+for transiting planets.
+Light curves from the primary \kepler\ mission are typically de-trended to
+remove the effects of stellar variability before searching for transiting 
+planets. 
+With \KT, the authors of each of these papers fit and subtract their measured
+effects from the spacecraft pointing variations and stellar variability.
+Such a technique can be extremely dangerous.
+Small signals, such as planet transits, can be partially absorbed into the 
+assumed-stellar signals, making each individual transit event appear 
+shallower.
+Small planets that should appear just above a specific signal-to-noise
+threshold could then be missed because of the de-trending.
+
+The alternative to this approach is to simultaneously fit both the systematics
+and the transit signals. 
+This method enables us to search for and measure exoplanet signals 
+independently of an estimate of the systematics, provided that the systematics
+lie in the domain of the model.
+The likelihood of the simultaneous fit of the systematics and transit signals
+to the data can then be compared to the likelihood of the fit of the systematics
+alone, reducing exoplanet ``search'' to a simple model comparison problem.
+
+In this \paper\ we present a
 data-analysis technique for exoplanet search and characterization that
@@
 
-...simultaneous fitting of systematics and transit signals is a way of
-searching for (and measuring) exoplanet signals independent of the
-systematics, provided that the systematics lie in the domain of the
-model.
-
-...put in a warning here about \foreign{a priori} ``fit and subtract''
-or ``correction'' of light curves.  These methods are very sensitive
-to over-fitting in general, so either the investigator must
-artificially restrict the model freedom or else do clever
-data-censoring methods to avoid it (cite Dun AAS and in prep here).
+(cite Dun AAS and in prep here).
 

### 2015-02-06 ms.tex
nothing really
words about posterior sampling

@@
 true injected values, we deemed the injection a success.
-Figure ZZZZ shows the fraction of recovered signals as a function of the
+\Fig{completeness} shows the fraction of recovered signals as a function of the
 physical parameters of the injection and the magnitude of the star.
@@
 
-\subsection{Planet candidates}
+After running the 21XXX light curves through our full pipeline, we end up
+with XXXX TCEs \dfmtodo{change this name} and after hand vetting, we are left
+with YYYY convincing transiting candidates.
+Of these candidates, ZZZ are probable binaries with obviously visible
+secondary eclipses and we list these candidates in Table \dfmtodo{SOMETABLE}.
+This leaves WWW planet candidates that are listed in Table
+\dfmtodo{SOMETABLE}.
 
-\subsection{Probable binaries}
+\paragraph{Posterior constraints on physical parameters}
+
+To fit for the observable parameters of the transit signals in detail, we use
+the same linear model for the systematics but then we combine this with a
+physical transit model (M\&A, etc.).
+Since this transit model is no longer linear, we use Markov Chain Monte Carlo
+(MCMC; cite emcee) to draw posterior samples from this model.
+At each step in the chain, we \emph{marginalize over the model of the
+systematics}.
+This means that we don't de-trend the data or make any hard decision about
+the actual value of the systematics.
+We sample the stellar density, limb-darkening coefficients, period, phase,
+radius ratio, impact parameter, eccentricity, and argument of periapsis.
+\dfmtodo{List priors.}
+The quantiles of these posterior samplings are given in table \dfmtodo{some
+table} and the full chains are available electronically \dfmtodo{some URL}.
 

### 2015-02-06 ms.tex
Introduction changes

--- 2015-02-06 ms.tex
@@
 hardware-induced) trends in the light curves.
+We assume the trends in the observed light curves in each star due to 
+spacecraft motion are shared by each star, and run PCA to measure the dominant
+modes.
+We then search for planets by modeling the data as a linear combination of
+these basis vectors and a transit model.
+Such a technique builds on the ideas of previous PCA-based \kepler\ planet 
+searches, such as those of (cite-Petigura).
+
+The methods developed within this paper are highly relevant to the upcoming 
+\tess\ mission (Cite-Ricker 14). 
+\tess will feature pointing precision of \sim 3 arcseconds (cite), 
+similar to the level of pointing drift with \KT.
+Moreover, the typical star will be only observed for one month at a time, and
+the typical transit detection will be at a similar signal-to-noise ratio as
+with \KT.
+
+Catalogs of transiting planets found by \KT\ will be important to better 
+understand the formation and evolution of planetary systems. 
+These planets, especially when they orbit especially bright or late-type stars,
+will be useful targets for ground-based and space-based follow-up, both for 
+current facilities and those planned in the near-future such as JWST.
+
+The \paper\ is organized as follows. 
+In \textsection\ref{sec:phot}, we describe our analysis of the photometric 
+data collected by \KT.
+In \textsection\ref{sec:model}, we expain our simultaneous fit of the 
+systematics and transit model.
+In \textsection\ref{sec:search}, we describe our search pipeline for 
+planet candidates.
+In \textsection\ref{sec:perform}, we quantify the performace of our pipeline 
+through the analysis of injected planetary signals.
+In \textsection\ref{sec:K2OIs}, we present the results of our search: 
+catalogs of \KT\ planet candidates and eclipsing binaries.
+In \textsection\ref{sec:discuss}, we discuss our results and outline our
+future work.
 
@@
 
-...we are not the first to search the \KT\ data (cite Crossfield, etc),
-and we build on ideas from \kepler\ searches (cite Petigura and
-\kepler).
-
-...our goals are to find new exoplanets, to generate targets for
-ground-based and space-based (JWST, even) follow-up, and to understand
-the full population of exoplanets.  We (as a community) have made
-progress on all these fronts, but there is much more to do.
-
-...The future is \tess\ (cite something); everything we do here is
-highly relevant to that important mission!
-
 \section{Photometry}
+\label{sec:phot}
 
@@
 \section{Joint transit \& variability model}
+\label{sec:model}
 
@@
 \section{Search pipeline}
+\label{sec:search}
 

### 2015-02-06 ms.tex
abstract tweaks

@@
 planet candidates transiting YYY stars.
-We also present a list of probably astrophysical false positives, and
-the results of some follow-up spectroscopic data on a few of the
-planet candidates
-The most interesting systems are JJJ and HHH.
+For all planet candidates, we present posterior distributions on the 
+properties of each system based strictly on the transit observables.
+We also present a list of ZZZ candidate eclipsing binary systems.
 

### 2015-02-06 ms.tex
centroid words

@@
 baseline and the increased photometric uncertainty in \KT\ data.
-Searching for centroid variations is also more difficult in \KT:
+Centroid variations are feasible in \KT\ but must be treated differently
+than in the original \kepler\ mission.
+In that data, centroid positions are measured for the data during and out of
+transit by coadding all the relevant frames in each quarter. 
+Such a technique is feasible due to the remarkably stable pointing of the
+instrument.
+Searching for centroid variations with this method is more difficult in \KT:
 to measure a centroid offset, one must know where the centroid is
 supposed to be.
-Predicting a centroid position is trivial with \kepler\ data due to the
-remarkably stable pointing of the instrument.
 With \KT\ this is only possible if one understands the pointing of the
@@
 be simultaneously inferred.
+
+While the traditional method to measure centroids is significantly more 
+challenging with \KT\ data, we have developed an alternative method
+to identify centroid offsets during transits in our data.
+
 Therefore, false positives caused by background eclipsing binaries which could

### 2015-02-06 ms.tex
more centroid words

@@
 to identify centroid offsets during transits in our data.
+In our data analysis, we model the systematics in the light curve
+caused by spacecraft motion, constrained by the ensemble of all stars in 
+the field of view.
+The same can be done with the positions of each star, instead of the flux, 
+as a function of time.
+In this case, for each candidate, we model the time series of centroid
+positions in each dimension as a linear combination of our PCA basis vectors
+plus a shift of unknown amplitude during transit events.
+Such a technique enables us to measure the centroid shift during transit and
+quantify an uncertainty of the size of this shift.
 
-Therefore, false positives caused by background eclipsing binaries which could
-be identified as such by \kepler\ data alone will be much more difficult to
-distinguish in \KT\ data, making high-contrast adaptive optics images of
-planet candidates an essential follow-up tool.
+%Therefore, false positives caused by background eclipsing binaries which could
+%be identified as such by \kepler\ data alone will be much more difficult to
+%distinguish in \KT\ data, making high-contrast adaptive optics images of
+%planet candidates an essential follow-up tool.
 

### 2015-02-07 ms.tex
Facilities tag in acknowledgements
more fixes
A few edits

--- 2015-02-06 ms.tex
@@
 \tess\ mission (Cite-Ricker 14).
-\tess will feature pointing precision of \sim 3 arcseconds (cite), 
+\tess will feature pointing precision of $\sim 3$ arcseconds (cite),
 similar to the level of pointing drift with \KT.
@@
 Then, we extract photometry using fixed circular apertures of varying sizes
-centered on the mean position of the brightest star (on average) in each
-frame.
-The centroids and initial flux estimates were measured using
-\project{simplexy}, a component of the \project{Astrometry.net} pipeline
-\citep{astrometry}.
-For each time series, we used 20 circular apertures ranging in radius from 0.5
-to 10 pixels and---following \citet{vanderberg-a}---chose the aperture size
-that resulted in the smallest CDPP \dfmtodo{CITE CDPP-Jessie Christiansen,
-Jon Jenkins, et al 2012} with a 6 hour
-window.\footnote{Note that although we chose a specific aperture, photometry
-for every aperture size is available online at \dfmtodo{some URL}.}
+centered on the predicted location of the target star based on the world
+coordinate system.
+For each time series, we used circular apertures ranging in radius from 0.5 to
+5 pixels (in steps of 0.5 pixels) and---following \citet{vanderberg-a}---chose
+the aperture size that resulted in the smallest CDPP \dfmtodo{CITE CDPP-Jessie
+Christiansen, Jon Jenkins, et al 2012} with a 6 hour window.\footnote{Note
+that although we chose a specific aperture, photometry for every aperture size
+is available online at \dfmtodo{some URL}.}
 
 Most methods for analyzing \KT\ data---and \kepler\ data, for that
-matter---involves some sort of pre-processing or ``de-trending'' step.
+matter---involve some sort of pre-processing or ``de-trending'' step.
 For example, \citet{vanderberg-a} measure the centroid motion for each star
@@
 the detector.
-To exploit this fact, the \project{PDC} component of the \kepler\ pipeline
+To make use of this, the \project{PDC} component of the \kepler\ pipeline
 removes any trends from the light curves that can be fit using a linear
@@
 \citep{map-pdc1, map-pdc2}.
-Similarly, we ran PCA (as implemented by the \project{scikit-learn} project
-\citealt{sklearn}) on the full set of Campaign 1 light curves to determine a
-basis of representative ELCs.
+Similarly, we ran PCA on the full set of Campaign 1 light curves to determine
+a basis of representative ELCs.
 We chose to use the top 150 components---many more than are normally

### 2015-02-07 ms.tex

@@
 \tess\ mission (Cite-Ricker 14).
-\tess will feature pointing precision of $\sim 3$ arcseconds (cite),
+\tess\ will feature pointing precision of \sim 3 arcseconds (cite),
 similar to the level of pointing drift with \KT.
@@
 baseline and the increased photometric uncertainty in \KT\ data.
-Searching for centroid variations is also more difficult in \KT:
+Centroid variations are feasible in \KT\ but must be treated differently
+than in the original \kepler\ mission.
+In that data, centroid positions are measured for the data during and out of
+transit by coadding all the relevant frames in each quarter.
+Such a technique is feasible due to the remarkably stable pointing of the
+instrument.
+Searching for centroid variations with this method is more difficult in \KT:
 to measure a centroid offset, one must know where the centroid is
 supposed to be.
-Predicting a centroid position is trivial with \kepler\ data due to the
-remarkably stable pointing of the instrument.
 With \KT\ this is only possible if one understands the pointing of the
@@
 be simultaneously inferred.
-Therefore, false positives caused by background eclipsing binaries which could
-be identified as such by \kepler\ data alone will be much more difficult to
-distinguish in \KT\ data, making high-contrast adaptive optics images of
-planet candidates an essential follow-up tool.
+
+While the traditional method to measure centroids is significantly more
+challenging with \KT\ data, we have developed an alternative method
+to identify centroid offsets during transits in our data.
+In our data analysis, we model the systematics in the light curve
+caused by spacecraft motion, constrained by the ensemble of all stars in
+the field of view.
+The same can be done with the positions of each star, instead of the flux,
+as a function of time.
+In this case, for each candidate, we model the time series of centroid
+positions in each dimension as a linear combination of our PCA basis vectors
+plus a shift of unknown amplitude during transit events.
+Such a technique enables us to measure the centroid shift during transit and
+quantify an uncertainty of the size of this shift.
+
+%Therefore, false positives caused by background eclipsing binaries which could
+%be identified as such by \kepler\ data alone will be much more difficult to
+%distinguish in \KT\ data, making high-contrast adaptive optics images of
+%planet candidates an essential follow-up tool.
 
@@
 This research made use of the NASA \project{Astrophysics Data System}.
+
+{\it Facilities:} \facility{Kepler}
 

### 2015-02-07 ms.tex
change author order

@@
     David~W.~Hogg\altaffilmark{\nyu,\mpia,\cds},
+    Dun~Wang\altaffilmark{\nyu},
     Bernhard~Sch\"olkopf\altaffilmark{\mpis},
-    Dun~Wang\altaffilmark{\nyu},
     \etal

### 2015-02-07 ms.tex
fixing \sim
switching to bibtex

@@
 \usepackage{booktabs}
+
+\usepackage{natbib}
+\bibliographystyle{apj}
 
@@
 Previous studies have developed methods to work with \KT\ data.
-\citet{vanderburg-a} extract aperture photometry from the pixel data
+\citet{Vanderburg:2014} extract aperture photometry from the pixel data
 and decorrelate with image centroid position, producing light curves for each
@@
 These data have produced the first confirmed planet found with
-\KT\ \citep{vanderburg-b}.
-\citet{crossfield} iteratively construct a robust Gaussian Process
+\KT\ \citep{Vanderburg:2015}.
+\citet{Crossfield:2015} iteratively construct a robust Gaussian Process
 model for the photometry as a function of the measured centroids and de-trend
@@
 \tess\ mission (Cite-Ricker 14).
-\tess\ will feature pointing precision of \sim 3 arcseconds (cite),
+\tess\ will feature pointing precision of $\sim 3$ arcseconds (cite),
 similar to the level of pointing drift with \KT.
@@
 For each time series, we used circular apertures ranging in radius from 0.5 to
-5 pixels (in steps of 0.5 pixels) and---following \citet{vanderberg-a}---chose
-the aperture size that resulted in the smallest CDPP \dfmtodo{CITE CDPP-Jessie
-Christiansen, Jon Jenkins, et al 2012} with a 6 hour window.\footnote{Note
-that although we chose a specific aperture, photometry for every aperture size
-is available online at \dfmtodo{some URL}.}
+5 pixels (in steps of 0.5 pixels) and---following
+\citet{Vanderburg:2014}---chose the aperture size that resulted in the
+smallest CDPP \citep{cdpp}
+with a 6 hour window.\footnote{Note that although we chose a specific
+aperture, photometry for every aperture size is available online at
+\dfmtodo{some URL}.}
 
@@
 matter---involve some sort of pre-processing or ``de-trending'' step.
-For example, \citet{vanderberg-a} measure the centroid motion for each star
+For example, \citet{Vanderburg:2014} measure the centroid motion for each star
 and regress out any signal in their aperture photometry that can be fit by
 this motion.
-Similarly, \citet{crossfield} iteratively construct a robust Gaussian Process
-model for the photometry as a function of the measured centroids and de-trend
-using the mean prediction from that model.
+Similarly, \citet{Crossfield:2015} iteratively construct a robust Gaussian
+Process model for the photometry as a function of the measured centroids and
+de-trend using the mean prediction from that model.
 In our analysis, we don't do any further preprocessing of the light curves
@@
 running Principal Component Analysis (PCA) on a set of light curves
-\citep{map-pdc1, map-pdc2}.
+\citep{pdc1, pdc2}.
 Similarly, we ran PCA on the full set of Campaign 1 light curves to determine
@@
 This intuition is also exploited by other methods that model the systematics
-using only empirical centroids \citep{vanderberg-a, crossfield} but out more
-flexible model should capture the systematic effects more robustly but there
-is a risk of over-fitting.
+using only empirical centroids \citep{Vanderburg:2014, Crossfield:2015} but
+out more flexible model should capture the systematic effects more robustly
+but there is a risk of over-fitting.
 \Fig{corr} shows the application of this model to a light curve with no known
@@
 In the primary \kepler\ mission, this number was significantly lower:
-the false positive rate was only 5-10\% \citep{morton11}.
+the false positive rate was only 5-10\% \citep{Morton:2011}.
 Such improvement was enabled by the relatively small pixels, stable
@@
 
-\newcommand{\arxiv}[1]{\href{http://arxiv.org/abs/#1}{arXiv:#1}}
-\begin{thebibliography}{}\raggedright
-
-\bibitem[Crossfield \etal(2015)]{crossfield}
-Crossfield, I.~J.~M., Petigura, E., Schlieder, J., \etal\ 2015,
-\arxiv{1501.03798}
-
-\bibitem[Lang \etal(2010)]{astrometry}
-Lang, D., Hogg, D.~W., Mierle, K., Blanton, M., \& Roweis, S.\ 2010, \aj, 139,
-1782
-
-\bibitem[Pedregosa \etal(2011)]{sklearn}
-Pedregosa, F., Varoquaux, G., Gramfort, A., \etal\ 2011, JMLR, 12, 2825
-
-\bibitem[Smith \etal(2012)]{map-pdc2}
-Smith,~J.~C., Stumpe,~M.~C., Van Cleve,~J.~E., \etal\ 2012,
-\pasp, 124, 1000
-
-\bibitem[Stumpe \etal(2012)]{map-pdc1}
-Stumpe,~M.~C., Smith,~J.~C., Van Cleve,~J.~E., \etal\ 2012,
-\pasp, 124, 985
-
-\bibitem[Vanderburg \& Johnson(2014a)]{vanderberg-a}
-Vanderburg, A., \& Johnson, J.~A.\ 2014, \pasp, 126, 948
-
-\bibitem[Vanderburg \etal(2014b)]{vanderburg-b}
-Vanderburg, A., Montet, B.~T., Johnson, J.~A., \etal\ 2014, \arxiv{1412.5674}
-
-\end{thebibliography}
+\bibliography{k2}
 

### 2015-02-07 ms.tex
Hogg hacking on the intro

@@
 %  * ``light curve'' not ``light-curve'' or ``lightcurve''
+%  * Do not put in any comments that might get tweeted by @OverheardOnAph
 %  * that is all.
@@
 photometry---than the original \kepler\ data.
-This makes good data-analysis techniques extremely valuable.
+This makes good data-analysis techniques even more valuable.
 
 Good photometry relies on either a near-perfect flat-field
-and pointing model or data-analysis techniques that are
+and pointing model or else data-analysis techniques that are
 insensitive to such variations.
 The flat-field for \kepler\ was measured on the ground before the launch of
-the spacecraft, but (blah blah it sucks for describing the FF now).
-Inference of the flat field is challenging because of the nature of the
-spacecraft's observations: point sources are observed with relatively limited
+the spacecraft, but is not nearly as accurate as required to make
+pointing-insensitive photometric measurements at the relevant level of precision.
+In principle direct inference of the flat-field might be possible;
+however, because point sources are observed with relatively limited
 spacecraft motion, and only a few percent of the data are actually stored and
-downloaded to Earth.
-Therefore, much of the effort in \KT\ is focused on the potential of the latter.
+downloaded to Earth, there isn't enough information in the data to derive or
+infer a highly accurate flat-field map.
+Therefore, work on \KT\ is sensibly focused on building data-analysis
+techniques that are pointing-insensitive.
 
-Previous studies have developed methods to work with \KT\ data.
+Previous projects have developed methods to work with \KT\ data.
 \citet{Vanderburg:2014} extract aperture photometry from the pixel data
@@
 using the mean prediction from that model.
+DFM HERE IS WHERE WE (cite Dun AAS and in prep).
 
-In both of these cases, the authors follow a standard procedure when working
-with \kepler\ data: ``correcting'' the light curve as a step before the search
-for transiting planets.
+In these light-curve processing methodologies,
+the authors follow a traditional procedure of ``correcting'' the light curve
+as a step that happens \emph{before} the search for transiting planets.
 Light curves from the primary \kepler\ mission are typically de-trended to
@@
 planets.
-With \KT, the authors of each of these papers fit and subtract their measured
+With \KT, application of the traditional methods involves fitting and subtracting measured
 effects from the spacecraft pointing variations and stellar variability.
-Such a technique can be extremely dangerous.
+Fit-and-subtract is dangerous:
 Small signals, such as planet transits, can be partially absorbed into the
-assumed-stellar signals, making each individual transit event appear
-shallower.
-Small planets that should appear just above a specific signal-to-noise
-threshold could then be missed because of the de-trending.
+best-fit stellar variability or systematics models, making each individual transit event appear
+shallower; that is, the traditional methods are prone to over-fitting.
+Because over-fitting will in general reduce the amplitude of true exoplanet signals,
+small planets that ought to appear just above any specific signal-to-noise
+or depth
+threshold could be missed because of the de-trending.
 
@@
 and the transit signals.
-This method enables us to search for and measure exoplanet signals
-independently of an estimate of the systematics, provided that the systematics
-lie in the domain of the model.
+Simultaneous fitting enables a search for---and measurement of---exoplanet signals
+to deliver results that are 
+independent of any implied estimate of the systematics, provided that the true
+systematics lie in the domain of the systematics model.
+DFM I WOULD SAY HERE \emph{WHY} SIMULTANEOUS FITTING LEADS TO INDEPENDENCE, AND WHAT DO YOU MEAN BY THAT?
 The likelihood of the simultaneous fit of the systematics and transit signals
@@
 alone, reducing exoplanet ``search'' to a simple model comparison problem.
+
+DFM:  HERE IS WHERE I WOULD TALK ABOUT MARGINALIZATION...DFM: DOES THIS METHOD MARGINALIZE OUT THE SYSTEMATICS?  (It could,
+right, because the mean and variance of the Gaussian likelihood are
+analytic (though maybe expensive).)  If we \emph{do} marginalize (or
+maybe either way), we need to emphasize here the difference between
+simultaneously \emph{estimating} the signal and the noise as opposed
+to simultaneously \emph{fitting} the signal and the noise and
+marginalization out of the latter.  Key idea: Don't come to a
+conclusion about (estimate) anything you don't care about, if you can
+possibly avoid it!
 
@@
 
-Catalogs of transiting planets found by \KT\ will be important to better
-understand the formation and evolution of planetary systems.
+Catalogs of transiting planets found in the \KT\ data will be important to better
+understand the physical properties, formation, and evolution of planetary systems.
 These planets, especially when they orbit especially bright or late-type stars,
@@
 current facilities and those planned in the near-future such as JWST.
+They will also deliver input data for next-generation population inferences (cite DFM),
+which in turn constrain population synthesis models.
 
@@
 future work.
-
-(cite Dun AAS and in prep here).
-
-...DFM: DOES THIS METHOD MARGINALIZE OUT THE SYSTEMATICS?  (It could,
-right, because the mean and variance of the Gaussian likelihood are
-analytic (though maybe expensive).)  If we \emph{do} marginalize (or
-maybe either way), we need to emphasize here the difference between
-simultaneously \emph{estimating} the signal and the noise as opposed
-to simultaneously \emph{fitting} the signal and the noise and
-marginalization out of the latter.  Key idea: Don't come to a
-conclusion about (estimate) anything you don't care about, if you can
-possibly avoid it!
 

### 2015-02-08 ms.tex
grant numbers; tense of acks

@@
 for helpful contributions to the ideas and code presented here.
-This project was partially supported by the NSF (grant AST-0908357), NASA
-(grant NNX08AJ48G), and the Moore--Sloan Data Science Environment at NYU.
-B.T.M. is supported by the National Science Foundation Graduate Research
-Fellowship under Grant No. DGE‐1144469.
+DFM, DWH, and DW were partially supported by the National Science Foundation (grant IIS-1124794),
+the National Aeronautics and Space Administration
+(grant NNX12AI50G), and the Moore--Sloan Data Science Environment at NYU.
+BTM was supported by a National Science Foundation Graduate Research
+Fellowship (grant DGE‐1144469).
 This research made use of the NASA \project{Astrophysics Data System}.

### 2015-02-08 ms.tex
Adding some references

@@
 Results from the primary mission include the detection of planet
-transits with depths as small as (XX) parts per million (cite Barclay).
+transits with depths as small as 12 parts per million \citep{Barclay:2013}.
 
 The noise floor for \kepler\ data is often quoted as 15 parts per million per
-six hours of observations (cite someone- Gilliland 11?).
+six hours of observations \citep{Gilliland:2011}.
 Although they generally do not influence the ability to search for transiting
@@
 pointing.
-The \KT\ Mission (cite something-Howell 14) is a follow-on to the primary
+The \KT\ Mission \citep{Howell:2014} is a follow-on to the primary
 \kepler\ Mission, observing approximately a dozen fields near the ecliptic
@@
 The methods developed within this paper are highly relevant to the upcoming
-\tess\ mission (Cite-Ricker 14).
+\tess\ mission \citep{Ricker:2014}.
 \tess\ will feature pointing precision of $\sim 3$ arcseconds (cite),

### 2015-02-08 ms.tex
notes for the discussion section

@@
 
-\paragraph{Maybe this goes in results}
+\paragraph{Maybe this goes in results} (Hogg say yes!)
 
@@
 
+The goal of this \paper\ was to get exoplanet candidates out of the \KT\ pixel-level data,
+it was not to generate light curves...
+the project does not really produce corrected light curves at all; why not?
+
+This is not the last time the \KT\ data will be searched...
+list some deficiencies of this search method
+(these might include approximations in the PHIC,
+the fact that it deals well with spacecraft systematics but not stellar variability,
+and that it isn't sensitive to single transits (which must be common)).
+
+The machine and hand vetting leave much to be desired...
+list some deficiencies of the vetting.
+
+Characterization of these candidates can be much improved...
+list the things we could know if we had follow-up observations of the stars.
+
 To use these distributions to characterize the properties of specific systems,
-one should weight our samples by inferred stellar properties.
+one should weight our samples by inferred stellar properties...
+Perhaps give a specific example here with some detailed discussion or math.
+
+The completeness and false-positive assessment could be vastly improved...
+completeness estimates are not as extensive as desired;
+there is essentially no estimate of the non-astrophysical false positive rate.
+
+We have not attempted to do any kind of populations analysis...
+but presumably \KT\ data will rock this.  In what ways?
 

### 2015-02-09 ms.tex
adding @timothydmorton to author list

@@
 %  * Do not put in any comments that might get tweeted by @OverheardOnAph
+%    (or maybe do put in a few....)
 %  * that is all.
@@
 \newcommand{\cds}{6}
-\newcommand{\mpis}{7}
+\newcommand{\princeton}{7}
+\newcommand{\mpis}{8}
 \author{%
@@
     David~W.~Hogg\altaffilmark{\nyu,\mpia,\cds},
+    Timothy~D.~Morton\altaffilmark{\princeton},
     Dun~Wang\altaffilmark{\nyu},
@@
                           726 Broadway, 7th Floor, New York, NY, 10003, USA}
+\altaffiltext{\princeton}{Department of Astrophysics, Princeton University,
+                          Princeton, NJ, 08544, USA}
 \altaffiltext{\mpis}     {Max Planck Institute for Intelligent Systems

### 2015-02-11 ms.tex
a few words about false positives

@@
 
-In \KT, we will not be able to rely on any of these techniques to
-characterize systems \textit{en masse}.
-There are typically only a handful of transits, meaning differences
-between ``odd'' and ``even'' transits must be large to create
-a significant difference.
-Searching for ellipsoidal varaitions is hindered by the short time
-baseline and the increased photometric uncertainty in \KT\ data.
-Centroid variations are feasible in \KT\ but must be treated differently
-than in the original \kepler\ mission.
+In \KT, the precision of these tests is lower and they must be applied with
+care.
+There are typically only a handful of transits, meaning differences between
+``odd'' and ``even'' transits must be large to create a significant
+difference.
+Searching for ellipsoidal varaitions is hindered by the short time baseline
+and the increased photometric uncertainty in \KT\ data.
+Centroid variations are feasible in \KT\ but must be treated differently than
+in the original \kepler\ mission where this effect was generally measured
+using difference imaging (cite Howell).
+
+To obtain an initial assessment of the astrophysical false positive rate in
+our catalog of planet candidates, we test for centroid offsets and variable
+depth transits using the machinery that we have already established for
+modeling the systematic trends in the data.
+This is only the first word and a more complete characterization of our
+catalog's reliability is forthcoming (Montet, Foreman-Mackey, \etal\ in prep).
+
+To measure \emph{centroid offsets}, we start by empirically measuring the
+pixel centroid time series for each candidate by modeling the pixels near the
+peak as a two-dimensional quadratic and finding the maximum at each time.
+This method has been shown to produce higher precision centroid measurements
+than center-of-light estimates (@HOGG: is this true? Is there a citation? MJ
+in prep?).
+Figure SOMEFIGURE shows the measure $x$ and $y$ pixel coordinate traces for
+SOMECANDIDATE.
+Much like the photometry, this signal is dominated by the rigid body motion
+of the spacecraft and we can, in fact, model it identically.
+Previously (SOMEEQUATION), we modeled the light curve as a linear combination
+of ELCs and a simple box transit model at a given period, phase, and duration.
+Under this model, the maximum likelihood depth can be computed analytically.
+If we apply \emph{exactly the same model} to the centroid trace, the ``depth''
+that we compute becomes the centroid motion in transit in units of pixels.
+
 In that data, centroid positions are measured for the data during and out of

### 2015-02-11 ms.tex
more words about FPs

@@
 that we compute becomes the centroid motion in transit in units of pixels.
+Since the motions won't necessarily point in a consistent direction across
+transits, we treat each transit independently and report the average offset
+amplitude weighted by the precision of each measurement.
+To compute the significance of a centroid offset, we bootstrap the offset
+amplitude for models at the same period and duration but randomly oriented
+phases.
+If the centroid measured for the candidate transit is substantially larger
+(by SOMEAMOUNT) than the random realizations, then the candidate is labeled
+as a false positive.
+Figure SOMEFIGURE shows the distribution of centroid offsets across our
+catalog and YYYY---or ZZZZ\%---of our candidates fail this test.
 
-In that data, centroid positions are measured for the data during and out of
-transit by coadding all the relevant frames in each quarter.
-Such a technique is feasible due to the remarkably stable pointing of the
-instrument.
-Searching for centroid variations with this method is more difficult in \KT:
-to measure a centroid offset, one must know where the centroid is
-supposed to be.
-With \KT\ this is only possible if one understands the pointing of the
-spacecraft at a specific time.
-In theory, this is possible: the spacecraft is a rigid body, and by measuring
-the mean motion of stars across the detector over time, the
-Euler angles can be inferred at all times.
-However, properly measuring positions of stars is a difficult problem:
-the centroid depends sensitively on the (unknown) flat field, which must
-be simultaneously inferred.
+We also test the consistency \emph{between even and odd transit depths} for
+each of our candidates.
+As described in SOMESECTION, our method for transit search automatically
+rejects signals with wildly varying depths but.
 
-While the traditional method to measure centroids is significantly more
-challenging with \KT\ data, we have developed an alternative method
-to identify centroid offsets during transits in our data.
-In our data analysis, we model the systematics in the light curve
-caused by spacecraft motion, constrained by the ensemble of all stars in
-the field of view.
-The same can be done with the positions of each star, instead of the flux,
-as a function of time.
-In this case, for each candidate, we model the time series of centroid
-positions in each dimension as a linear combination of our PCA basis vectors
-plus a shift of unknown amplitude during transit events.
-Such a technique enables us to measure the centroid shift during transit and
-quantify an uncertainty of the size of this shift.
-
-%Therefore, false positives caused by background eclipsing binaries which could
-%be identified as such by \kepler\ data alone will be much more difficult to
-%distinguish in \KT\ data, making high-contrast adaptive optics images of
-%planet candidates an essential follow-up tool.
+Blah blah blah.
+Therefore, false positives caused by background eclipsing binaries which could
+be identified as such by \kepler\ data alone will be much more difficult to
+distinguish in \KT\ data, making high-contrast adaptive optics images of
+planet candidates an essential follow-up tool.
 

### 2015-02-12 ms.tex
words about vetting

@@
 
-\paragraph{Machine vetting}
+\dfmtodo{Iterative search.}
 
-To generate an initial candidate list, we start by .
+\paragraph{Initial candidate list}
+
+To generate an initial candidate list, we estimate the signal-to-noise of
+each candidate in the \TIC\ periodogram by comparing the peak height to a
+robust estimate of variance in \TIC\ values across period.
+A cut in this quantity can reject most variable stars and low
+signal-to-noise candidates that can't be reliably recovered from the data.
+Figure SOMEFIGURE shows the distribution of signal-to-noise for a set of
+injections and compares it to the distribution of false candidates that are
+proposed by the pipeline.
+To minimize contamination from false alarms but maximize our sensitivity, we
+choose a threshold of 15 \dfmtodo{right number?}.
+We also find that the signals with periods $\lesssim 4$ days are very
+contaminated by false alarms.
+This might be due to the fact that our independence assumption (SOMEEQUATION)
+breaks down at these short periods.
+Therefore, we discard all signals with periods shorter than 4 days.
+After these cuts, we're left with 700 \dfmtodo{right number?} candidates that
+we then examine by hand.
+The full list of peaks and their relevant meta data is available online at
+\dfmtodo{SOMEURL}.
 
@@
 
-There are many instrumental or astrophysical effects that can mimic a transit
-signal in time series photometry.
-For the primary \kepler\ mission, the noise induced by instrumental artifacts
-on transit timescales was significantly smaller than transit depths for
-all but the smallest planets.
-With \KT\ this is no longer the case.
-The motion of the instrument causes a drift in the pointing of approximately
-$1''$ per hour, causing variations in the flat field to dominate the
-photometric signal.
+After our initial cuts on the candidate list, the majority of signals are
+still false alarms mostly due to variable stars or single outlying data
+points.
+It should be possible to construct a more robust machine vetting algorithm
+that discards these samples without missing real transits (CITE SOME THINGS)
+but for the purposes of this \paper, we simply inspect the light curve for
+each of the YYYY candidates \emph{by hand} to discard signals that are not
+convincing transits.
+The results of this vetting can be seen online at SOMEURL.
 
-As a result, artifacts in the data induced by pointing jitter can ...
-
-If the properties of the noise in the data can be fully understood and
-modeled, such artifacts can be separated from true astrophysical events.
-Our model, however, makes no assumptions about the properties of the noise
-other than that it is correlated across many stars on the detector.
-Therefore, our model can occassionally be fooled by instrumental artifacts
-that a more sophisticated method, or the human eye, can easily separate
-from true astrophysical signals.
-
-To this end, we (euphamism for look at by eye) each system to identify the
-most promising, likely astrophysical signals.
+This vetting resulted in a list of ZZZZ transiting candidates.
+Many of these signals are due to astrophysical ``false positives'' like
+eclipsing binaries or blending.
+We address this effect in the following section and separate the list of
+candidates into a list of astrophysical false positives and planet candidates.
 

### 2015-02-12 ms.tex
iterative search

@@
 where the maximum likelihood depth is
-\begin{eqnarray}
+\begin{eqnarray}\eqlabel{periodic-depth}
 \depth &=& {\sigma_\depth}^2\,\sum_{m=1}^{M(\period,\,\phase)}
@@
 and the uncertainty on this depth is given by
-\begin{eqnarray}
+\begin{eqnarray}\eqlabel{periodic-depth-uncert}
 \frac{1}{{\sigma_\depth}^2} &=& \sum_{m=1}^{M(\period,\,\phase)}
@@
 To limit memory consumption, in the periodic search, we actually profile (or
-maximize) over \phase\ subject to the constraint that $\TIC_\mathrm{const} >
-\TIC_\mathrm{var}$.
+maximize) over \phase\ and \duration\ subject to the constraint that
+$\TIC_\mathrm{const} > \TIC_\mathrm{var}$.
+This results in a one-dimensional ``periodogram'' measuring the quality of
+the fit as a function of period.
+To choose the ``best'' candidate signal, we found that the best quantity to
+select on was the signal-to-noise with which the depth was measured at a
+given period, $\depth/\sigma_\depth$, computed using
+Equations~(\ref{eq:periodic-depth}) and (\ref{eq:periodic-depth-uncert}).
+Figure SOMEFIGURE shows the signal-to-noise of the depth measurement as a
+function of period for SOMECANDIDATE.
 
-\dfmtodo{Iterative search.}
+After selecting the best candidate based on the signal-to-noise of the depth,
+we mask out the sections of the linear search corresponding to these transits
+and iterate the periodic search.
+Under our assumption of independent transits, this is equivalent to removing
+the sections of data that have a transit caused by the highest peak.
+For the purposes of this \paper, we iterate the periodic search until we find
+three peaks for each light curve.
+This will necessarily miss the smallest and longest period planets in systems
+with more than three transiting planets but given the precision---or lack
+thereof---of the current method, we deemed this number sufficient.
 
@@
 
-To generate an initial candidate list, we estimate the signal-to-noise of
-each candidate in the \TIC\ periodogram by comparing the peak height to a
-robust estimate of variance in \TIC\ values across period.
-A cut in this quantity can reject most variable stars and low
-signal-to-noise candidates that can't be reliably recovered from the data.
+The periodic search procedure returned three signals per target so this gave
+an initial list of ZZZZ candidates.
+The vast majority of these signals are, of course, not induced by a
+transiting planet.
+Therefore to reduce the search space, we estimate the signal-to-noise of each
+candidate by comparing the peak height to a robust estimate of variance in
+\TIC\ values across period.
+This is not the same criterion used to select the initial three peaks but we
+found that at this stage, it produced a more complete and pure sample.
+A cut in this quantity can reject most variable stars and low signal-to-noise
+candidates that can't be reliably recovered from the data.
 Figure SOMEFIGURE shows the distribution of signal-to-noise for a set of
@@
 contaminated by false alarms.
-This might be due to the fact that our independence assumption (SOMEEQUATION)
-breaks down at these short periods.
+This might be because of the fact that our independence assumption
+(SOMEEQUATION) breaks down at these short periods.
 Therefore, we discard all signals with periods shorter than 4 days.

### 2015-02-12 ms.tex
editing the intro a bit

@@
 afflicted by systematic effects caused by the relative imprecision of the
-telescope pointing, and possibly other spacecraft effects.
+telescope pointing and other spacecraft effects.
 We present a method for searching these light curves for evidence of
@@
 This method is more computationally expensive than standard search algorithms
-but we demonstrate that it can be efficiently implemented and used to
-discover transit signals in the existing dataset.
+but we demonstrate that it can be efficiently implemented and used to robustly
+discover transit signals.
 We apply this method to the full Campaign 1 dataset and report a list of XXX
@@
 
-The \kepler\ Mission (cite something) has been incredibly succesful at
-finding periodic transits (eclipses) in the light curves (time-series
-photometry) of stars (cite something).
-The Mission has demonstrated that it is possible to routinely measure
-signals in stellar light curves at the part-in-$10^5$ level.
-Results from the primary mission include the detection of planet
-transits with depths as small as 12 parts per million \citep{Barclay:2013}.
+The \kepler\ Mission (cite something) has been incredibly successful at
+finding transiting exoplanets in the light curves of stars (cite something).
+The Mission has demonstrated that it is possible to routinely measure signals
+in stellar light curves at the part-in-$10^5$ level.
+Results from the primary mission include the detection of planet transits with
+depths as small as 12 parts per million \citep{Barclay:2013}.
 
@@
 Although they generally do not influence the ability to search for transiting
-planets, larger systematic (noise shits) exist on different timescales.
-One of the most serious of these is spacecraft pointing:
-If the detector flat-field is not known \emph{exquisitely}, then
-tiny changes to the relative illumination of pixels caused by a star's
-motion in the focal plane (or caused by motion of the focal-plane
-boresight or orientation relative to the celestial sphere) will lead
+planets, larger systematic effects exist on different timescales.
+One of the most serious of these is spacecraft pointing: If the detector
+flat-field is not known \emph{exquisitely}, then tiny changes to the relative
+illumination of pixels caused by a star's motion in the focal plane will lead
 to changes in the measured or inferred brightness of the star.
@@
 the primary mission.
-This primary mission came to an end with the failure of a critical
-reaction wheel, rendering the spacecraft less able to maintain precise
-pointing.
-The \KT\ Mission \citep{Howell:2014} is a follow-on to the primary
-\kepler\ Mission, observing approximately a dozen fields near the ecliptic
-plane, each for 75 days at a time.
-Because of the degraded spacecraft orientation systems, the new
-\KT\ data will in general exhibit far greater pointing
-variations---and far greater pointing-induced variations in
-photometry---than the original \kepler\ data.
+This stability came to an end with the failure of a critical reaction wheel.
+The \KT\ Mission \citep{Howell:2014} is a follow-on to the primary \kepler\
+Mission, observing about a dozen fields near the ecliptic plane, each for
+$\sim 75$ days at a time.
+Because of the degraded spacecraft orientation systems, the new \KT\ data
+exhibit far greater pointing variations---and substantially more
+pointing-induced variations in photometry---than the original \kepler\ data.
 This makes good data-analysis techniques even more valuable.
@@
 \KT\ \citep{Vanderburg:2015}.
-\citet{Crossfield:2015} iteratively construct a robust Gaussian Process
-model for the photometry as a function of the measured centroids and de-trend
-using the mean prediction from that model.
-DFM HERE IS WHERE WE (cite Dun AAS and in prep).
+Both \citet{Aigrain:2015} and \citet{Crossfield:2015} use a Gaussian Process
+model for the measured flux, with pointing measurements as the inputs, and
+then ``de-trend'' using the mean prediction from that model.
+Other data-driven approaches have been developed and applied to the \Kepler\
+data \citep[for example,][]{pdc1, pdc2, arc, dun} but they have yet to be
+generalized to be applicable to \KT.
 
-In these light-curve processing methodologies,
-the authors follow a traditional procedure of ``correcting'' the light curve
-as a step that happens \emph{before} the search for transiting planets.
-Light curves from the primary \kepler\ mission are typically de-trended to
-remove the effects of stellar variability before searching for transiting
-planets.
-With \KT, application of the traditional methods involves fitting and subtracting measured
-effects from the spacecraft pointing variations and stellar variability.
-Fit-and-subtract is dangerous:
-Small signals, such as planet transits, can be partially absorbed into the
-best-fit stellar variability or systematics models, making each individual transit event appear
-shallower; that is, the traditional methods are prone to over-fitting.
-Because over-fitting will in general reduce the amplitude of true exoplanet signals,
-small planets that ought to appear just above any specific signal-to-noise
-or depth
-threshold could be missed because of the de-trending.
+In all of these light-curve processing methodologies, the authors follow a
+traditional procedure of ``correcting'' or ``de-trending'' the light curve to
+remove systematic and stellar variability as a step that happens \emph{before}
+the search for transiting planets.
+Fit-and-subtract is dangerous: Small signals, such as planet transits, can be
+partially absorbed into the best-fit stellar variability or systematics
+models, making each individual transit event appear shallower.
+In other words, the traditional methods are prone to over-fitting.
+Because over-fitting will in general reduce the amplitude of true exoplanet
+signals, small planets that ought to appear just above any specific
+signal-to-noise or depth threshold could be missed because of the de-trending.
+This becomes especially important as the amplitude of the noise increases.
 

### 2015-02-12 ms.tex
more intro edits

@@
 \newcommand{\tess}{\project{TESS}}
+\newcommand{\jwst}{\project{JWST}}
 \newcommand{\terra}{\project{TERRA}}
@@
 then ``de-trend'' using the mean prediction from that model.
-Other data-driven approaches have been developed and applied to the \Kepler\
+Other data-driven approaches have been developed and applied to the \kepler\
 data \citep[for example,][]{pdc1, pdc2, arc, dun} but they have yet to be
@@
 and the transit signals.
-Simultaneous fitting enables a search for---and measurement of---exoplanet signals
-to deliver results that are
-independent of any implied estimate of the systematics, provided that the true
-systematics lie in the domain of the systematics model.
-DFM I WOULD SAY HERE \emph{WHY} SIMULTANEOUS FITTING LEADS TO INDEPENDENCE, AND WHAT DO YOU MEAN BY THAT?
-The likelihood of the simultaneous fit of the systematics and transit signals
-to the data can then be compared to the likelihood of the fit of the systematics
-alone, reducing exoplanet ``search'' to a simple model comparison problem.
+This method can push the detection limits to lower signal-to-noise while
+robustly accounting for uncertainties about the systematic trends.
+In particular, this allows us to \emph{marginalize} over choices in the noise
+model and propagate any uncertainties to our confidence in the detection.
+\dfmtodo{Do we need more about marginalization here?}
 
-DFM:  HERE IS WHERE I WOULD TALK ABOUT MARGINALIZATION...DFM: DOES THIS METHOD MARGINALIZE OUT THE SYSTEMATICS?  (It could,
-right, because the mean and variance of the Gaussian likelihood are
-analytic (though maybe expensive).)  If we \emph{do} marginalize (or
-maybe either way), we need to emphasize here the difference between
-simultaneously \emph{estimating} the signal and the noise as opposed
-to simultaneously \emph{fitting} the signal and the noise and
-marginalization out of the latter.  Key idea: Don't come to a
-conclusion about (estimate) anything you don't care about, if you can
-possibly avoid it!
-
-In this \paper\ we present a
-data-analysis technique for exoplanet search and characterization that
-is insensitive to spacecraft-induced (or, in general,
-hardware-induced) trends in the light curves.
-We assume the trends in the observed light curves in each star due to
+In this \paper\ we present a data-analysis technique for exoplanet search and
+characterization that is insensitive to spacecraft-induced trends in the light
+curves.
+We assume that the trends in the observed light curves in each star due to
 spacecraft motion are shared by each star, and run PCA to measure the dominant
 modes.
-We then search for planets by modeling the data as a linear combination of
-these basis vectors and a transit model.
-Such a technique builds on the ideas of previous PCA-based \kepler\ planet
-searches, such as those of (cite-Petigura).
+We then search for planets by modeling the data as a linear combination of a
+huge number of these basis vectors and a transit model.
+Our method builds on the ideas of previous data-driven de-trending procedures
+like Pre-search data conditioning \citep[PDC;][]{pdc1, pdc2} but we can use a
+much more flexible systematics model without worrying about over-fitting.
 
-The methods developed within this paper are highly relevant to the upcoming
-\tess\ mission \citep{Ricker:2014}.
-\tess\ will feature pointing precision of $\sim 3$ arcseconds (cite),
-similar to the level of pointing drift with \KT.
+The methods developed within this paper are highly relevant to both \KT\ and
+the upcoming \tess\ mission \citep{Ricker:2014}.
+\tess\ will feature pointing precision of $\sim 3$ arcseconds (cite), similar
+to the level of pointing drift with \KT.
 Moreover, the typical star will be only observed for one month at a time, and
@@
 
-Catalogs of transiting planets found in the \KT\ data will be important to better
-understand the physical properties, formation, and evolution of planetary systems.
-These planets, especially when they orbit especially bright or late-type stars,
-will be useful targets for ground-based and space-based follow-up, both for
-current facilities and those planned in the near-future such as JWST.
-They will also deliver input data for next-generation population inferences (cite DFM),
-which in turn constrain population synthesis models.
+Catalogs of transiting planets found in the \KT\ data will be important to
+better understand the physical properties, formation, and evolution of
+planetary systems.
+These planets, especially when they orbit especially bright or late-type
+stars, will be useful targets for ground-based and space-based follow-up, both
+for current facilities and those planned in the near-future such as \jwst.
+They will also deliver input data for next-generation population inferences
+\citep{dfm}, especially for the population of planets around cool stars
+\citep[for example][]{dressing}.
 
@@
 \end{eqnarray}
+Note that this result is \emph{marginalized} over the parameters of the
+systematics model.
+Therefore, this estimate of the uncertainty on the depth takes any
+uncertainty that we have about the systematics into account.
 

### 2015-02-12 ms.tex
editing photometry

@@
 \newcommand{\terra}{\project{TERRA}}
+\newcommand{\pdc}{\project{PDC}}
 \newcommand{\license}{MIT License}
@@
 Our method builds on the ideas of previous data-driven de-trending procedures
-like Pre-search data conditioning \citep[PDC;][]{pdc1, pdc2} but we can use a
+like Pre-search data conditioning \citep[\pdc;][]{pdc1, pdc2} but we can use a
 much more flexible systematics model without worrying about over-fitting.
@@
 
-Most methods for analyzing \KT\ data---and \kepler\ data, for that
-matter---involve some sort of pre-processing or ``de-trending'' step.
-For example, \citet{Vanderburg:2014} measure the centroid motion for each star
-and regress out any signal in their aperture photometry that can be fit by
-this motion.
-Similarly, \citet{Crossfield:2015} iteratively construct a robust Gaussian
-Process model for the photometry as a function of the measured centroids and
-de-trend using the mean prediction from that model.
+All previous methods for analyzing \KT\ data involve some sort of
+``correction'' or ``de-trending'' step based on measurements of the pointing
+motion of the spacecraft \citep{Vanderburg:2014, Aigrain:2015,
+Crossfield:2015}.
 In our analysis, we don't do any further preprocessing of the light curves
 because, as we describe in the next section, we simultaneously fit for the
-trends and the transit signals that we are searching for.
+trends and the transit signals that we are searching for in the raw
+photometric light curves.
 
@@
 the detector.
-To make use of this, the \project{PDC} component of the \kepler\ pipeline
+To make use of this, the \pdc\ component of the \kepler\ pipeline
 removes any trends from the light curves that can be fit using a linear
-combination of a small number of ``eigen-light curves'' (ELCs) found by
-running Principal Component Analysis (PCA) on a set of light curves
-\citep{pdc1, pdc2}.
+combination of a small number of ``co-trending basis vectors''.
+This basis of trends was found by running Principal Component Analysis (PCA)
+on a large set of light curves and extracting the top few ($\sim 4$)
+components \citep{pdc1, pdc2}.
 Similarly, we ran PCA on the full set of Campaign 1 light curves to determine
-a basis of representative ELCs.
-We chose to use the top 150 components---many more than are normally
-used---for our model described in the following section.
-\Fig{pca} shows the top few ELCs.
+a basis of representative trends but, unlike \pdc, we retain and use
+a large number of these components.
+For clarity, we will refer to our basis as a set of ``eigen light curves''
+(ELCs) and the full set is made available online (SOMEURL).
+\Fig{pca} shows the top ten ELCs for Campaign 1.
 
@@
 For \KT, this has been implemented by asserting that the centroids contain
-all of the information needed to describe the trends.
+all of the information needed to describe the trends \citep{Vanderburg:2014,
+Aigrain:2015, Crossfield:2015}.
 In the \kepler\ pipeline, this is implemented by only allowing a small number
-of PCA components to contribute to the fit.
+of PCA components to contribute to the fit in the \pdc\ procedure.
 
-Physically, the motivation for our model---and the PDC model---is that every
+Physically, the motivation for our model---and the \pdc\ model---is that every
 star on the detector should be affected by same set of systematic effects.

### 2015-02-12 ms.tex
editing model section

@@
 The main reason for this is that the signal is not exactly orthogonal to the
-systematics and the de-trending will over-fit causing the signal to be
-distorted and weaker.
+systematics and any de-trending will over-fit; decreasing the amplitude of the
+signal and distorting its shape.
 In order to reduce this effect, most procedures use a very rigid model for
@@
 of PCA components to contribute to the fit in the \pdc\ procedure.
+Instead, we will use a large number of ELCs---a very flexible model---and
+use a physically motivated method to avoid over-fitting.
 
 Physically, the motivation for our model---and the \pdc\ model---is that every
-star on the detector should be affected by same set of systematic effects.
+star on the detector should be affected by the same set of systematic effects.
 These are caused by things like pointing jitter, temperature variations, and
 other sources of PSF modulation and each one will be imprinted in the light
-curves of many stars with varying amplitudes and signs.
+curves of many stars with varying amplitudes and signs as a result of the
+varying flat field.
 Therefore, while it is hard to write down a physical generative model for the
@@
 This intuition is also exploited by other methods that model the systematics
-using only empirical centroids \citep{Vanderburg:2014, Crossfield:2015} but
-out more flexible model should capture the systematic effects more robustly
-but there is a risk of over-fitting.
-\Fig{corr} shows the application of this model to a light curve with no known
-transit signals.
+using only empirical centroids \citep{Vanderburg:2014, Aigrain:2015,
+Crossfield:2015} but our more flexible model should capture the systematic
+effects more robustly.
+For example, \Fig{corr} shows the application of our model---with 150
+ELCs---to a light curve with no known transit signals and the precision is
+excellent.
+If, however, we were to apply this model blindly to a light curve with
+transits, we would be at risk of over-fitting and decreasing the amplitude of
+the signal.
 
-To avoid over-fitting in our pipeline, we simultaneously fit for the transit
+To avoid over-fitting, in our pipeline we simultaneously fit for the transit
 signal and the trends using a rigid model for the signal and a relatively
@@
 Specifically, we model the light curve as being generated by linear
-combination of the 150 basis light curves and a ``box'' transit model at a
-given period and phase.
+combination of 150 ELCs and a ``box'' transit model at a specific period,
+phase, and duration.
+The mathematical details are given in \app{math} but in summary, since the
+model is linear, we can analytically compute the likelihood
+function---conditioned on a specific period, phase, and duration---for the
+depth \emph{marginalized over the systematics model}.
+This computation is expensive but, as described in the following sections, it
+is possible to scale the method to a \KT-scale dataset.
+
+It is worth noting that this model can be equivalently thought of as a
+(computationally expensive) generalization of the ``Box Least Squares''
+\citep[\project{BLS};][]{bls} method to a more sophisticated description of
+the noise and systematics.
+Therefore, any existing search pipeline based on \project{BLS} could, in
+theory, use this model as a drop-in replacement, although some modifications
+might be required for computational tractability.
 
@@
 
-\bibliography{k2}
-
 \clearpage
@@
 
+\clearpage
+\bibliography{k2}
 \clearpage

### 2015-02-12 ms.tex
adjustments to title, abstract, discussion

@@
 \title{%
-    A systematic search for transiting planets using \KT
+    A systematic search for transiting planets in the \KT\ data % hogg changed title!
 }
@@
 afflicted by systematic effects caused by the relative imprecision of the
-telescope pointing and other spacecraft effects.
+telescope pointing and other spacecraft issues.
 We present a method for searching these light curves for evidence of
@@
 
-\paragraph{Maybe this goes in results} (Hogg say yes!)
+We have searched the \KT\ Campaign~1 data set for exoplanet transit signals.
+Our search is novel because it includes a very flexible systematics model,
+which is fit simultaneously with the exoplanet signals of interest, and
+marginalized out.
+By this method, we find XXX new exoplanets, which we have vetted by ZZZ
+method and characterized by probabilistic modeling.
+The candidates are listed in \dfmtodo{some table} and
+posterior distributions of planet candidate properties are available at
+\dfmtodo{thisurl}.
 
-We include posterior distributions of planet candidate properties, available at
-\dfmtodo{thisurl}.
-These distributions are specifically \emph{NOT} marginalized over stellar
-properties.
-In this work, we are agnostic about fundamental properties of the host star.
-In fact, the only assumptions we make are that the star targeted by the \KT\
+The posterior distributions we release are given in terms of observational
+quantities (rather than physical quantities) and are specifically \emph{NOT}
+marginalized over stellar properties.
+In this work, we are agnostic about fundamental properties of the host stars.
+The only assumptions we make are that the star targeted by the \KT\
 team is truly the planet host, and that there is no dilution by other stars in
@@
 As a result, these posterior distributions reflect the maximum possible
-uncertainty in parameters such as the planet radius which depend sensitively
+uncertainty in parameters such as the planet radius, which depend sensitively
 on properties of the host star.

### 2015-02-12 ms.tex
reasons we use a high-parameter linear model

@@
 
+The systematics model is a 150-parameter linear combination of PCA components
+derived from the full set of 20,000 stellar lightcurves.
+That is, it presumes that the systematics afflicting each star are shared in
+some way across all other stars.
+It is our belief---although not a strict assumption of our model---that these
+systematics are caused primarily by pointing drifts, or movements of the
+pixels in the focal plane relative to the stars.
+In principle, if the systematics \emph{are} dominated by pointing issues, the
+systematics model could require only three parameters---three Euler
+angles---not 150 amplitudes.
+However, because (as the pointing drifts) each star sees it's own unique
+local patch of flat-field variations, the mapping from pointing drifts to
+brightness variations can be extremely non-linear.
+Furthermore, because when the pointing is moving fast, there is effectively
+a smearing of the point-spread function, there are effects keyed to the
+time derivative of the Euler angles as well.
+The large number (150) of linear coefficients gives the linear model the
+freedom to model complex non-linear behavior; we are trading off parsimony
+in parameters with the enormous computational advantages of maintaining
+linearity (and therefore also convexity).
+The computational advantages of the linear model are three-fold:
+Convexity obviates searching in parameter space for alternative modes;
+linear least-squares optimization can be performed with simple linear algebra;
+given Gaussian uncertainties and uninformative priors, marginalizations over
+the linear parameters also reduces to pure linear algebra.
+
 The posterior distributions we release are given in terms of observational

### 2015-02-12 ms.tex
copyright statement
not much
limitations of what we have done

@@
+% This paper is part of the k2-paper project.
+% Copyright 2015 Dan Foreman-Mackey (NYU) and the co-authors listed below.
 %
@@
 
-The systematics model is a 150-parameter linear combination of PCA components
+The flexible systematics model we employ is a 150-parameter linear combination of PCA components
 derived from the full set of 20,000 stellar lightcurves.
 That is, it presumes that the systematics afflicting each star are shared in
-some way across all other stars.
+some way across other stars.
 It is our belief---although not a strict assumption of our model---that these
@@
 brightness variations can be extremely non-linear.
-Furthermore, because when the pointing is moving fast, there is effectively
+Furthermore, because when the pointing is moving fast there is effectively
 a smearing of the point-spread function, there are effects keyed to the
@@
 
-The goal of this \paper\ was to get exoplanet candidates out of the \KT\ pixel-level data,
-it was not to generate light curves...
-the project does not really produce corrected light curves at all; why not?
+The goal of this \paper\ was to get exoplanet candidates out of the
+\KT\ pixel-level data, it was \emph{not} to generate light curves.
+That is, both the search phase and the characterization phase of the method
+are approximations to computations of a likelihood function for the pixel
+data telemetered down from the satellite.
+We did not generate ``corrected'' or ``pre-search conditioned'' light-curves
+at any stage; we simultaneously fit systematics and the signals of interest
+to the raw data.
+For this reason, there is no sense in which this method ever really
+produces corrected light curves.
+For us, a systematics-corrected light curve is not really a thing.
 
-This is not the last time the \KT\ data will be searched...
-list some deficiencies of this search method
-(these might include approximations in the PHIC,
-the fact that it deals well with spacecraft systematics but not stellar variability,
-and that it isn't sensitive to single transits (which must be common)).
+This is not the last time the \KT\ data will be searched!
+There are many heuristic choices and short-cuts made in this search.
+For example, the choice to work at 150 principal components is a choice
+driven more by computational feasibility than any model selection or
+utility optimization.
+The systematics model is good for spacecraft-induced variability, but not
+intrinsic stellar variability.
+The systematics model has no concept of a physical model of the spacecraft or
+the camera; that is, it makes little use of our prior information about how
+\KT\ images are generated physically.
+The search is performed with a box model and severe approximations are employed
+to make it fast.
+We don't consider planets (which must be abundant) on periods longer
+than those that would leave two transits within the \KT\ Campaign~1
+data set.
 
-The machine and hand vetting leave much to be desired...
+Most importantly, perhaps, the machine and hand vetting leave much to be desired...
 list some deficiencies of the vetting.
@@
 there is essentially no estimate of the non-astrophysical false positive rate.
+(There really is no proposal on the table anywhere for getting a false-positive
+rate for the non-astrophysical FPs.)
 

### 2015-02-12 ms.tex
a bit of reordering in discussion
editing pipeline intro and linear search

--- 2015-02-12 ms.tex
@@
 \section{Joint transit \& variability model}
-\label{sec:model}
+\sectlabel{model}
 
@@
 depth \emph{marginalized over the systematics model}.
+The signal-to-noise of this depth measurement can then be used as a quality
+of fit metric or candidate selection scalar.
 This computation is expensive but, as described in the following sections, it
@@
 
-In theory, search could proceed by evaluating the model described above on a
-fine three-dimensional grid in period, phase, and duration.
+In principle, the search for transit signals simply requires evaluating the
+model described above on a fine three-dimensional grid in period, phase, and
+duration, and then detecting high significance peaks in that space.
 In practice, this is computationally intractable for any grids of the
@@
 
-The specific quantity that we will be searching is the likelihood for the
-light curve of star $n$ given a set of transit parameters:
-\begin{eqnarray}
+Specifically, we must evaluate the likelihood function for the light curve of
+star $n$ given a period \period, reference transit time \phase, and duration
+\duration
+\begin{eqnarray}\eqlabel{full-likelihood}
 p(\{\flux\}_n\,|\,\period,\,\phase,\,\duration,\,\depth) \quad.
 \end{eqnarray}
-We will make the simplifying assumption that each transit is independent
-because it will be approximately satisfied for all but the shortest periods
-and it leads to a huge computational advantage.
+We make the simplifying assumption that each transit enters this quantity
+independently because it is approximately satisfied for all but the shortest
+periods and it leads to a huge computational advantage.
 Under this assumption, this likelihood function can be rewritten as
 \begin{eqnarray}\eqlabel{indtran}
-p(\{\flux\}_n\,|\,\period,\,\phase,\,\duration,\,\depth) &\approx&
+p(\{\flux\}_n\,|\,\period,\,\phase,\,\duration,\,\depth) &=&
 \prod_{m=1}^{M(\period,\,\phase)}
@@
 \Eq{indtran} can be efficiently computed for many periods and phases if we
-first compute a set of likelihood functions for single transits on a fine grid
-in $\transittime_l$
+first compute a set of likelihood functions for single transits on a grid
+in $\transittime_l$ and duration $\duration_k$
 \begin{eqnarray}\eqlabel{singletransit}
 \left \{ p(\{\flux\}_n\,|\,\transittime_l,\,\duration_k,\,\depth)
-\right\}_{l=1,\,k=1}^{L,\,K}
+\right\}_{l=1,\,k=1}^{L,\,K} \quad.
 \end{eqnarray}
-then use these results as a lookup table.
+Then, we can use these results as a look-up table to approximately evaluate
+\eq{full-likelihood}.
 
@@
 three-dimensional grid of periodic signals.
-Then, we run a peak detection algorithm on this grid that discards peaks that
-share transits with a shorter period candidate and signals with substantially
-varying transit depths.
+Then, we run a peak detection algorithm on this grid that discards signals
+with substantially varying transit depths.
 These transit candidates are then passed along for machine and human {\bf
@@
 
-The linear search involves hypothesizing a transit signal on a
+The linear search requires hypothesizing a set of transit signals on a
 two-dimensional grid in transit time and duration.
-For each point in the grid, we use the model described in the previous
-section to evaluate \emph{the likelihood function} of the transit depth.
-Because the model is linear, the likelihood function for the depth
-(marginalized over the model of the systematics) is a Gaussian with
-analytic amplitude $L$, mean $\bar{\depth}$, and variance
-$\delta\bar{\depth}^2$ derived in \app{math}.
+For each point in the grid, we use the model described in \sect{model} to
+evaluate \emph{the likelihood function} for the transit depth at that time
+and duration.
+Since the model is linear, the likelihood function for the depth (marginalized
+over the model of the systematics) is a Gaussian with analytic amplitude $L$,
+mean $\bar{\depth}$, and variance $\delta\bar{\depth}^2$ derived in
+\app{math}.
 Therefore in the linear search, we save these three numbers for a
-two-dimensional grid in transit time \transittime\ and duration \duration.
+two-dimensional grid in transit time $\transittime_l$ and duration
+$\duration_k$.
 The transit time grid spans the duration of Campaign 1 with half hour spacing
@@
 with transits at the times indicated by the vertical green bars.
-The computational complexity of this step is $\mathcal{O}(M\,K^3)$ where $M$
-is the number of points in the grid and $K$ is the number of data points.
+
+% The computational complexity of this step is $\mathcal{O}(M\,K^3)$ where $M$
+% is the number of points in the grid and $K$ is the number of data points.
 
@@
 
-\clearpage
 \appendix

### 2015-02-12 ms.tex

@@
 
+The goal of this \paper\ was to get exoplanet candidates out of the
+\KT\ pixel-level data, it was \emph{not} to generate light curves.
+That is, both the search phase and the characterization phase of the method
+are approximations to computations of a likelihood function for the pixel
+data telemetered down from the satellite.
+We did not generate ``corrected'' or ``pre-search conditioned'' light-curves
+at any stage; we simultaneously fit systematics and the signals of interest
+to the raw data.
+For this reason, there is no sense in which this method ever really
+produces corrected light curves.
+For us, a systematics-corrected light curve is not really a thing.
+
 The posterior distributions we release are given in terms of observational
@@
 
-The goal of this \paper\ was to get exoplanet candidates out of the \KT\ pixel-level data,
-it was not to generate light curves...
-the project does not really produce corrected light curves at all; why not?
-
-This is not the last time the \KT\ data will be searched...
-list some deficiencies of this search method
-(these might include approximations in the PHIC,
-the fact that it deals well with spacecraft systematics but not stellar variability,
-and that it isn't sensitive to single transits (which must be common)).
-
-The machine and hand vetting leave much to be desired...
-list some deficiencies of the vetting.
-
-Characterization of these candidates can be much improved...
-list the things we could know if we had follow-up observations of the stars.
-
 To use these distributions to characterize the properties of specific systems,
@@
 
+This is not the last time the \KT\ data will be searched!
+There are many heuristic choices and short-cuts made in this search.
+For example, the choice to work at 150 principal components is a choice
+driven more by computational feasibility than any model selection or
+utility optimization.
+The systematics model is good for spacecraft-induced variability, but not
+intrinsic stellar variability.
+The systematics model has no concept of a physical model of the spacecraft or
+the camera; that is, it makes little use of our prior information about how
+\KT\ images are generated physically.
+The search is performed with a box model and severe approximations are employed
+to make it fast.
+We don't consider planets (which must be abundant) on periods longer
+than those that would leave two transits within the \KT\ Campaign~1
+data set.
+
+Most importantly, perhaps, the machine and hand vetting leave much to be desired...
+list some deficiencies of the vetting.
+
 The completeness and false-positive assessment could be vastly improved...

### 2015-02-13 ms.tex
a few specific numbers

@@
 To minimize contamination from false alarms but maximize our sensitivity, we
-choose a threshold of 15 \dfmtodo{right number?}.
+choose a threshold of 15.
 We also find that the signals with periods $\lesssim 4$ days are very
@@
 Therefore, we discard all signals with periods shorter than 4 days.
-After these cuts, we're left with 700 \dfmtodo{right number?} candidates that
-we then examine by hand.
+After these cuts, we're left with 741 candidates that we then examine by hand.
 The full list of peaks and their relevant meta data is available online at

### 2015-02-13 ms.tex
outline and injections

@@
 The \paper\ is organized as follows.
-In \textsection\ref{sec:phot}, we describe our analysis of the photometric
-data collected by \KT.
-In \textsection\ref{sec:model}, we expain our simultaneous fit of the
-systematics and transit model.
-In \textsection\ref{sec:search}, we describe our search pipeline for
-planet candidates.
-In \textsection\ref{sec:perform}, we quantify the performace of our pipeline
-through the analysis of injected planetary signals.
-In \textsection\ref{sec:K2OIs}, we present the results of our search:
-catalogs of \KT\ planet candidates and eclipsing binaries.
-In \textsection\ref{sec:discuss}, we discuss our results and outline our
-future work.
+In \sect{phot}, we describe our method of extracting aperture photometry from
+the calibrated \KT\ postage stamp time series.
+In \sect{model} (with details in \app{math}), we describe our data-driven
+model for the systematic trends in the photometric light curves and our method
+for fitting this model simultaneously with a transit signal.
+In \sect{search}, we give the detailed procedure that we use for discovering
+and vetting planet candidates.
+To quantify the performance and detection efficiency of our pipeline, we test
+(in \sect{perform}) the recovery and false alarm rate of synthetic transit
+signals, spanning a large range of physical parameters, injected into real
+\KT\ light curves.
+Finally, in \sect{results}, we present a catalog of XXXX planet candidates
+orbiting WWWW stars---and a supplementary list of YYYY eclipsing binary
+candidates---in the publicly available \KT\ Campaign 1 dataset.
 
 \section{Photometry}
-\label{sec:phot}
+\sectlabel{phot}
 
@@
 \section{Search pipeline}
-\label{sec:search}
+\sectlabel{search}
 
@@
 difference.
-Searching for ellipsoidal varaitions is hindered by the short time baseline
+Searching for ellipsoidal variations is hindered by the short time baseline
 and the increased photometric uncertainty in \KT\ data.
@@
 To obtain an initial assessment of the astrophysical false positive rate in
-our catalog of planet candidates, we test for centroid offsets and variable
-depth transits using the machinery that we have already established for
-modeling the systematic trends in the data.
+our catalog of planet candidates, we test for significant centroid offsets
+using the machinery that we have already established for modeling the
+systematic trends in the data.
 This is only the first word and a more complete characterization of our
@@
 of the spacecraft and we can, in fact, model it identically.
-Previously (SOMEEQUATION), we modeled the light curve as a linear combination
-of ELCs and a simple box transit model at a given period, phase, and duration.
+Previously (\eqalt{linear-model}), we modeled the light curve as a linear
+combination of ELCs and a simple box transit model at a given period, phase,
+and duration.
 Under this model, the maximum likelihood depth can be computed analytically.
@@
 If the centroid measured for the candidate transit is substantially larger
-(by SOMEAMOUNT) than the random realizations, then the candidate is labeled
-as a false positive.
-Figure SOMEFIGURE shows the distribution of centroid offsets across our
-catalog and YYYY---or ZZZZ\%---of our candidates fail this test.
-
-We also test the consistency \emph{between even and odd transit depths} for
-each of our candidates.
-As described in SOMESECTION, our method for transit search automatically
-rejects signals with wildly varying depths but.
-
-Blah blah blah.
-Therefore, false positives caused by background eclipsing binaries which could
-be identified as such by \kepler\ data alone will be much more difficult to
-distinguish in \KT\ data, making high-contrast adaptive optics images of
-planet candidates an essential follow-up tool.
+than the random realizations, we label the candidate as a false positive.
+In practice, the precision of the centroid measurements isn't sufficient to
+robustly reject many candidates but of the list of 100 (RIGHT NUMBER), two
+candidates---EPIC AAA and BBB---have offsets large enough that we remove them
+from our final catalog.
+Figure SOMEFIGURE shows the distribution of centroid offsets across the full
+catalog.
 
 \section{Performance}
+\sectlabel{perform}
 
-To test the performance of our method, we conducted a suite of XXXX injection
-and recovery tests.
+To test the performance and detection efficiency of our method, we conducted a
+suite of XXXX injection and recovery tests, this is the result of 5 tests per
+star.
 For each test, we inject the signal from a realistic planetary system into the
-raw aperture photometry and passed it through the full pipeline.
+raw aperture photometry of a random target and run the resulting light curve
+through the full pipeline.
+If the search returns a planet candidate---passing all of the same cuts as we
+apply in the main search---with period and reference transit time within
+HOWMANY days of the injected signal, we count that injection as recovered.
+The detection efficiency of the search is approximately given by the fraction
+of recovered injections as a function of the relevant parameters.
+
 These synthetic systems have periods and radius ratios drawn uniformly in
@@
 \section{Results}
+\sectlabel{results}
 
@@
 
-\section{Mathematical model}\sectlabel{math}
+\section{Mathematical model}
+\sectlabel{math}
 

### 2015-02-13 ms.tex
tinytweak

--- 2015-02-13 ms.tex
@@
 Our search is novel because it includes a very flexible systematics model,
-which is fit simultaneously with the exoplanet signals of interest, and
-marginalized out.
+which is fit simultaneously with the exoplanet signals of interest (and
+marginalized out).
 By this method, we find XXX new exoplanets, which we have vetted by ZZZ

### 2015-02-13 ms.tex
table of parameters for injections

@@
 \newcommand{\transittime}{{\ensuremath{T}}}
+\newcommand{\impact}{{\ensuremath{b}}}
+\newcommand{\ecc}{{\ensuremath{e}}}
+\newcommand{\pomega}{{\ensuremath{\varpi}}}
 
@@
 
+To generate the synthetic signals, we follow the following procedure:
+\begin{enumerate}
+
+{\item draw the number of transiting planets based on the observed
+multiplicity distribution of KOIs (CITE),}
+
+{\item for each planet, choose limb darkening parameters, orbital periods,
+phases, radius ratios, impact parameters, eccentricity, and argument of
+periapsis, from the distributions listed in \tab{dist}}
+
+\end{enumerate}
+
 These synthetic systems have periods and radius ratios drawn uniformly in
@@
 
+\clearpage
+
+\begin{table}[p]
+\begin{center}
+\begin{tabular}{lcc}
+\toprule
+Parameter & Units & Distribution \\
+\midrule
+
+limb darkening parameters $q_1$ and $q_2$ & --- & $q \sim U(0,\,1)$ \\
+orbital period \period & days & $\ln \period \sim U(\ln 0.5,\,\ln 70)$ \\
+reference transit time \phase & days & $\phase \sim U(0,\,\period)$ \\
+radius ratio $R_P/R_\star$ & --- & $\ln R_P/R_\star \sim U(\ln 0.02,\,\ln 0.2)$ \\
+impact parameter \impact & --- & $\impact \sim U(0,\,1)$ \\
+eccentricity \ecc & --- & $\ecc \sim \mathrm{Beta}(0.867,\,3.03)$ \\
+argument of periapsis \pomega & --- & $\pomega \sim U(-\pi,\,\pi)$ \\
+
+\bottomrule
+\end{tabular}
+\end{center}
+\caption{%
+The distribution of physical parameters for the injected signals.
+The eccentricity distribution is based on \citet{kipping-ecc} and the
+limb darkening parameterization is given by \citet{kipping-ld}.
+\tablabel{dist}}
+\end{table}
+
 \begin{table}[p]

### 2015-02-13 ms.tex
intro tweaks

--- 2015-02-13 ms.tex
@@
 
-The noise floor for \kepler\ data is often quoted as 15 parts per million per
+The noise floor for \kepler\ data is often quoted as 15 parts per million (ppm) per
 six hours of observations \citep{Gilliland:2011}.
-Although they generally do not influence the ability to search for transiting
+Although they generally do not interfere with searches for transiting
 planets, larger systematic effects exist on different timescales.
 One of the most serious of these is spacecraft pointing: If the detector
-flat-field is not known \emph{exquisitely}, then tiny changes to the relative
+flat-field is not known with very high accuracy, then tiny changes to the relative
 illumination of pixels caused by a star's motion in the focal plane will lead
@@
 
-The pointing of \kepler\ was stable at the (LEVEL) level (citation) throughout
-the primary mission.
-This stability came to an end with the failure of a critical reaction wheel.
-The \KT\ Mission \citep{Howell:2014} is a follow-on to the primary \kepler\
-Mission, observing about a dozen fields near the ecliptic plane, each for
+The great stability of the original \kepler\ Mission
+came to an end with the failure of a critical reaction wheel.
+The \KT\ Mission \citep{Howell:2014} is a follow-on to the primary Mission,
+observing about a dozen fields near the ecliptic plane, each for
 $\sim 75$ days at a time.
@@
 exhibit far greater pointing variations---and substantially more
-pointing-induced variations in photometry---than the original \kepler\ data.
+pointing-induced variations in photometry---than the original \kepler\ Mission data.
 This makes good data-analysis techniques even more valuable.
@@
 and pointing model or else data-analysis techniques that are
-insensitive to such variations.
+insensitive to these instrument properties.
 The flat-field for \kepler\ was measured on the ground before the launch of
@@
 downloaded to Earth, there isn't enough information in the data to derive or
-infer a highly accurate flat-field map.
+infer a complete or accurate flat-field map.
 Therefore, work on \KT\ is sensibly focused on building data-analysis
@@
 the search for transiting planets.
-Fit-and-subtract is dangerous: Small signals, such as planet transits, can be
+Fit-and-subtract is dangerous:
+Small signals, such as planet transits, can be
 partially absorbed into the best-fit stellar variability or systematics
@@
 
-The alternative to this approach is to simultaneously fit both the systematics
+The alternative to this approach is to \emph{simultaneously fit} both the systematics
 and the transit signals.
-This method can push the detection limits to lower signal-to-noise while
+Simultaneous fitting can push the detection limits to lower signal-to-noise while
 robustly accounting for uncertainties about the systematic trends.
-In particular, this allows us to \emph{marginalize} over choices in the noise
-model and propagate any uncertainties to our confidence in the detection.
+In particular, it permits us to \emph{marginalize} over choices in the noise
+model and propagate any uncertainties about the systematic effects
+to our confidence in the detection.
 \dfmtodo{Do we need more about marginalization here?}

### 2015-02-13 ms.tex
intro tweaks

@@
 to our confidence in the detection.
-\dfmtodo{Do we need more about marginalization here?}
+This marginalization ensures that any conclusions we come to about the exoplanet
+properties are conservative, given the freedom of the systematics model.
 
@@
 We assume that the trends in the observed light curves in each star due to
-spacecraft motion are shared by each star, and run PCA to measure the dominant
-modes.
-We then search for planets by modeling the data as a linear combination of a
-huge number of these basis vectors and a transit model.
-Our method builds on the ideas of previous data-driven de-trending procedures
-like Pre-search data conditioning \citep[\pdc;][]{pdc1, pdc2} but we can use a
+spacecraft motion are shared by other stars; the systematic effects are
+modeled as sums of stars.
+We reduce the dimensionality by running PCA on stellar light curves
+to obtain the dominant modes.
+The search for planets proceeds by modeling the data as a linear combination of
+150 of these basis vectors and a transit model.
+Our method builds on the ideas behind previous data-driven de-trending procedures
+such as the \kepler\ pipeline pre-search data conditioning \citep[\pdc;][]{pdc1, pdc2},
+but (because of our simultaneous fitting approach) we can use a
 much more flexible systematics model without worrying about over-fitting.
@@
 planetary systems.
-These planets, especially when they orbit especially bright or late-type
+These planets, especially when they orbit bright or late-type
 stars, will be useful targets for ground-based and space-based follow-up, both
-for current facilities and those planned in the near-future such as \jwst.
+for current facilities and those planned in the near future such as \jwst.
 They will also deliver input data for next-generation population inferences
 \citep{dfm}, especially for the population of planets around cool stars
-\citep[for example][]{dressing}.
+\citep[for example,][]{dressing}.
 

### 2015-02-13 ms.tex
words about completeness

--- 2015-02-13 ms.tex
@@
 \newcommand{\ecc}{{\ensuremath{e}}}
-\newcommand{\pomega}{{\ensuremath{\varpi}}}
+\newcommand{\pomega}{{\ensuremath{\omega}}}
 
@@
 \title{%
-    A systematic search for transiting planets in the \KT\ data % hogg changed title!
+    A systematic search for transiting planets in the \KT\ data
 }
@@
 
-The noise floor for \kepler\ data is often quoted as 15 parts per million (ppm) per
+The noise floor for \kepler\ data is often quoted as 15 parts per million per
 six hours of observations \citep{Gilliland:2011}.
-Although they generally do not interfere with searches for transiting
+Although they generally do not influence the ability to search for transiting
 planets, larger systematic effects exist on different timescales.
 One of the most serious of these is spacecraft pointing: If the detector
-flat-field is not known with very high accuracy, then tiny changes to the relative
+flat-field is not known \emph{exquisitely}, then tiny changes to the relative
 illumination of pixels caused by a star's motion in the focal plane will lead
@@
 
-The great stability of the original \kepler\ Mission
-came to an end with the failure of a critical reaction wheel.
-The \KT\ Mission \citep{Howell:2014} is a follow-on to the primary Mission,
-observing about a dozen fields near the ecliptic plane, each for
+The pointing of \kepler\ was stable at the (LEVEL) level (citation) throughout
+the primary mission.
+This stability came to an end with the failure of a critical reaction wheel.
+The \KT\ Mission \citep{Howell:2014} is a follow-on to the primary \kepler\
+Mission, observing about a dozen fields near the ecliptic plane, each for
 $\sim 75$ days at a time.
@@
 exhibit far greater pointing variations---and substantially more
-pointing-induced variations in photometry---than the original \kepler\ Mission data.
+pointing-induced variations in photometry---than the original \kepler\ data.
 This makes good data-analysis techniques even more valuable.
@@
 and pointing model or else data-analysis techniques that are
-insensitive to these instrument properties.
+insensitive to such variations.
 The flat-field for \kepler\ was measured on the ground before the launch of
@@
 downloaded to Earth, there isn't enough information in the data to derive or
-infer a complete or accurate flat-field map.
+infer a highly accurate flat-field map.
 Therefore, work on \KT\ is sensibly focused on building data-analysis
@@
 the search for transiting planets.
-Fit-and-subtract is dangerous:
-Small signals, such as planet transits, can be
+Fit-and-subtract is dangerous: Small signals, such as planet transits, can be
 partially absorbed into the best-fit stellar variability or systematics
@@
 
-The alternative to this approach is to \emph{simultaneously fit} both the systematics
+The alternative to this approach is to simultaneously fit both the systematics
 and the transit signals.
-Simultaneous fitting can push the detection limits to lower signal-to-noise while
+This method can push the detection limits to lower signal-to-noise while
 robustly accounting for uncertainties about the systematic trends.
-In particular, it permits us to \emph{marginalize} over choices in the noise
-model and propagate any uncertainties about the systematic effects
-to our confidence in the detection.
+In particular, this allows us to \emph{marginalize} over choices in the noise
+model and propagate any uncertainties to our confidence in the detection.
 \dfmtodo{Do we need more about marginalization here?}
@@
 
-To generate the synthetic signals, we follow the following procedure:
+To generate the synthetic signals, we use the following procedure:
 \begin{enumerate}
 
-{\item draw the number of transiting planets based on the observed
-multiplicity distribution of KOIs (CITE),}
-
-{\item for each planet, choose limb darkening parameters, orbital periods,
-phases, radius ratios, impact parameters, eccentricity, and argument of
-periapsis, from the distributions listed in \tab{dist}}
+{\item Draw the number of transiting planets based on the observed
+multiplicity distribution of KOIs (CITE).}
+
+{\item Sample---from the distributions listed in
+\tab{dist}---limb darkening parameters and, for each planet, an orbital
+period, phase, radius ratio, impact parameter, eccentricity, and argument of
+periapsis.}
+
+{\item Based on the chosen physical parameters, simulate the light curve,
+taking limb darkening and integration time into account \citep{ma,
+kipping-int}, and multiply it into the raw aperture photometry.}
 
 \end{enumerate}
-
-These synthetic systems have periods and radius ratios drawn uniformly in
-\dfmtodo{some range} and uniformly distributed impact parameters and phases.
-The eccentricities are drawn from a beta distribution with \dfmtodo{some
-parameters; cite Kipping} and the multiplicity is set to match the observed
-multiplicity distribution in the KOI catalog \dfmtodo{cite}.
-MA limb darkening, exposure time integration, etc.
-
-After running these light curves with injections through the full pipeline, if
-the resulting period and phase of the recovered signal were within YYYY of the
-true injected values, we deemed the injection a success.
-\Fig{completeness} shows the fraction of recovered signals as a function of the
-physical parameters of the injection and the magnitude of the star.
+We then process these light curves using exactly the pipeline that we use for
+the light curves without injections.
+Finally, we test for recovery after applying the cuts in signal-to-noise and
+period.
+We should, of course, also process the results of the injection tests by hand
+to ensure that our measurements of detection efficiency aren't biased by this
+step but, since we chose to limit our sample to very high signal-to-noise
+candidates, it seems unlikely that our hand vetting removed any true transit
+signals.
+Any estimates of the false alarm rate will, however, be affected by this
+negligence but we leave a treatment of this for future discussion.
+
+\Fig{completeness} shows the fraction of recovered signals as a function of
+the physical parameters of the injection and the magnitude of the star.
 As expected, the shallower transits at longer periods are recovered less

### 2015-02-14 ms.tex
acks

@@
 It is a pleasure to thank
-\ldots\
+Ruth Angus (Oxford), Tom Barclay (Ames), \etal
 for helpful contributions to the ideas and code presented here.
-DFM, DWH, and DW were partially supported by the National Science Foundation (grant IIS-1124794),
+DFM, DWH, and DW were partially supported by the National Science Foundation
+(grant IIS-1124794),
 the National Aeronautics and Space Administration
@@
 Fellowship (grant DGE‐1144469).
+
 This research made use of the NASA \project{Astrophysics Data System}.
+This \paper\ includes data collected by the \kepler\ mission. Funding for the
+\kepler\ mission is provided by the NASA Science Mission directorate.
+These data were obtained from the Mikulski Archive for Space Telescopes
+(MAST).
+STScI is operated by the Association of Universities for Research in
+Astronomy, Inc., under NASA contract NAS5-26555.
+Support for MAST is provided by the NASA Office of Space Science via grant
+NNX13AC07G and by other grants and contracts.
 

### 2015-02-14 ms.tex
results words

@@
 robustly.
+It is worth noting that this figure is a two-dimensional projection (or
+marginalization) of a higher dimensional measurement.
+For example, this completeness map is conditioned on our assumptions about
+the eccentricity distribution of planets and it is marginalized over the
+distribution of stellar parameters.
+It is possible to relax this assumption and apply different distributions by
+re-weighting the simulations used to generate this figure.
+Therefore, alongside this \paper, we publish the full list of injection
+simulations\footnote{SOMEURL} to be used for population inference (occurrence
+rate measurements).
+In \fig{completeness}, we also show the detection efficiency---marginalized
+over the same range of periods---as a function of stellar magnitude in the
+\kepler\ bandpass as reported in the EPIC.
 
@@
 
-After running the 21XXX light curves through our full pipeline, we end up
-with XXXX TCEs \dfmtodo{change this name} and after hand vetting, we are left
-with YYYY convincing transiting candidates.
-Of these candidates, ZZZ are probable binaries with obviously visible
-secondary eclipses and we list these candidates in Table \dfmtodo{SOMETABLE}.
-This leaves WWW planet candidates that are listed in Table
-\dfmtodo{SOMETABLE}.
-
-\paragraph{Posterior constraints on physical parameters}
-
-To fit for the observable parameters of the transit signals in detail, we use
-the same linear model for the systematics but then we combine this with a
-physical transit model (M\&A, etc.).
-Since this transit model is no longer linear, we use Markov Chain Monte Carlo
-(MCMC; cite emcee) to draw posterior samples from this model.
-At each step in the chain, we \emph{marginalize over the model of the
-systematics}.
-This means that we don't de-trend the data or make any hard decision about
-the actual value of the systematics.
-We sample the stellar density, limb-darkening coefficients, period, phase,
-radius ratio, impact parameter, eccentricity, and argument of periapsis.
-\dfmtodo{List priors.}
-The quantiles of these posterior samplings are given in table \dfmtodo{some
-table} and the full chains are available electronically \dfmtodo{some URL}.
+After running the 21XXX light curves through our full pipeline, we end up with
+XXXX TCEs \dfmtodo{change this name} and after hand vetting by the two first
+authors of this \paper, we are left with YYYY convincing transiting
+candidates.
+We choose to separate this list into two tables: planet candidates
+(\tab{cand}) and eclipsing binary candidates (\tab{eb}).
+For our purposes, we define an binary candidate as any system where we can
+find a secondary eclipse by visual inspection but in most cases, the
+secondary eclipse is also detected as a smaller transit signal at the same
+period as the primary.
+In this dataset, we discover ZZZ planet candidates around WWW stars.
+Two of these were previously published \citep{Crossfield:2015} but, to our
+knowledge, the remaining list is currently unpublished.
+The third planet published by \citet{Crossfield:2015} is found as the third
+signal for that target by our pipeline but it falls just below our
+signal-to-noise cut so we left it out of the catalog for consistency.
+This suggests that a less conservative cut in signal-to-noise and more
+aggressive machine vetting could yield a much more complete catalog at smaller
+radii and longer periods even with the existing dataset.
+
+For the binaries, we simply list the period, phase, and depth determined by
+the search algorithm but for the planet candidates, we perform a full physical
+transit fit to the light curve.
+To do this fit, we use Markov Chain Monte Carlo \citep[MCMC;][]{emcee} to
+sample from the posterior probability for the stellar and planetary
+parameters taking limb darkening and integration time into account.
+In this fit, we continue to model the trends in the data as a linear
+combination of 150 ELCs but, at this point, we combine this with a realistic
+light curve model \citet{ma, kipping-ld}.
+Even though we have no constraints on the stellar parameters, we also sample
+over a large range in stellar mass and radius so that future measurements can
+be applied by re-weighting the published samples.
+In \tab{cand} we list the sample quantiles for the observable quantities and
+the full chains are available electronically at \dfmtodo{some URL}.
+
+SOMEFIGURE shows the distribution of radius ratios and periods of candidates
+from our sample.
 
@@
 It is a pleasure to thank
+Andrew Vanderburg (Harvard),
 Ruth Angus (Oxford), Tom Barclay (Ames), \etal
@@
 
-This research made use of the NASA \project{Astrophysics Data System}.
+This research made use of the NASA \project{Astrophysics Data System} and the
+NASA Exoplanet Archive.
+The Archive is operated by the California Institute of Technology, under
+contract with NASA under the Exoplanet Exploration Program.
 This \paper\ includes data collected by the \kepler\ mission. Funding for the

### 2015-02-14 ms.tex
more results words

@@
 \newcommand{\paper}{\textsl{Article}}
+\newcommand{\papertwo}{\textsl{Paper II}}
 
@@
 maximize) over \phase\ and \duration\ subject to the constraint that
-$\TIC_\mathrm{const} > \TIC_\mathrm{var}$.
+$\TIC_\mathrm{const} > \TIC_\mathrm{var}$ and requiring that the signal have
+at least two observed transits.
 This results in a one-dimensional ``periodogram'' measuring the quality of
@@
 
-SOMEFIGURE shows the distribution of radius ratios and periods of candidates
-from our sample.
+SOMEFIGURE shows the observed distribution of planet candidates in our
+catalog.
+Using this and the detection efficiency function computed in the previous
+section, we compute the occurrence rate as a function of period by ignoring
+the measurement uncertainties and following the method described in the
+Appendix of \citet{dfm}.
+This function is shown in SOMEFIGURE and IS THIS CONSISTENT INTERESTING ETC?
+
+In \papertwo, we will characterize the stars for each of our candidates in
+detail but for now it's worth noting that about half (IS THIS TRUE) of our
+planet candidates are orbiting M-type stars.
+If this rate remains robust after stellar characterization and if these
+numbers are representative of the \KT\ yields in upcoming Campaigns, this
+will substantially increase the number of planets known to transit cool stars!
 

### 2015-02-14 ms.tex
photometry section tweaks

--- 2015-02-14 ms.tex
@@
 
-\section{Photometry}
+\section{Photometry and Eigen Light Curves}
 \sectlabel{phot}
@@
 The starting point for analysis is the raw pixel data.
-We download the full set of XXX target pixel files for \KT's Campaign 1 from
+We download the full set of \dfmtodo{XXX} target pixel files for \KT's Campaign 1 from
 MAST\footnote{\url{https://archive.stsci.edu/k2/}}.
-Then, we extract photometry using fixed circular apertures of varying sizes
+We extract photometry using fixed circular apertures of varying sizes
 centered on the predicted location of the target star based on the world
 coordinate system.
-For each time series, we used circular apertures ranging in radius from 0.5 to
+\dfmtodo{In detail, the apertures are only approximately circular; in detail each pixel
+gets a weight of unity if its center is in the circle, and zero otherwise.}
+For each target, we performed the photometry in a set of
+circular apertures ranging in radius from 0.5 to
 5 pixels (in steps of 0.5 pixels) and---following
@@
 with a 6 hour window.\footnote{Note that although we chose a specific
-aperture, photometry for every aperture size is available online at
+aperture for each star, photometry for this aperture and every other
+aperture size at which we easured is all available online at
 \dfmtodo{some URL}.}
@@
 ``correction'' or ``de-trending'' step based on measurements of the pointing
-motion of the spacecraft \citep{Vanderburg:2014, Aigrain:2015,
+of the spacecraft \citep{Vanderburg:2014, Aigrain:2015,
 Crossfield:2015}.
 In our analysis, we don't do any further preprocessing of the light curves
-because, as we describe in the next section, we simultaneously fit for the
+because, as we describe in the next section, we are going to simultaneously fit for the
 trends and the transit signals that we are searching for in the raw
@@
 effects are shared---with different signs and weights---by all the stars on
-the detector.
-To make use of this, the \pdc\ component of the \kepler\ pipeline
+the focal plane.
+To capitalize on this, the \pdc\ component of the \kepler\ pipeline
 removes any trends from the light curves that can be fit using a linear
@@
 This basis of trends was found by running Principal Component Analysis (PCA)
-on a large set of light curves and extracting the top few ($\sim 4$)
+on a large set of (filtered) light curves and extracting the top few ($\sim 4$)
 components \citep{pdc1, pdc2}.
-Similarly, we ran PCA on the full set of Campaign 1 light curves to determine
+Similarly, we ran PCA on the full set of our own generated \KT\ Campaign~1 light curves to determine
 a basis of representative trends but, unlike \pdc, we retain and use
-a large number of these components.
+a large number of these components ($150$).
 For clarity, we will refer to our basis as a set of ``eigen light curves''
-(ELCs) and the full set is made available online (SOMEURL).
-\Fig{pca} shows the top ten ELCs for Campaign 1.
+(ELCs) and the full set is made available online (\dfmtodo{SOMEURL}).
+The top \dfmtodo{ten} ELCs for Campaign~1 are shown in \Fig{pca}.
 

### 2015-02-14 ms.tex
typo

@@
 coordinate system.
-\dfmtodo{In detail, the apertures are only approximately circular; in detail each pixel
+\dfmtodo{In detail, the apertures are only approximately circular; each pixel
 gets a weight of unity if its center is in the circle, and zero otherwise.}

### 2015-02-14 ms.tex
joint transit model section tweaks

--- 2015-02-14 ms.tex
@@
 (ELCs) and the full set is made available online (\dfmtodo{SOMEURL}).
-The top \dfmtodo{ten} ELCs for Campaign~1 are shown in \Fig{pca}.
+The top ten ELCs for Campaign~1 are shown in \Fig{pca}.
 
@@
 other standard procedures is that no de-trending is necessary.
-Instead, we can fit for the noise (or trends) and signal simultaneously.
+Instead, we can fit for the noise (or trends) and exoplanet signals simultaneously.
 This is theoretically appealing because it will be more sensitive to low
 signal-to-noise transits.
-The main reason for this is that the signal is not exactly orthogonal to the
-systematics and any de-trending will over-fit; decreasing the amplitude of the
-signal and distorting its shape.
+The main reason for this is that the signal is never precisely orthogonal to the
+systematics and any de-trending will over-fit.
+This will, in turn, decrease the amplitude of the
+signal and distort its shape.
 In order to reduce this effect, most procedures use a very rigid model for
 the trends.
-For \KT, this has been implemented by asserting that the centroids contain
+For \KT, this rigidity has been implemented by
+effectively asserting that centroid measurements contain
 all of the information needed to describe the trends \citep{Vanderburg:2014,
 Aigrain:2015, Crossfield:2015}.
-In the \kepler\ pipeline, this is implemented by only allowing a small number
+In the \kepler\ pipeline, this is implemented by allowing only a small number
 of PCA components to contribute to the fit in the \pdc\ procedure.
 Instead, we will use a large number of ELCs---a very flexible model---and
-use a physically motivated method to avoid over-fitting.
+use a simultaneous fitting and marginalization to avoid over-fitting.
 
@@
 These are caused by things like pointing jitter, temperature variations, and
-other sources of PSF modulation and each one will be imprinted in the light
+other sources of PSF modulation.
+Each of these effects will be imprinted in the light
 curves of many stars with varying amplitudes and signs as a result of the
-varying flat field.
+varying flat field and PSF.
 Therefore, while it is hard to write down a physical generative model for the
@@
 using only empirical centroids \citep{Vanderburg:2014, Aigrain:2015,
-Crossfield:2015} but our more flexible model should capture the systematic
-effects more robustly.
+Crossfield:2015}, but our more flexible model should capture a wider range of
+effects, including those related to PSF and temperature.
 For example, \Fig{corr} shows the application of our model---with 150
@@
 excellent.
-If, however, we were to apply this model blindly to a light curve with
+If, however, we were to apply this systematics model alone (without a simultaneous fit
+of the exoplanet transit model) to a light curve with
 transits, we would be at risk of over-fitting and decreasing the amplitude of
@@
 
-To avoid over-fitting, in our pipeline we simultaneously fit for the transit
+In our pipeline we simultaneously fit for the transit
 signal and the trends using a rigid model for the signal and a relatively
-flexible model for the noise.
+flexible model for the systematic noise.
 Specifically, we model the light curve as being generated by linear
@@
 phase, and duration.
-The mathematical details are given in \app{math} but in summary, since the
+The mathematical details are given in \app{math}, but in summary, since the
 model is linear, we can analytically compute the likelihood
 function---conditioned on a specific period, phase, and duration---for the
-depth \emph{marginalized over the systematics model}.
+depth \emph{marginalizing out the systematics model}.
 The signal-to-noise of this depth measurement can then be used as a quality
@@
 This computation is expensive but, as described in the following sections, it
-is possible to scale the method to a \KT-scale dataset.
+is possible to scale the method to a \KT-size dataset.
 

### 2015-02-14 ms.tex
search tweaks

@@
 %    (or maybe do put in a few....)
+%  * ``percent'' (not \%) is a unit, as is ppm, so 5~percent.
 %  * that is all.
@@
 \newcommand{\eqlabel}[1]{\label{eq:#1}}
-\newcommand{\Sect}[1]{Section~\ref{sect:#1}}
+\newcommand{\sectionname}{Section}
+\newcommand{\Sect}[1]{\sectionname~\ref{sect:#1}}
 \newcommand{\sect}[1]{\Sect{#1}}
@@
 In our analysis, we don't do any further preprocessing of the light curves
-because, as we describe in the next section, we are going to simultaneously fit for the
+because, as we describe in the next \sectionname, we are going to simultaneously fit for the
 trends and the transit signals that we are searching for in the raw
@@
 of fit metric or candidate selection scalar.
-This computation is expensive but, as described in the following sections, it
+This computation is expensive but, as described in the following \sectionname s, it
 is possible to scale the method to a \KT-size dataset.
@@
 
-In principle, the search for transit signals simply requires evaluating the
+In principle, the search for transit signals simply requires evaluation of the
 model described above on a fine three-dimensional grid in period, phase, and
-duration, and then detecting high significance peaks in that space.
+duration, and then detection of high significance peaks in that space.
 In practice, this is computationally intractable for any grids of the
-required size.
+required size and resolution.
 Instead, we can compute the values on this grid approximately, but at very
@@
 We make the simplifying assumption that each transit enters this quantity
-independently because it is approximately satisfied for all but the shortest
-periods and it leads to a huge computational advantage.
+independently.
+This is not true; as we change beliefs about each transit, we change beliefs
+about the systematics model, which in turn affects the other transits.
+However, this simplifying assumption
+is approximately satisfied for all but the shortest
+periods and leads to a huge computational advantage.
 Under this assumption, this likelihood function can be rewritten as
@@
 Then, we can use these results as a look-up table to approximately evaluate
+the full likelihood in
 \eq{full-likelihood}.
 
-In the remainder of this section, we give more details about each step of the
-search procedure but in summary, it breaks into three main steps: linear
+In the remainder of this \sectionname, we give more details about each step of the
+search procedure.
+In summary, it breaks into three main steps: linear
 search, periodic search, and vetting.
@@
 over the model of the systematics) is a Gaussian with analytic amplitude $L$,
-mean $\bar{\depth}$, and variance $\delta\bar{\depth}^2$ derived in
+mean $\bar{\depth}$, and variance $\delta\bar{\depth}^2$, all derived and given in
 \app{math}.
-Therefore in the linear search, we save these three numbers for a
-two-dimensional grid in transit time $\transittime_l$ and duration
+In the linear search, we save these three numbers on a
+two-dimensional grid of transit times $\transittime_l$ and durations
 $\duration_k$.
-The transit time grid spans the duration of Campaign 1 with half hour spacing
+The transit time grid spans the full length of Campaign 1 with half hour spacing
 and we choose to only test three durations: 1.2, 2.4, and 4.8 hours.
@@
 and we choose $\alpha$ heuristically.
-For the K2 Campaign 1 dataset, we find that $\alpha \sim 1250$ leads to robust
+For the K2 Campaign 1 dataset, we find that $\alpha \sim 1250$ leads to reliable
 recovery of injected signals while still being fairly insensitive to false
@@
 Equations~(\ref{eq:periodic-depth}) and (\ref{eq:periodic-depth-uncert}).
-Figure SOMEFIGURE shows the signal-to-noise of the depth measurement as a
-function of period for SOMECANDIDATE.
+Figure \dfmtodo{SOMEFIGURE} shows the signal-to-noise of the depth measurement as a
+function of period for \dfmtodo{SOMECANDIDATE}.
 
@@
 and iterate the periodic search.
-Under our assumption of independent transits, this is equivalent to removing
-the sections of data that have a transit caused by the highest peak.
+This permits us to find second transiting planets in light curves in which
+we have already found a more prominent signal.
+Under our assumption of independent transits, this masking procedure is equivalent to removing
+the sections of data that have a transit caused by the exoplanet that produces the highest peak.
 For the purposes of this \paper, we iterate the periodic search until we find
@@
 an initial list of ZZZZ candidates.
-The vast majority of these signals are, of course, not induced by a
-transiting planet.
+The vast majority of these signals are not induced by a
+transiting planet; there are many false positives.
 Therefore to reduce the search space, we estimate the signal-to-noise of each
@@
 This is not the same criterion used to select the initial three peaks but we
-found that at this stage, it produced a more complete and pure sample.
+find that it produces a more complete and pure sample.
 A cut in this quantity can reject most variable stars and low signal-to-noise
 candidates that can't be reliably recovered from the data.
-Figure SOMEFIGURE shows the distribution of signal-to-noise for a set of
+Figure~\dfmtodo{SOMEFIGURE} shows the distribution of signal-to-noise for a set of
 injections and compares it to the distribution of false candidates that are
@@
 choose a threshold of 15.
-We also find that the signals with periods $\lesssim 4$ days are very
+We also find that the signals with periods $\lesssim 4$ days are strongly
 contaminated by false alarms.
 This might be because of the fact that our independence assumption
-(SOMEEQUATION) breaks down at these short periods.
+\dfmtodo{(SOMEEQUATION)} breaks down at these short periods.
 Therefore, we discard all signals with periods shorter than 4 days.
@@
 It should be possible to construct a more robust machine vetting algorithm
-that discards these samples without missing real transits (CITE SOME THINGS)
+that discards these samples without missing real transits \dfmtodo{(CITE SOME THINGS)}
 but for the purposes of this \paper, we simply inspect the light curve for
-each of the YYYY candidates \emph{by hand} to discard signals that are not
+each of the \dfmtodo{YYYY} candidates \emph{by hand} to discard signals that are not
 convincing transits.
-The results of this vetting can be seen online at SOMEURL.
-
-This vetting resulted in a list of ZZZZ transiting candidates.
+The results of this vetting can be seen online at \dfmtodo{SOMEURL}.
+
+This vetting resulted in a list of \dfmtodo{ZZZZ} transiting candidates.
 Many of these signals are due to astrophysical ``false positives'' like
 eclipsing binaries or blending.
-We address this effect in the following section and separate the list of
+We address this effect in the following \sectionname, where we separate the list of
 candidates into a list of astrophysical false positives and planet candidates.
@@
 transiting planets and eclipsing binaries.
-Ground-based surveys before \kepler\ often had a false-positive rate
-of 30-40\%. (because of shit?)
-In the primary \kepler\ mission, this number was significantly lower:
-the false positive rate was only 5-10\% \citep{Morton:2011}.
+Ground-based surveys prior to \kepler\ often had a false-positive rate
+of 30 to 40~percent. \dfmtodo{(because of shit?)}
+In the primary \kepler\ Mission, this number was significantly lower:
+the false positive rate was only 5 to 10~percent \citep{Morton:2011}.
 Such improvement was enabled by the relatively small pixels, stable
-pointing, and high precision of \kepler.
+pointing, and high precision of the \kepler\ spacecraft.
 In \kepler\ data, false positives can be reliably separated from
@@
 centroid of light during transit events with respect to the
-out-of-transit data (e.g. citation), variations in the depth of
-alternating transits (e.g. citation), and evidence for ellipsoidal
-variations between transits (e.g. citation).
+out-of-transit data \dfmtodo{(e.g. citation)}, variations in the depth of
+alternating transits \dfmtodo{(e.g. citation)}, and evidence for ellipsoidal
+variations between transits \dfmtodo{(e.g. citation)}.
 
@@
 This method has been shown to produce higher precision centroid measurements
-than center-of-light estimates (@HOGG: is this true? Is there a citation? MJ
-in prep?).
-Figure SOMEFIGURE shows the measure $x$ and $y$ pixel coordinate traces for
-SOMECANDIDATE.
+than center-of-light estimates (Vakili \etal, in preparation).
+\dfmtodo{Figure SOMEFIGURE shows the measure $x$ and $y$ pixel coordinate traces for
+SOMECANDIDATE.}
 Much like the photometry, this signal is dominated by the rigid body motion
@@
 In practice, the precision of the centroid measurements isn't sufficient to
-robustly reject many candidates but of the list of 100 (RIGHT NUMBER), two
-candidates---EPIC AAA and BBB---have offsets large enough that we remove them
+robustly reject many candidates but of the list of \dfmtodo{100 (RIGHT NUMBER)}, two
+candidates---\dfmtodo{EPIC AAA and BBB}---have offsets large enough that we remove them
 from our final catalog.
-Figure SOMEFIGURE shows the distribution of centroid offsets across the full
+\dfmtodo{Figure SOMEFIGURE} shows the distribution of centroid offsets across the full
 catalog.

### 2015-02-14 ms.tex
updated EB table and discussion

--- 2015-02-14 ms.tex
@@
 discover transit signals.
-We apply this method to the full Campaign 1 dataset and report a list of XXX
-planet candidates transiting YYY stars.
+We apply this method to the full Campaign 1 dataset and report a list of 38
+planet candidates transiting 33 stars.
 For all planet candidates, we present posterior distributions on the
@@
 \KT\ light curves.
-Finally, in \sect{results}, we present a catalog of XXXX planet candidates
-orbiting WWWW stars---and a supplementary list of YYYY eclipsing binary
+Finally, in \sect{results}, we present a catalog of 38 planet candidates
+orbiting 33 stars---and a supplementary list of YYYY eclipsing binary
 candidates---in the publicly available \KT\ Campaign 1 dataset.
@@
 The starting point for analysis is the raw pixel data.
-We download the full set of \dfmtodo{XXX} target pixel files for \KT's Campaign 1 from
-MAST\footnote{\url{https://archive.stsci.edu/k2/}}.
+We download the full set of 21,703 target pixel files for \KT's Campaign 1
+from MAST\footnote{\url{https://archive.stsci.edu/k2/}}.
 We extract photometry using fixed circular apertures of varying sizes
@@
 components \citep{pdc1, pdc2}.
-Similarly, we ran PCA on the full set of our own generated \KT\ Campaign~1 light curves to determine
-a basis of representative trends but, unlike \pdc, we retain and use
-a large number of these components ($150$).
+Similarly, we ran PCA on the full set of our own generated \KT\ Campaign~1
+light curves to determine a basis of representative trends but, unlike \pdc,
+we retain and use a large number of these components ($150$).
 For clarity, we will refer to our basis as a set of ``eigen light curves''
@@
 The periodic search procedure returned three signals per target so this gave
-an initial list of ZZZZ candidates.
+an initial list of 65,109 candidates.
 The vast majority of these signals are, of course, not induced by a
@@
 but for the purposes of this \paper, we simply inspect the light curve for
-each of the YYYY candidates \emph{by hand} to discard signals that are not
+each of the 741 candidates \emph{by hand} to discard signals that are not
 convincing transits.
@@
 
-This vetting resulted in a list of ZZZZ transiting candidates.
+This vetting resulted in a list of 101 candidate transit signals.
 Many of these signals are due to astrophysical ``false positives'' like
@@
 in the original \kepler\ mission where this effect was generally measured
-using difference imaging (cite Howell).
+using difference imaging (cite).
 
@@
 In practice, the precision of the centroid measurements isn't sufficient to
-robustly reject many candidates but of the list of 100 (RIGHT NUMBER), two
-candidates---EPIC AAA and BBB---have offsets large enough that we remove them
-from our final catalog.
+robustly reject many candidates but two candidates---EPIC 201202105 and EPIC
+201632708---have offsets large enough that we remove them from our final
+catalog.
 Figure SOMEFIGURE shows the distribution of centroid offsets across the full
@@
 
-After running the 21XXX light curves through our full pipeline, we end up with
-XXXX TCEs \dfmtodo{change this name} and after hand vetting by the two first
-authors of this \paper, we are left with YYYY convincing transiting
-candidates.
-We choose to separate this list into two tables: planet candidates
-(\tab{cand}) and eclipsing binary candidates (\tab{eb}).
-For our purposes, we define an binary candidate as any system where we can
-find a secondary eclipse by visual inspection but in most cases, the
-secondary eclipse is also detected as a smaller transit signal at the same
-period as the primary.
-In this dataset, we discover ZZZ planet candidates around WWW stars.
-Two of these were previously published \citep{Crossfield:2015} but, to our
-knowledge, the remaining list is currently unpublished.
+Out of the 21,703 Campaign 1 light curves, our pipeline returns 741 signals
+that pass the signal-to-noise and period cuts.
+After hand vetting by the two first authors, this list is reduced to 101
+convincing astrophysical transit candidates.
+Of these, 38 signals---in 33 light curves---have no visible secondary
+eclipse and these planet candidates are listed in \tab{cand}.
+Two were previously published \citep{Crossfield:2015} but, to our knowledge,
+the remaining list is currently unpublished.
 The third planet published by \citet{Crossfield:2015} is found as the third
@@
 
-For the binaries, we simply list the period, phase, and depth determined by
-the search algorithm but for the planet candidates, we perform a full physical
-transit fit to the light curve.
+The remaining signals are caused by eclipsing binaries.
+In most cases, the search reports the secondary eclipse as a candidate and in
+a few very high signal-to-noise cases, the period reported by the pipeline is
+incorrect and multiple candidates correspond to the same transit.
+After accounting for these by hand, we find 18 eclipsing binary candidates
+and list them in \tab{eb} along with the period, phase, and depth reported by
+the pipeline.
+It is important to note that the choices made in the search were
+heuristically tuned to find planets, not binaries, so this list should not be
+considered complete or exhaustive, especially at short orbital periods.
+
+For the planet candidates, we perform a full physical transit fit to the light
+curve.
 To do this fit, we use Markov Chain Monte Carlo \citep[MCMC;][]{emcee} to
@@
 \caption{%
-Probable binaries.
+Probable binaries. \
+$^\mathrm{a}$ The period for EPIC 201161715 was estimated using the secondary
+eclipses since there is only a single primary transit.
 \tablabel{eb}}

### 2015-02-14 ms.tex

--- 2015-02-14 ms.tex
@@
 The periodic search procedure returned three signals per target so this gave
-an initial list of ZZZZ candidates.
-The vast majority of these signals are not induced by a
-transiting planet; there are many false positives.
+an initial list of 65,109 candidates.
+The vast majority of these signals are not induced by a transiting planet;
+there are many false positives.
 Therefore to reduce the search space, we estimate the signal-to-noise of each
@@
 but for the purposes of this \paper, we simply inspect the light curve for
-each of the \dfmtodo{YYYY} candidates \emph{by hand} to discard signals that are not
+each of the 741 candidates \emph{by hand} to discard signals that are not
 convincing transits.
@@
 
-This vetting resulted in a list of \dfmtodo{ZZZZ} transiting candidates.
+This vetting resulted in a list of 101 candidate transit signals.
 Many of these signals are due to astrophysical ``false positives'' like
@@
 In practice, the precision of the centroid measurements isn't sufficient to
-robustly reject many candidates but of the list of \dfmtodo{100 (RIGHT NUMBER)}, two
-candidates---\dfmtodo{EPIC AAA and BBB}---have offsets large enough that we remove them
-from our final catalog.
-\dfmtodo{Figure SOMEFIGURE} shows the distribution of centroid offsets across the full
+robustly reject many candidates but two candidates---EPIC 201202105 and EPIC
+201632708---have offsets large enough that we remove them from our final
+catalog.
+Figure SOMEFIGURE shows the distribution of centroid offsets across the full
 catalog.

### 2015-02-15 ms.tex
few tweaks

@@
 To test the performance and detection efficiency of our method, we conducted a
-suite of XXXX injection and recovery tests, this is the result of 5 tests per
-star.
+suite of \dfmtodo{XXXX} injection and recovery tests, five tests per
+target star.
 For each test, we inject the signal from a realistic planetary system into the
-raw aperture photometry of a random target and run the resulting light curve
-through the full pipeline.
+raw aperture photometry of a random target and run the resulting injected light curve
+through the full pipeline (except the manual vetting).
 If the search returns a planet candidate---passing all of the same cuts as we
 apply in the main search---with period and reference transit time within
-HOWMANY days of the injected signal, we count that injection as recovered.
-The detection efficiency of the search is approximately given by the fraction
+\dfmtodo{HOWMANY~days} of the injected signal, we count that injection as recovered.
+The detection efficiency of the search is given approximately by the fraction
 of recovered injections as a function of the relevant parameters.

### 2015-02-15 ms.tex
a few new figures
dfmtodo issues

@@
 % TO DOS
-\newcommand{\todo}[3]{{\color{#2} \emph{#1} TODO: #3}}
+\newcommand{\todo}[3]{{\color{#2}\emph{#1}: #3}}
 \newcommand{\dfmtodo}[1]{\todo{DFM}{red}{#1}}
@@
 properties of each system based strictly on the transit observables.
-We also present a list of ZZZ candidate eclipsing binary systems.
+We also present a list of \dfmtodo{ZZZZ} candidate eclipsing binary systems.
 
@@
 Finally, in \sect{results}, we present a catalog of 38 planet candidates
-orbiting 33 stars---and a supplementary list of YYYY eclipsing binary
+orbiting 33 stars---and a supplementary list of \dfmtodo{YYYY} eclipsing binary
 candidates---in the publicly available \KT\ Campaign 1 dataset.
@@
 marginalized out).
-By this method, we find XXX new exoplanets, which we have vetted by ZZZ
+By this method, we find \dfmtodo{XXXX} new exoplanets, which we have vetted by \dfmtodo{ZZZZ}
 method and characterized by probabilistic modeling.
@@
 \begin{center}
-\includegraphics{figures/depth_s2n.pdf}
+\includegraphics{figures/de-trended.pdf}
 \end{center}
 \caption{%
-The signal-to-noise of the transit depth as a function of period for the same
-signal as in \fig{periodic}.
-The correct injected period is indicated by the vertical green line.
-\figlabel{depth-s2n}}
+\figlabel{de-trended}}
+\end{figure}
+
+\begin{figure}[p]
+\begin{center}
+\includegraphics[width=0.5\textwidth]{figures/centroid.pdf}
+\includegraphics[width=0.5\textwidth]{figures/centroid-2.pdf}
+\end{center}
+\caption{%
+\figlabel{centroid}}
+\end{figure}
+
+\begin{figure}[p]
+\begin{center}
+\includegraphics{figures/folded.pdf}
+\end{center}
+\caption{%
+\figlabel{folded}}
 \end{figure}

### 2015-02-15 ms.tex
consistency, todo typography, little crap

@@
 discover transit signals.
-We apply this method to the full Campaign 1 dataset and report a list of 38
+We apply this method to the full Campaign~1 dataset and report a list of 38
 planet candidates transiting 33 stars.
@@
 orbiting 33 stars---and a supplementary list of \dfmtodo{YYYY} eclipsing binary
-candidates---in the publicly available \KT\ Campaign 1 dataset.
+candidates---in the publicly available \KT\ Campaign~1 dataset.
 
@@
 The starting point for analysis is the raw pixel data.
-We download the full set of 21,703 target pixel files for \KT's Campaign 1
+We download the full set of 21,703 target pixel files for \KT's Campaign~1
 from MAST\footnote{\url{https://archive.stsci.edu/k2/}}.
@@
 $\duration_k$.
-The transit time grid spans the full length of Campaign 1 with half hour spacing
+The transit time grid spans the full length of Campaign~1 with half hour spacing
 and we choose to only test three durations: 1.2, 2.4, and 4.8 hours.
@@
 and we choose $\alpha$ heuristically.
-For the K2 Campaign 1 dataset, we find that $\alpha \sim 1250$ leads to reliable
+For the K2 Campaign~1 dataset, we find that $\alpha \sim 1250$ leads to reliable
 recovery of injected signals while still being fairly insensitive to false
@@
 catalog.
-Figure SOMEFIGURE shows the distribution of centroid offsets across the full
+Figure~\dfmtodo{SOMEFIGURE} shows the distribution of centroid offsets across the full
 catalog.
@@
 {\item Draw the number of transiting planets based on the observed
-multiplicity distribution of KOIs (CITE).}
+multiplicity distribution of KOIs (\dfmtodo{CITE}).}
 
@@
 
-Out of the 21,703 Campaign 1 light curves, our pipeline returns 741 signals
+Out of the 21,703 Campaign~1 light curves, our pipeline returns 741 signals
 that pass the signal-to-noise and period cuts.
@@
 
-SOMEFIGURE shows the observed distribution of planet candidates in our
+Figure~\dfmtodo{SOMEFIGURE} shows the observed distribution of planet candidates in our
 catalog.
@@
 Appendix of \citet{dfm}.
-This function is shown in SOMEFIGURE and IS THIS CONSISTENT INTERESTING ETC?
+This function is shown in Figure \dfmtodo{SOMEFIGURE and IS THIS CONSISTENT INTERESTING ETC?}
 
 In \papertwo, we will characterize the stars for each of our candidates in
-detail but for now it's worth noting that about half (IS THIS TRUE) of our
+detail but for now it's worth noting that about half \dfmtodo{(IS THIS TRUE?)} of our
 planet candidates are orbiting M-type stars.
 If this rate remains robust after stellar characterization and if these
-numbers are representative of the \KT\ yields in upcoming Campaigns, this
+numbers are representative of the yields in upcoming \KT\ Campaigns, this
 will substantially increase the number of planets known to transit cool stars!
@@
 The flexible systematics model we employ is a 150-parameter linear combination of PCA components
-derived from the full set of 20,000 stellar lightcurves.
+derived from the full set of 21,703 stellar lightcurves.
 That is, it presumes that the systematics afflicting each star are shared in
@@
 The top 10 eigen light curves (ELCs) generated by running principal component
-analysis on all the aperture photometry from Campaign 1.
+analysis on all the aperture photometry from Campaign~1.
 \figlabel{pca}}

### 2015-02-15 ms.tex
performance section tweaks

@@
 To test the performance and detection efficiency of our method, we conducted a
-suite of \dfmtodo{XXXX} injection and recovery tests, five tests per
-target star.
+suite of injection and recovery tests, five per
+star for all 21,703 target stars.
 For each test, we inject the signal from a realistic planetary system into the
@@
 If the search returns a planet candidate---passing all of the same cuts as we
-apply in the main search---with period and reference transit time within
+apply in the main search (except the manual vetting)---with period and reference transit time within
 \dfmtodo{HOWMANY~days} of the injected signal, we count that injection as recovered.
@@
 \begin{enumerate}
-
 {\item Draw the number of transiting planets based on the observed
 multiplicity distribution of KOIs (\dfmtodo{CITE}).}
-
 {\item Sample---from the distributions listed in
@@
 periapsis.}
-
 {\item Based on the chosen physical parameters, simulate the light curve,
@@
 kipping-int}, and multiply it into the raw aperture photometry.}
-
 \end{enumerate}
@@
 period.
-We should, of course, also process the results of the injection tests by hand
-to ensure that our measurements of detection efficiency aren't biased by this
+We should, of course, also vet the results of the injection tests by hand
+to ensure that our measurements of detection efficiency aren't biased by the
+hand-vetting
 step but, since we chose to limit our sample to very high signal-to-noise
@@
 Any estimates of the false alarm rate will, however, be affected by this
-negligence but we leave a treatment of this for future discussion.
+negligence but we leave a treatment of this for future work.
 
@@
 the eccentricity distribution of planets and it is marginalized over the
-distribution of stellar parameters.
+empirical distribution of stellar parameters.
 It is possible to relax this assumption and apply different distributions by
@@
 over the same range of periods---as a function of stellar magnitude in the
-\kepler\ bandpass as reported in the EPIC.
+\kepler\ bandpass as reported in the EPIC (\dfmtodo{CITATION NEEDED?}).
 

### 2015-02-15 ms.tex
results section tweaks

@@
 Of these, 38 signals---in 33 light curves---have no visible secondary
-eclipse and these planet candidates are listed in \tab{cand}.
-Two were previously published \citep{Crossfield:2015} but, to our knowledge,
+eclipse and are deemed planet candidates.
+These planet candidates are listed in \tab{cand}.
+Two (\dfmtodo{give names here})
+were previously published \citep{Crossfield:2015} but, to our knowledge,
 the remaining list is currently unpublished.
@@
 radii and longer periods even with the existing dataset.
+
+\dfmtodo{Didn't Charbonneau show some K2 planet at NYU?
+Is that in our list and does it need to be mentioned or discussed?
+Also, what about the planet we were shown by Vandenburg, private communication?}
 
@@
 In this fit, we continue to model the trends in the data as a linear
-combination of 150 ELCs but, at this point, we combine this with a realistic
+combination of the 150 ELCs but, at this point, we combine this with a realistic
 light curve model \citet{ma, kipping-ld}.

### 2015-02-15 ms.tex
no etal in author list

@@
     Dun~Wang\altaffilmark{\nyu},
-    Bernhard~Sch\"olkopf\altaffilmark{\mpis},
-    \etal
+    Bernhard~Sch\"olkopf\altaffilmark{\mpis}
 }

### 2015-02-15 ms.tex
tweak

@@
 If this rate remains robust after stellar characterization and if these
-numbers are representative of the yields in upcoming \KT\ Campaigns, this
+numbers are representative of the yields in upcoming \KT\ Campaigns, the
+\KT\ Mission
 will substantially increase the number of planets known to transit cool stars!

### 2015-02-15 ms.tex
todo marks in discussion; acks

@@
 
+\dfmtodo{
 To use these distributions to characterize the properties of specific systems,
@@
 Perhaps give a specific example here with some detailed discussion or math.
+}
 
@@
 
+\dfmtodo{
 Most importantly, perhaps, the machine and hand vetting leave much to be desired...
 list some deficiencies of the vetting.
-
+}
+
+\dfmtodo{
 The completeness and false-positive assessment could be vastly improved...
@@
 rate for the non-astrophysical FPs.)
-
+}
+
+\dfmtodo{
 We have not attempted to do any kind of populations analysis...
 but presumably \KT\ data will rock this.  In what ways?
+}
 
@@
 It is a pleasure to thank
-Andrew Vanderburg (Harvard),
-Ruth Angus (Oxford), Tom Barclay (Ames), \etal
+Ruth Angus (Oxford),
+Tom Barclay (Ames), and
+Andrew Vanderburg (Harvard)
 for helpful contributions to the ideas and code presented here.

### 2015-02-15 ms.tex
EPIC notes

@@
 over the same range of periods---as a function of stellar magnitude in the
-\kepler\ bandpass as reported in the EPIC (\dfmtodo{CITATION NEEDED?}).
+\kepler\ bandpass as reported in the Ecliptic Plane Input Catalog 
+(EPIC\footnote{http://archive.stsci.edu/k2/epic.pdf})
 
@@
 Also, what about the planet we were shown by Vandenburg, private communication?}
+
+(Note: C1 data came out the week between Christmas and New Years, so Charbonneau 
+didn't show anything from C1. Based on when he came down to visit you guys, it was
+very likely Andrew's HIP 116454 he showed).
 

### 2015-02-15 ms.tex
citing previous serches

--- 2015-02-15 ms.tex
@@
 properties of each system based strictly on the transit observables.
-We also present a list of \dfmtodo{ZZZZ} candidate eclipsing binary systems.
+We also present a list of 18 candidate eclipsing binary systems.
 
@@
 
-The \kepler\ Mission (cite something) has been incredibly successful at
-finding transiting exoplanets in the light curves of stars (cite something).
+The \kepler\ Mission was incredibly successful at finding transiting
+exoplanets in the light curves of stars.
 The Mission has demonstrated that it is possible to routinely measure signals
@@
 data \citep[for example,][]{pdc1, pdc2, arc, dun} but they have yet to be
-generalized to be applicable to \KT.
+generalized to \KT.
 
@@
 curves.
-We assume that the trends in the observed light curves in each star due to
-spacecraft motion are shared by other stars; the systematic effects are
-modeled as sums of stars.
-We reduce the dimensionality by running PCA on stellar light curves
-to obtain the dominant modes.
+We assume that the dominant trends in the observed light curves in each star
+are caused by the spacecraft and are, therefore, shared with other stars.
+We reduce the dimensionality by running PCA on stellar light curves to obtain
+the dominant modes.
 The search for planets proceeds by modeling the data as a linear combination of
 150 of these basis vectors and a transit model.
-Our method builds on the ideas behind previous data-driven de-trending procedures
-such as the \kepler\ pipeline pre-search data conditioning \citep[\pdc;][]{pdc1, pdc2},
-but (because of our simultaneous fitting approach) we can use a
-much more flexible systematics model without worrying about over-fitting.
+Our method builds on the ideas behind previous data-driven de-trending
+procedures such as the \kepler\ pipeline pre-search data conditioning
+\citep[\pdc;][]{pdc1, pdc2}, but (because of our simultaneous fitting
+approach) we can use a much more flexible systematics model without worrying
+about over-fitting.
 
@@
 the upcoming \tess\ mission \citep{Ricker:2014}.
-\tess\ will feature pointing precision of $\sim 3$ arcseconds (cite), similar
-to the level of pointing drift with \KT.
+\tess\ will feature pointing precision of $\sim 3$ arcseconds
+\dfmtodo{(cite)}, similar to the level of pointing drift with \KT.
 Moreover, the typical star will be only observed for one month at a time, and
@@
 planetary systems.
-These planets, especially when they orbit bright or late-type
-stars, will be useful targets for ground-based and space-based follow-up, both
-for current facilities and those planned in the near future such as \jwst.
+These planets, especially when they orbit bright or late-type stars, will be
+useful targets for ground-based and space-based follow-up, both for current
+facilities and those planned in the near future such as \jwst.
 They will also deliver input data for next-generation population inferences
@@
 \citep[for example,][]{dressing}.
+
+This project follows in the tradition of independently implemented transit
+search algorithms applied publicly available datasets \citep[such
+as][]{petigura1, petigura2, roberto, dressing}.
+These efforts have been hugely successful especially in the field of exoplanet
+population inference because, thanks to their relative simplicity, the
+efficiency and behavior of these pipelines can be quantified empirically.
+The work described in this \paper\ is built on many of the same principles as
+the previous projects built for studying \kepler\ data but our main
+contribution is a framework for including a model of the systematic trends
+into the search. \dfmtodo{blah}
 
@@
 Finally, in \sect{results}, we present a catalog of 38 planet candidates
-orbiting 33 stars---and a supplementary list of \dfmtodo{YYYY} eclipsing binary
+orbiting 33 stars---and a supplementary list of 18 eclipsing binary
 candidates---in the publicly available \KT\ Campaign~1 dataset.
@@
 over the same range of periods---as a function of stellar magnitude in the
-\kepler\ bandpass as reported in the EPIC (\dfmtodo{CITATION NEEDED?}).
+\kepler\ bandpass as reported in the EPIC \citep{epic}.
 
@@
 These planet candidates are listed in \tab{cand}.
-Two (\dfmtodo{give names here})
-were previously published \citep{Crossfield:2015} but, to our knowledge,
-the remaining list is currently unpublished.
+The two candidates transiting EPIC 201367065 were previously published
+\citep{Crossfield:2015} but, to our knowledge, the remaining list is currently
+unpublished.
 The third planet published by \citet{Crossfield:2015} is found as the third
@@
 
-\dfmtodo{Didn't Charbonneau show some K2 planet at NYU?
-Is that in our list and does it need to be mentioned or discussed?
-Also, what about the planet we were shown by Vandenburg, private communication?}
+% \dfmtodo{Didn't Charbonneau show some K2 planet at NYU?  Is that in our list
+% and does it need to be mentioned or discussed?  Also, what about the planet we
+% were shown by Vandenburg, private communication?}
 
@@
 
-Figure~\dfmtodo{SOMEFIGURE} shows the observed distribution of planet candidates in our
-catalog.
+Figure~\dfmtodo{SOMEFIGURE} shows the observed distribution of planet
+candidates in our catalog.
 Using this and the detection efficiency function computed in the previous
@@
 Appendix of \citet{dfm}.
-This function is shown in Figure \dfmtodo{SOMEFIGURE and IS THIS CONSISTENT INTERESTING ETC?}
+This function is shown in Figure \dfmtodo{SOMEFIGURE and IS THIS CONSISTENT
+INTERESTING ETC?}
 

### 2015-02-15 ms.tex
words in the intro

@@
 the previous projects built for studying \kepler\ data but our main
-contribution is a framework for including a model of the systematic trends
-into the search. \dfmtodo{blah}
+intellectual contribution is a computationally tractable framework for
+simultaneously fitting for the trends and the transit signal even when
+searching for planets.
 
@@
 over the same range of periods---as a function of stellar magnitude in the
-\kepler\ bandpass as reported in the EPIC \citep{epic}.
+\kepler\ bandpass as reported in the Ecliptic Plane Input Catalog
+(EPIC\footnote{http://archive.stsci.edu/k2/epic.pdf}).
 
@@
 
+% (Note: C1 data came out the week between Christmas and New Years, so Charbonneau
+% didn't show anything from C1. Based on when he came down to visit you guys, it was
+% very likely Andrew's HIP 116454 he showed).
+
+% That's correct. Everyone except for Hogg knows that so I don't think that we
+% need to say anything here :-)
+
 The remaining signals are caused by eclipsing binaries.
@@
 In this fit, we continue to model the trends in the data as a linear
-combination of the 150 ELCs but, at this point, we combine this with a realistic
-light curve model \citet{ma, kipping-ld}.
+combination of the 150 ELCs but, at this point, we combine this with a
+realistic light curve model \citet{ma, kipping-ld}.
 Even though we have no constraints on the stellar parameters, we also sample

### 2015-02-15 ms.tex
tweaks to photometry

@@
 from MAST\footnote{\url{https://archive.stsci.edu/k2/}}.
-We extract photometry using fixed circular apertures of varying sizes
-centered on the predicted location of the target star based on the world
-coordinate system.
-\dfmtodo{In detail, the apertures are only approximately circular; each pixel
-gets a weight of unity if its center is in the circle, and zero otherwise.}
-For each target, we performed the photometry in a set of
-circular apertures ranging in radius from 0.5 to
-5 pixels (in steps of 0.5 pixels) and---following
-\citet{Vanderburg:2014}---chose the aperture size that resulted in the
-smallest CDPP \citep{cdpp}
-with a 6 hour window.\footnote{Note that although we chose a specific
-aperture for each star, photometry for this aperture and every other
-aperture size at which we easured is all available online at
-\dfmtodo{some URL}.}
+We extract photometry using fixed approximately circular, binary apertures of
+varying sizes centered on the predicted location of the target star based on
+the world coordinate system.
+For each target, we use a set of apertures ranging in radius from 1 to 5
+pixels (in steps of 0.5 pixels).
+Following \citet{Vanderburg:2014}, we choose the aperture size with the
+minimum CDPP \citep{cdpp} with a 6 hour window.\footnote{Note that although we
+chose a specific aperture for each star, photometry for every aperture radius
+is available online at \dfmtodo{some URL}.}
 
@@
 ``correction'' or ``de-trending'' step based on measurements of the pointing
-of the spacecraft \citep{Vanderburg:2014, Aigrain:2015,
-Crossfield:2015}.
+of the spacecraft \citep{Vanderburg:2014, Aigrain:2015, Crossfield:2015}.
 In our analysis, we don't do any further preprocessing of the light curves
-because, as we describe in the next \sectionname, we are going to simultaneously fit for the
-trends and the transit signals that we are searching for in the raw
-photometric light curves.
+because, as we describe in the next \sectionname, we fit raw photometric light
+curves with a model that includes both the trends and the transit signal.
 

### 2015-02-15 ms.tex
removing cruft
words about single transits

@@
 
-% \dfmtodo{Didn't Charbonneau show some K2 planet at NYU?  Is that in our list
-% and does it need to be mentioned or discussed?  Also, what about the planet we
-% were shown by Vandenburg, private communication?}
-
-% (Note: C1 data came out the week between Christmas and New Years, so Charbonneau
-% didn't show anything from C1. Based on when he came down to visit you guys, it was
-% very likely Andrew's HIP 116454 he showed).
-
-% That's correct. Everyone except for Hogg knows that so I don't think that we
-% need to say anything here :-)
-
 The remaining signals are caused by eclipsing binaries.
@@
 marginalized out).
-By this method, we find \dfmtodo{XXXX} new exoplanets, which we have vetted by \dfmtodo{ZZZZ}
-method and characterized by probabilistic modeling.
-The candidates are listed in \dfmtodo{some table} and
-posterior distributions of planet candidate properties are available at
-\dfmtodo{thisurl}.
-
-The flexible systematics model we employ is a 150-parameter linear combination of PCA components
-derived from the full set of 21,703 stellar lightcurves.
+By this method, we find 38 transiting exoplanets, which we have vetted by both
+automatically and manually and characterized by probabilistic modeling.
+The candidates are listed in \tab{cand} and posterior distributions of planet
+candidate properties are available at \dfmtodo{thisurl}.
+
+The flexible systematics model we employ is a 150-parameter linear combination
+of PCA components derived from the full set of 21,703 stellar lightcurves.
 That is, it presumes that the systematics afflicting each star are shared in
@@
 
-The posterior distributions we release are given in terms of observational
-quantities (rather than physical quantities) and are specifically \emph{NOT}
-marginalized over stellar properties.
 In this work, we are agnostic about fundamental properties of the host stars.
@@
 on properties of the host star.
-
-\dfmtodo{
 To use these distributions to characterize the properties of specific systems,
-one should weight our samples by inferred stellar properties...
-Perhaps give a specific example here with some detailed discussion or math.
-}
-
-This is not the last time the \KT\ data will be searched!
-There are many heuristic choices and short-cuts made in this search.
-For example, the choice to work at 150 principal components is a choice
-driven more by computational feasibility than any model selection or
-utility optimization.
-The systematics model is good for spacecraft-induced variability, but not
-intrinsic stellar variability.
-The systematics model has no concept of a physical model of the spacecraft or
-the camera; that is, it makes little use of our prior information about how
-\KT\ images are generated physically.
-The search is performed with a box model and severe approximations are employed
-to make it fast.
-We don't consider planets (which must be abundant) on periods longer
-than those that would leave two transits within the \KT\ Campaign~1
-data set.
+one could re-weight our samples using a measurement of the inferred stellar
+properties.
+\dfmtodo{For example, let's do the Crossfield planets here. The results are
+consistent. Boom.}
+
+This project does not live in isolation and this is certainly not the last
+time the \KT\ data will be searched!
+There are other teams searching the \KT\ light curves for transiting planets
+(A.~Vanderburg, private comm.) and they are likely to find some planets that
+we did not and vice versa.
+We make many heuristic choices and short-cuts in this search.
+For example, the choice to work at 150 principal components was based on
+computational feasibility and qualitative tests on a handful of light curves
+instead of any real model selection or utility optimization.
+
+Another major limitation is that, in principle, the systematics model is
+designed to describe spacecraft-induced trends, but not intrinsic stellar
+variability.
+In practice, the method can still find planets around variable stars but a
+more sophisticated model should be more robust in this case.
+One appealing option would be to model the systematics as a Gaussian Process
+where the input parameters are both time and the same 150 ELCs.
+Interestingly, while this model isn't linear, the search and marginalization
+can still be executed efficiently---using optimized linear algebra algorithms
+\citep{fastgp}---inside the search loop.
 
@@
 }
+
+The catalog of planet candidates presented here includes only planets with
+periods longer than 4 days and at least two transits in the \KT\ Campaign~1
+footprint.
+This means that we are necessarily missing many planets with orbital periods
+outside  this range.
+In particular, planets with a single transit in the dataset must be
+abundant.
+These candidates are the most relevant for the study of planetary system
+formation and for statistical inference of the distribution of habitable zone
+exoplanets.
+What's more, given the observing strategy for \tess, where each field will
+only be contiguously observed for one month at a time, methods for finding and
+characterizing planets with a single transit are vital and the new \KT\ light
+curves are a perfect test bed.
 

### 2015-02-15 ms.tex
a few to dos

@@
 This might be because of the fact that our independence assumption
-\dfmtodo{(SOMEEQUATION)} breaks down at these short periods.
+(\eqalt{indtran}) breaks down at these short periods.
 Therefore, we discard all signals with periods shorter than 4 days.
@@
 If the search returns a planet candidate---passing all of the same cuts as we
-apply in the main search (except the manual vetting)---with period and reference transit time within
-\dfmtodo{HOWMANY~days} of the injected signal, we count that injection as recovered.
+apply in the main search (except the manual vetting)---with period and
+reference transit time within 12~hours of the injected signal, we count that
+injection as recovered.
 The detection efficiency of the search is given approximately by the fraction
@@
 {\item Draw the number of transiting planets based on the observed
-multiplicity distribution of KOIs (\dfmtodo{CITE}).}
+multiplicity distribution of KOIs \citep{kois}.}
 {\item Sample---from the distributions listed in

### 2015-02-15 ms.tex
new figures
removing two suspect candidates

@@
 discover transit signals.
-We apply this method to the full Campaign~1 dataset and report a list of 38
-planet candidates transiting 33 stars.
+We apply this method to the full Campaign~1 dataset and report a list of 36
+planet candidates transiting 31 stars.
 For all planet candidates, we present posterior distributions on the
@@
 \KT\ light curves.
-Finally, in \sect{results}, we present a catalog of 38 planet candidates
-orbiting 33 stars---and a supplementary list of 18 eclipsing binary
+Finally, in \sect{results}, we present a catalog of 36 planet candidates
+orbiting 31 stars---and a supplementary list of 18 eclipsing binary
 candidates---in the publicly available \KT\ Campaign~1 dataset.
@@
 convincing astrophysical transit candidates.
-Of these, 38 signals---in 33 light curves---have no visible secondary
+Of these, 36 signals---in 31 light curves---have no visible secondary
 eclipse and are deemed planet candidates.
@@
 marginalized out).
-By this method, we find 38 transiting exoplanets, which we have vetted by both
+By this method, we find 36 transiting exoplanets, which we have vetted by both
 automatically and manually and characterized by probabilistic modeling.
@@
 \begin{center}
-\includegraphics[width=\textwidth]{figures/completeness.pdf}
+\includegraphics{figures/completeness.pdf}
 \end{center}
@@
 \figlabel{completeness}}
+\end{figure}
+
+\begin{figure}[p]
+\begin{center}
+\includegraphics{figures/completeness-mag.pdf}
+\end{center}
+\caption{%
+\figlabel{completeness-mag}}
+\end{figure}
+
+\begin{figure}[p]
+\begin{center}
+\includegraphics{figures/candidates.pdf}
+\end{center}
+\caption{%
+\figlabel{candidates}}
 \end{figure}

### 2015-02-16 ms.tex
abstract tweaks

@@
     Timothy~D.~Morton\altaffilmark{\princeton},
-    Dun~Wang\altaffilmark{\nyu},
+    Dun~Wang\altaffilmark{\nyu}, \&
     Bernhard~Sch\"olkopf\altaffilmark{\mpis}
@@
 
-The photometry from the \KT\ extension of NASA's \kepler\ mission is
-afflicted by systematic effects caused by the relative imprecision of the
+Photometry of stars from the \KT\ extension of NASA's \kepler\ mission is
+afflicted by systematic effects caused by small (few-pixel) drifts in the
 telescope pointing and other spacecraft issues.
-We present a method for searching these light curves for evidence of
+We present a method for searching \KT\ light curves for evidence of
 exoplanets by simultaneously fitting for these systematics and the
@@
 This method is more computationally expensive than standard search algorithms
-but we demonstrate that it can be efficiently implemented and used to robustly
+but we demonstrate that it can be efficiently implemented and used to
 discover transit signals.
 We apply this method to the full Campaign~1 dataset and report a list of 36
-planet candidates transiting 31 stars.
+planet candidates transiting 31 stars, along with a completeness analysis
+based on artificial signal injections.
 For all planet candidates, we present posterior distributions on the

### 2015-02-16 ms.tex
MS changes, added Armstrong2014 to bib

@@
 Previous projects have developed methods to work with \KT\ data.
-\citet{Vanderburg:2014} extract aperture photometry from the pixel data
+Both \citet{Vanderburg:2014} and \citet{Armstrong:2014}
+extract aperture photometry from the pixel data
 and decorrelate with image centroid position, producing light curves for each
@@
 This project follows in the tradition of independently implemented transit
-search algorithms applied publicly available datasets \citep[such
+search algorithms applied to publicly available datasets \citep[such
 as][]{petigura1, petigura2, roberto, dressing}.
@@
 This intuition is also exploited by other methods that model the systematics
-using only empirical centroids \citep{Vanderburg:2014, Aigrain:2015,
+using only empirical centroids \citep{Vanderburg:2014, Armstrong:2014,
+Aigrain:2015,
 Crossfield:2015}, but our more flexible model should capture a wider range of
@@
 Therefore, we discard all signals with periods shorter than 4 days.
-After these cuts, we're left with 741 candidates that we then examine by hand.
+After these cuts, 741 candidates remain; we examine these signals by hand.
 The full list of peaks and their relevant meta data is available online at
@@
 This vetting resulted in a list of 101 candidate transit signals.
-Many of these signals are due to astrophysical ``false positives'' like
-eclipsing binaries or blending.
+Many of these signals are due to astrophysical ``false positives'' such as 
+eclipsing binary systems, either as the target star or as a background ``blend.''
 We address this effect in the following \sectionname, where we separate the list of
@@
 Ground-based surveys prior to \kepler\ often had a false-positive rate
-of 30 to 40~percent. \dfmtodo{(because of shit?)}
+of 30 to 40~percent. \dfmtodo{(because of shit?) Because of giant pixels.
+See references in Morton and Johnson intro, probably}
 In the primary \kepler\ Mission, this number was significantly lower:
@@
 in the original \kepler\ mission where this effect was generally measured
-using difference imaging (cite).
+using difference imaging \dfmtodo{(cite)}.
 
@@
 detail but for now it's worth noting that about half \dfmtodo{(IS THIS TRUE?)} of our
-planet candidates are orbiting M-type stars.
+planet candidates are orbiting stars selected for \KT\ as M-type stars.
 If this rate remains robust after stellar characterization and if these
@@
 \KT\ Mission
-will substantially increase the number of planets known to transit cool stars!
+will substantially increase the number of planets known to transit cool stars.
 

### 2015-02-16 ms.tex
captions

@@
 the upcoming \tess\ mission \citep{Ricker:2014}.
-\tess\ will feature pointing precision of $\sim 3$ arcseconds
-\dfmtodo{(cite)}, similar to the level of pointing drift with \KT.
+\tess\ will feature pointing precision of $\sim
+3$~arcseconds\footnote{\url{http://tess.gsfc.nasa.gov/documents/TESS_FactSheet_Oct2014.pdf}},
+similar to the level of pointing drift with \KT.
 Moreover, the typical star will be only observed for one month at a time, and
@@
 and we choose to only test three durations: 1.2, 2.4, and 4.8 hours.
-\Fig{linear} shows the mean transit depth $\bar{\depth}$ as a function of
-transit time \transittime\ for a light curve with an injected transit signal
-with transits at the times indicated by the vertical green bars.
-
-% The computational complexity of this step is $\mathcal{O}(M\,K^3)$ where $M$
-% is the number of points in the grid and $K$ is the number of data points.
+\Fig{linear} shows the maximum likelihood transit depth $\bar{\depth}$ as a
+function of transit time \transittime\ for the light curve of EPIC 201613023,
+a transiting planet candidate with a period of 8.3~days.
 
@@
 depth is constant.
-The variable depth likelihood is simply the product of amplitudes from the
+The variable depth likelihood is given by the product of amplitudes from the
 initial search
@@
 p_\mathrm{var}(\{\flux\}_n\,|\,\period,\,\phase,\,\duration) &=&
-\prod_{m=1}^{M(\period,\,\phase)} L_m \quad,
-\end{eqnarray}
-and the constant depth model is
+\prod_{m=1}^{M(\period,\,\phase)} L_m \quad.
+\end{eqnarray}
+Since the likelihood function for the depth at each transit time is known and
+Gaussian, the likelihood function for the depth under the periodic model can
+also be computed analytically; it is a product of Gaussian which itself is a
+Gaussian
 \begin{eqnarray}
@@
 \end{eqnarray}
-where the maximum likelihood depth is
+where the maximum likelihood depth, for the periodic model, is
 \begin{eqnarray}\eqlabel{periodic-depth}
@@
 \end{eqnarray}
-and the uncertainty on this depth is given by
+and the uncertainty is given by
 \begin{eqnarray}\eqlabel{periodic-depth-uncert}
@@
 likelihood because it is more flexible.
-Therefore, to compare these two models, we use the Bayesian Information
+Therefore, a formal model comparison is required to compete these two models
+against each other on equal footing.
+For computational simplicity and speed, we use the Bayesian Information
 Criterion (BIC).
@@
 \begin{eqnarray}
--\frac{1}{2}\,\BIC_\cdot &=&
-    \ln p_\cdot(\{\flux\}_n\,|\,\period,\,\phase,\,\duration)
-    - \frac{J}{2} \ln N
-\end{eqnarray}
-where the likelihood function is maximized, $J$ is an estimate of the model
-complexity and $N$ is the effective sample size.
-To emphasize that $J$ and $N$ are tuning parameters of the method, we
-redefine the BIC as the TIC
+-\frac{1}{2}\,\BIC &=&
+    \ln p(\{\flux\}_n\,|\,\period,\,\phase,\,\duration)
+    - \frac{K}{2} \ln N
+\end{eqnarray}
+where the likelihood function is evaluated at the maximum, $K$ is an estimate
+of the model complexity and $N$ is the effective sample size.
+To emphasize that $K$ and $N$ are tuning parameters of the method, we
+rewrite the BIC as something that we'll call the ``TIC''
 \begin{eqnarray}
-\TIC_\cdot &=&
-    \ln p_\cdot(\{\flux\}_n\,|\,\period,\,\phase,\,\duration) - \alpha
-\end{eqnarray}
-and we choose $\alpha$ heuristically.
-For the K2 Campaign~1 dataset, we find that $\alpha \sim 1250$ leads to reliable
-recovery of injected signals while still being fairly insensitive to false
-signals.
-
-To limit memory consumption, in the periodic search, we actually profile (or
-maximize) over \phase\ and \duration\ subject to the constraint that
+\TIC &=&
+    \ln p(\{\flux\}_n\,|\,\period,\,\phase,\,\duration) -
+        \frac{J\,\alpha}{2}
+\end{eqnarray}
+where $J$ is the number of allowed depths---one for the constant depth model
+and the number of transits for the variable depth model---and $\alpha$ is
+chosen heuristically.
+For the K2 Campaign~1 dataset, we find that $\alpha \sim 1240$ leads to
+reliable recovery of injected signals while still being fairly insensitive to
+false signals.
+
+To limit memory consumption, in the periodic search, we profile (or maximize)
+over \phase\ and \duration\ subject to the constraint that
 $\TIC_\mathrm{const} > \TIC_\mathrm{var}$ and requiring that the signal have
 at least two observed transits.
-This results in a one-dimensional ``periodogram'' measuring the quality of
-the fit as a function of period.
-To choose the ``best'' candidate signal, we found that the best quantity to
-select on was the signal-to-noise with which the depth was measured at a
-given period, $\depth/\sigma_\depth$, computed using
-Equations~(\ref{eq:periodic-depth}) and (\ref{eq:periodic-depth-uncert}).
-Figure \dfmtodo{SOMEFIGURE} shows the signal-to-noise of the depth measurement as a
-function of period for \dfmtodo{SOMECANDIDATE}.
+This yields a one-dimensional spectrum of the signal-to-noise of the depth
+measurement as a function of period using Equations~(\ref{eq:periodic-depth})
+and (\ref{eq:periodic-depth-uncert}) to compute $\depth/\sigma_\depth$ at
+each period.
+The result is a generalization of the \project{BLS} frequency spectrum
+\citep{bls} to a light curve model that includes both a transit and the
+trends.
+For example, \fig{periodic} shows the spectrum for a planet candidate
+transiting EPIC 201613023.
 
@@
 we have already found a more prominent signal.
-Under our assumption of independent transits, this masking procedure is equivalent to removing
-the sections of data that have a transit caused by the exoplanet that produces the highest peak.
+Under our assumption of independent transits, this masking procedure is
+equivalent to removing the sections of data that have a transit caused by the
+exoplanet that produces the highest peak.
 For the purposes of this \paper, we iterate the periodic search until we find
@@
 This will necessarily miss the smallest and longest period planets in systems
-with more than three transiting planets but given the precision---or lack
-thereof---of the current method, we deemed this number sufficient.
+with more than three transiting planets but given the conservative vetting in
+the next \sectionname, three peaks are sufficient to discover all the high
+signal-to-noise transits.
 
@@
 For each test, we inject the signal from a realistic planetary system into the
-raw aperture photometry of a random target and run the resulting injected light curve
-through the full pipeline (except the manual vetting).
+raw aperture photometry of a random target and run the resulting injected
+light curve through the full pipeline (except the manual vetting).
 If the search returns a planet candidate---passing all of the same cuts as we
 apply in the main search (except the manual vetting)---with period and
-reference transit time within 12~hours of the injected signal, we count that
+reference transit time within 6~hours of the injected signal, we count that
 injection as recovered.
@@
 \kepler\ bandpass as reported in the Ecliptic Plane Input Catalog
-(EPIC\footnote{http://archive.stsci.edu/k2/epic.pdf}).
+(EPIC\footnote{\url{http://archive.stsci.edu/k2/epic.pdf}}).
 
@@
 The 6-hour precision of this light curve is 31 ppm.
+Note that although we show a ``de-trended'' light curve to give a qualitative
+understanding of the model, this is not a product of the analysis.
+In this search for transits, \emph{the data are never de-trended}.
 \figlabel{corr}}
@@
 \caption{%
-The estimated transit depth as a function of transit time as computed in a
-linear search.
-This light curve has an injected signal with transits at the times indicated
-with green vertical lines.
+The maximum likelihood transit depth as a function of transit time as computed
+in the linear search of the light curve of EPIC 201613023.
+After the periodic search and vetting this target is found to have a planet
+candidate with a period of 8.3~days.
+The first transit occurs at 7.4~days on this plot.
 \figlabel{linear}}
@@
 \caption{%
-The periodogram for the same signal as in \fig{linear}.
-This plot was generated by the periodic search procedure.
-The true period is indicated by the vertical green line.
+The signal-to-noise spectrum as a function of period for the light curve of
+EPIC 201613023.
+This is the generalization of the \project{BLS} spectrum \citep{bls} to this
+simultaneous model of the transit and the systematic trends.
+To compute this spectrum, the results of the linear search (\fig{linear})
+were used as described in \sect{search}.
+The top peak (at a period of 8.3~days) is indicated with a green dot.
+Iterating the periodic search found no other transit signals above the
+signal-to-noise threshold.
 \figlabel{periodic}}

### 2015-02-16 ms.tex
centroid caption

@@
 It should be possible to construct a more robust machine vetting algorithm
-that discards these samples without missing real transits \dfmtodo{(CITE SOME THINGS)}
-but for the purposes of this \paper, we simply inspect the light curve for
-each of the 741 candidates \emph{by hand} to discard signals that are not
-convincing transits.
+that discards these samples without missing real transits but for the purposes
+of this \paper, we simply inspect the light curve for each of the 741
+candidates \emph{by hand} to discard signals that are not convincing transits.
 The results of this vetting can be seen online at \dfmtodo{SOMEURL}.
@@
 than center-of-light estimates (Vakili \etal, in preparation).
-\dfmtodo{Figure SOMEFIGURE shows the measure $x$ and $y$ pixel coordinate traces for
-SOMECANDIDATE.}
+\Fig{centroid} shows the measured $x$ and $y$ pixel coordinate traces for EPIC
+201613023.
 Much like the photometry, this signal is dominated by the rigid body motion
@@
 
+% \begin{figure}[p]
+% \begin{center}
+% \includegraphics{figures/de-trended.pdf}
+% \end{center}
+% \caption{%
+% \figlabel{de-trended}}
+% \end{figure}
+
 \begin{figure}[p]
 \begin{center}
-\includegraphics{figures/de-trended.pdf}
+\includegraphics[width=0.4\textwidth]{figures/centroid.pdf}
+\includegraphics[width=0.4\textwidth]{figures/centroid-2.pdf}
 \end{center}
 \caption{%
-\figlabel{de-trended}}
-\end{figure}
-
-\begin{figure}[p]
-\begin{center}
-\includegraphics[width=0.5\textwidth]{figures/centroid.pdf}
-\includegraphics[width=0.5\textwidth]{figures/centroid-2.pdf}
-\end{center}
-\caption{%
+The centroid motion for EPIC 201613023.
+\emph{Left:} The measured $x$ and $y$ pixel coordinates as a function of time.
+\emph{Right:} The pixel coordinates color-coded by time.
+As identified by \citet{Vanderburg}, the centroid motions fall in a slowly
+time variable locus.
+If the centroid coordinates in transit are inconsistent with the
+out-of-transit motions, the candidate is likely to be an astrophysical false
+positive.
 \figlabel{centroid}}

### 2015-02-16 ms.tex
fixing a reference
some fpp text

--- 2015-02-16 ms.tex
@@
 
-A major problem with any transit search is the potential confusion between
-transiting planets and eclipsing binaries.
+A major problem with any transit search is the potential confusion
+between transiting planets and stellar eclipsing binaries.  Of
+particular concern are grazing stellar eclipses or stellar eclipses
+that contribute only a small fraction of the total light in a target
+star's photometric aperture, thus display greatly diluted eclipse
+depths able to mimic the signals of small planets.
+
+Ground-based transit surveys have experienced false-positive rates
+well over 50\%.  For example, \citet{Latham:2009} reported eight
+eclipsing binaries and one transiting planet among the sample of
+transit candidates in one field of the Hungarian Automated Telescope
+Network transit search.  In fact, the follow-up process to try to rule
+out such astrophysical false positives is a large portion of the
+effort that goes into a transit survey
+\citep[e.g.,][]{Odonovan:2006,Almenara:2009,Poleski:2010}.
+
+Despite this large fraction of astrophysical false positives in
+ground-based surveys, the primary \kepler\ Mission saw a much lower
+false positive rate \citep{Morton:2011, Fressin:2013}, primarily due
+to two major factors.  First, the superior precision of
+the \kepler\ photometry enabled
+
 Ground-based surveys prior to \kepler\ often had a false-positive rate

### 2015-02-16 ms.tex

--- 2015-02-16 ms.tex
@@
 \emph{Right:} The pixel coordinates color-coded by time.
-As identified by \citet{Vanderburg}, the centroid motions fall in a slowly
-time variable locus.
+As identified by \citet{Vanderburg:2014}, the centroid motions fall in a
+slowly time variable locus.
 If the centroid coordinates in transit are inconsistent with the

### 2015-02-16 ms.tex
words and captions for hand vetting

--- 2015-02-16 ms.tex
@@
 
-This vetting resulted in a list of 101 candidate transit signals.
-Many of these signals are due to astrophysical ``false positives'' such as
-eclipsing binary systems, either as the target star or as a background ``blend.''
-We address this effect in the following \sectionname, where we separate the list of
+Although de-trended light curves are never used in the automated analysis of
+the data, when conditioned on a specific set of transit parameters, the model
+produces an estimate of what the light curve would look like in the absence
+of systematic effects.
+This prediction is one of the plots that we examine when vetting candidates
+by hand.
+For example, \fig{de-trended} shows the maximum likelihood light curve for
+EPIC 201613023 evaluated at the candidate period, phase, duration, and depth.
+Similarly, \fig{folded} shows the same prediction folded on the 8.3~day
+period of this candidate.
+
+After visually inspecting 741 signals, 101 candidate transits pass and are
+selected as astrophysical events.
+Many of these signals are due to ``false positives'' such as eclipsing binary
+systems, either as the target star or as a background ``blend.'' We address
+this effect in the following \sectionname, where we separate the list of
 candidates into a list of astrophysical false positives and planet candidates.
@@
 catalog.
-Figure~\dfmtodo{SOMEFIGURE} shows the distribution of centroid offsets across the full
-catalog.
 
@@
 
-% \begin{figure}[p]
-% \begin{center}
-% \includegraphics{figures/de-trended.pdf}
-% \end{center}
-% \caption{%
-% \figlabel{de-trended}}
-% \end{figure}
+\begin{figure}[p]
+\begin{center}
+\includegraphics{figures/de-trended.pdf}
+\end{center}
+\caption{%
+The maximum likelihood ``de-trended'' light curve for EPIC 201613023
+evaluated at the planet candidate's period, phase, duration, and depth.
+The transit times are indicated by the green ticks below the light curve.
+This Figure is only generated for qualitative hand vetting and in the search
+procedure, the model is always marginalized over any choices about the
+systematic trends.
+\figlabel{de-trended}}
+\end{figure}
+
+\begin{figure}[p]
+\begin{center}
+\includegraphics{figures/folded.pdf}
+\end{center}
+\caption{%
+The maximum likelihood prediction for the light curve of EPIC 201613023 (see
+also \fig{de-trended}) folded on the 8.3~day period of this planet candidate.
+The points are color-coded by time and the median \emph{a posteriori} transit
+model is overplotted as a black line.
+\figlabel{folded}}
+\end{figure}
 
@@
 \figlabel{centroid}}
-\end{figure}
-
-\begin{figure}[p]
-\begin{center}
-\includegraphics{figures/folded.pdf}
-\end{center}
-\caption{%
-\figlabel{folded}}
 \end{figure}

### 2015-02-16 ms.tex
more fpp text

--- 2015-02-16 ms.tex
@@
 ground-based surveys, the primary \kepler\ Mission saw a much lower
-false positive rate \citep{Morton:2011, Fressin:2013}, primarily due
-to two major factors.  First, the superior precision of
-the \kepler\ photometry enabled
+false positive rate of only 5-10\% \citep{Morton:2011, Fressin:2013},
+primarily due to two major factors.  First, the superior precision of
+the \kepler\ photometry enables detection of secondary stellar
+eclipses to a much lower level than ground-based surveys; and second,
+the relatively small pixels and stable pointing of the
+\kepler\ telescope has enabled the identification of many spatially
+distinct blended eclipsing binaries by means of detailed pixel-level
+analysis \citep{Bryson:2013}.
 

### 2015-02-16 ms.tex
addressing #21

--- 2015-02-16 ms.tex
@@
 \newcommand{\figref}[1]{\ref{fig:#1}}
-\newcommand{\Fig}[1]{Figure~\figref{#1}}
+\newcommand{\Fig}[1]{\figurename~\figref{#1}}
 \newcommand{\fig}[1]{\Fig{#1}}
@@
 We apply this method to the full Campaign~1 dataset and report a list of 36
-planet candidates transiting 31 stars, along with a completeness analysis
-based on artificial signal injections.
+planet candidates transiting 31 stars, along with a analysis of the pipeline
+performance and detection efficiency based on artificial signal injections
+and recoveries.
 For all planet candidates, we present posterior distributions on the
@@
 
-\Fig{completeness} shows the fraction of recovered signals as a function of
-the physical parameters of the injection and the magnitude of the star.
+\figurename s~\figref{completeness} and~\figref{completeness-mag} show the
+fraction of recovered signals as a function of the physical parameters of the
+injection and the magnitude of the star in the \kepler\ bandpass as reported
+in the Ecliptic Plane Input Catalog
+(EPIC\footnote{\url{http://archive.stsci.edu/k2/epic.pdf}}).
 As expected, the shallower transits at longer periods are recovered less
-robustly.
-It is worth noting that this figure is a two-dimensional projection (or
-marginalization) of a higher dimensional measurement.
-For example, this completeness map is conditioned on our assumptions about
-the eccentricity distribution of planets and it is marginalized over the
+robustly and all signals become harder to detect for fainter stars.
+It is worth noting that these \figurename s are projections (or
+marginalizations) of a higher dimensional measurement of the recovery rate as
+a function of all of the input parameters.
+For example, this detection efficiency map is conditioned on our assumptions
+about the eccentricity distribution of planets and it is marginalized over the
 empirical distribution of stellar parameters.
@@
 rate measurements).
-In \fig{completeness}, we also show the detection efficiency---marginalized
-over the same range of periods---as a function of stellar magnitude in the
-\kepler\ bandpass as reported in the Ecliptic Plane Input Catalog
-(EPIC\footnote{\url{http://archive.stsci.edu/k2/epic.pdf}}).
 
@@
 
-\begin{table}[p]
-\begin{center}
-\include{tab-eb}
-\end{center}
-\caption{%
-Probable binaries. \
-$^\mathrm{a}$ The period for EPIC 201161715 was estimated using the secondary
-eclipses since there is only a single primary transit.
-\tablabel{eb}}
-\end{table}
-
 \end{document}

### 2015-02-16 ms.tex
tdm edit

@@
 particular concern are grazing stellar eclipses or stellar eclipses
-that contribute only a small fraction of the total light in a target
-star's photometric aperture, thus display greatly diluted eclipse
-depths able to mimic the signals of small planets.
+that contribute only a small fraction of the total light in a
+photometric aperture, thus display greatly diluted eclipse depths able
+to mimic the signals of small planets.
 

### 2015-02-16 ms.tex
tdm edit

@@
 that contribute only a small fraction of the total light in a
-photometric aperture, thus display greatly diluted eclipse depths able
+photometric aperture, resulting in greatly diluted eclipse depths able
 to mimic the signals of small planets.

### 2015-02-16 ms.tex
completeness captions

--- 2015-02-16 ms.tex
@@
 the full chains are available electronically at \dfmtodo{some URL}.
-
-Figure~\dfmtodo{SOMEFIGURE} shows the observed distribution of planet
-candidates in our catalog.
-Using this and the detection efficiency function computed in the previous
-section, we compute the occurrence rate as a function of period by ignoring
-the measurement uncertainties and following the method described in the
-Appendix of \citet{dfm}.
-This function is shown in Figure \dfmtodo{SOMEFIGURE and IS THIS CONSISTENT
-INTERESTING ETC?}
+\fig{candidates} shows the observed distribution of planet candidates in the
+catalog.
 
 In \papertwo, we will characterize the stars for each of our candidates in
-detail but for now it's worth noting that about half \dfmtodo{(IS THIS TRUE?)} of our
-planet candidates are orbiting stars selected for \KT\ as M-type stars.
+detail but for now it's worth noting that many of the planet candidates are
+orbiting stars selected for \KT\ as M-type stars.
 If this rate remains robust after stellar characterization and if these
-numbers are representative of the yields in upcoming \KT\ Campaigns, the
-\KT\ Mission
-will substantially increase the number of planets known to transit cool stars.
+numbers are representative of the yields in upcoming \KT\ Campaigns, the \KT\
+Mission will substantially increase the number of planets known to transit
+cool stars.
 
@@
 \caption{%
+The detection efficiency of the search procedure as a function of the
+physical transit parameters computed empirically by
+injecting synthetic transit signals into the raw light curves and measuring
+the fraction that are successfully recovered.
+These tests were performed on the entire set of stars so these numbers are
+marginalized over all the stellar properties, including magnitude.
 \figlabel{completeness}}
@@
 \caption{%
+Like \fig{completeness}, the empirically measured detection efficiency of the
+search procedure as a function of stellar magnitude as reported by the EPIC.
+This never reaches 90~percent because these numbers are marginalized over the
+range of physical parameters shown in \fig{completeness}.
+Even for the brightest stars, the long period, small transits cannot be
+detected.
 \figlabel{completeness-mag}}

### 2015-02-16 ms.tex

@@
 particular concern are grazing stellar eclipses or stellar eclipses
-that contribute only a small fraction of the total light in a target
-star's photometric aperture, thus display greatly diluted eclipse
-depths able to mimic the signals of small planets.
+that contribute only a small fraction of the total light in a
+photometric aperture, resulting in greatly diluted eclipse depths able
+to mimic the signals of small planets.
 

### 2015-02-16 ms.tex
candidates captions

@@
 \caption{%
+The \emph{a posteriori} distribution of planet candidates in the catalog.
+The error bars indicate the 0.16 and 0.84 posterior sample quantiles for the
+radius ratios.
 \figlabel{candidates}}
@@
 \caption{%
-Candidates
+The catalog of planet candidates and their observable properties.
+These values and their uncertainties are derived from MCMC samplings and the
+numbers are computed as the 0.16, 0.5, and 0.84 posterior sample quantiles.
+\dfmtodo{RA/Dec coords.}
 \tablabel{cand}}

### 2015-02-16 ms.tex
adding Armstrong:2015 and tweaking EB discussion

@@
 properties of each system based strictly on the transit observables.
-We also present a list of 18 candidate eclipsing binary systems.
 
@@
 Finally, in \sect{results}, we present a catalog of 36 planet candidates
-orbiting 31 stars---and a supplementary list of 18 eclipsing binary
-candidates---in the publicly available \KT\ Campaign~1 dataset.
+orbiting 31 stars in the publicly available \KT\ Campaign~1 dataset.
 
@@
 
-The remaining signals are caused by eclipsing binaries.
+The remaining signals are caused by eclipsing binaries (EBs).
 In most cases, the search reports the secondary eclipse as a candidate and in
@@
 incorrect and multiple candidates correspond to the same transit.
-After accounting for these by hand, we find 18 eclipsing binary candidates
-and list them in \tab{eb} along with the period, phase, and depth reported by
-the pipeline.
-It is important to note that the choices made in the search were
-heuristically tuned to find planets, not binaries, so this list should not be
-considered complete or exhaustive, especially at short orbital periods.
+It is important to note, however, that the choices made in the search were
+heuristically tuned to find planets, not binaries, so our results are not
+complete or exhaustive, especially at short orbital periods.
+There are other methods specifically tuned to find EBs in \KT\
+\citep[such as][]{Armstrong:2014, Armstrong:2015} and these catalogs contain
+our full sample of EBs and more.
 

### 2015-02-16 ms.tex
adding some URLs

@@
 \newcommand{\pomega}{{\ensuremath{\omega}}}
+
+\newcommand{\datareleaseurl}{{\url{http://bbq.dfm.io/ketu}}}
 
@@
 chose a specific aperture for each star, photometry for every aperture radius
-is available online at \dfmtodo{some URL}.}
+is available online: \datareleaseurl.}
 
@@
 For clarity, we will refer to our basis as a set of ``eigen light curves''
-(ELCs) and the full set is made available online (\dfmtodo{SOMEURL}).
+(ELCs) and the full set is made available online\footnote{\datareleaseurl}.
 The top ten ELCs for Campaign~1 are shown in \Fig{pca}.
@@
 candidates that can't be reliably recovered from the data.
-Figure~\dfmtodo{SOMEFIGURE} shows the distribution of signal-to-noise for a set of
-injections and compares it to the distribution of false candidates that are
-proposed by the pipeline.
 To minimize contamination from false alarms but maximize our sensitivity, we
@@
 After these cuts, 741 candidates remain; we examine these signals by hand.
-The full list of peaks and their relevant meta data is available online at
-\dfmtodo{SOMEURL}.
+The full list of peaks and their relevant meta data is available online
+at\footnote{\datareleaseurl}.
 
@@
 candidates \emph{by hand} to discard signals that are not convincing transits.
-The results of this vetting can be seen online at \dfmtodo{SOMEURL}.
+The results of this vetting can be seen online\footnote{\datareleaseurl}.
 
@@
 Therefore, alongside this \paper, we publish the full list of injection
-simulations\footnote{SOMEURL} to be used for population inference (occurrence
-rate measurements).
+simulations\footnote{\datareleaseurl} to be used for population inference
+(occurrence rate measurements).
 
@@
 
-The remaining signals are caused by eclipsing binaries (EBs).
+The remaining signals are caused by eclipsing binaries (EBs) with visible
+secondary eclipses.
 In most cases, the search reports the secondary eclipse as a candidate and in
@@
 In \tab{cand} we list the sample quantiles for the observable quantities and
-the full chains are available electronically at \dfmtodo{some URL}.
+the full chains are available electronically\footnote{\datareleaseurl}.
 \fig{candidates} shows the observed distribution of planet candidates in the
@@
 The candidates are listed in \tab{cand} and posterior distributions of planet
-candidate properties are available at \dfmtodo{thisurl}.
+candidate properties are available\footnote{\datareleaseurl}.
 
@@
 
+As a supplement to this \paper, we make all the results, data products, and
+MCMC chains available at \datareleaseurl.
+The \LaTeX\ source for this \paper, complete with the full revision history,
+is available at \url{http://github.com/dfm/k2-paper} and the pipeline
+implementation is available at \url{http://github.com/dfm/ketu} under the MIT
+open-source software license.
+This code and a lot of computation time are all that is needed to reproduce
+the \figurename s in this \paper.
+
 \acknowledgments

### 2015-02-16 ms.tex
words about auto-vetting

@@
 \newcommand{\paper}{\textsl{Article}}
-\newcommand{\papertwo}{\textsl{Paper II}}
 
@@
 This is only the first word and a more complete characterization of our
-catalog's reliability is forthcoming (Montet, Foreman-Mackey, \etal\ in prep).
+catalog's reliability is forthcoming (Montet, Foreman-Mackey, \etal\ in
+preparation).
 
@@
 
-In \papertwo, we will characterize the stars for each of our candidates in
-detail but for now it's worth noting that many of the planet candidates are
-orbiting stars selected for \KT\ as M-type stars.
+In a follow-up to this \paper, we will characterize the stars for each of the
+candidates in detail but for now it's worth noting that many of the planet
+candidates are orbiting stars selected for \KT\ as M-type stars.
 If this rate remains robust after stellar characterization and if these
@@
 can still be executed efficiently---using optimized linear algebra algorithms
-\citep{fastgp}---inside the search loop.
-
-\dfmtodo{
-Most importantly, perhaps, the machine and hand vetting leave much to be desired...
-list some deficiencies of the vetting.
-}
-
-\dfmtodo{
-The completeness and false-positive assessment could be vastly improved...
-completeness estimates are not as extensive as desired;
-there is essentially no estimate of the non-astrophysical false positive rate.
-(There really is no proposal on the table anywhere for getting a false-positive
-rate for the non-astrophysical FPs.)
-}
-
-\dfmtodo{
-We have not attempted to do any kind of populations analysis...
-but presumably \KT\ data will rock this.  In what ways?
-}
+\citep[][Foreman-Mackey et al.\ in preparation]{fastgp}---inside the search
+loop.
+
+A substantial caveat to the reliability of all existing transiting exoplanet
+searches is that they all include human intervention.
+This makes quantifying the false alarm rate of these catalogs complicated.
+There has been some work on automated vetting algorithms using supervised
+classification algorithms \citep{vetting, jenkins} but these methods rely on
+hand classified examples for training and the performance is not yet
+competitive with human classification.
 
@@
 evaluated at the maximum likelihood value ${\bvec{w}_k}^*$.
-
-Remember that the likelihood defined in \eq{depth-likelihood} is a function of
-the parameters \bvec{\theta} (the period, phase, and duration of the planet).
-In principle, this means that a transit search can proceed by building a dense
-3D grid of \bvec{\theta} values and evaluating the likelihood of the data
-$\mathcal{L}_k$ using \eq{depth-likelihood} at each point in the grid.
 

### 2015-02-16 ms.tex
to do comment-done
Difference imaging centroid citation

@@
 in the original \kepler\ mission where this effect was generally measured
-using difference imaging \dfmtodo{(cite)}.
+using difference imaging \citep{Batalha:2010}.
 
@@
 numbers are computed as the 0.16, 0.5, and 0.84 posterior sample quantiles.
-\dfmtodo{RA/Dec coords.}
 \tablabel{cand}}

### 2015-02-16 ms.tex
added batalha2010 citation and text
wording tweak

@@
 of the spacecraft and we can, in fact, model it identically.
-Previously (\eqalt{linear-model}), we modeled the light curve as a linear
+In our analysis, (\eqalt{linear-model}), we model the light curve as a linear
 combination of ELCs and a simple box transit model at a given period, phase,

### 2015-02-16 ms.tex
fpp text changes; some quant added

--- 2015-02-16 ms.tex
@@
 A major problem with any transit search is the potential confusion
-between transiting planets and stellar eclipsing binaries.  Of
+between transiting planets and stellar eclipsing binaries (EBs).  Of
 particular concern are grazing stellar eclipses or stellar eclipses
@@
 false positive rate of only 5-10\% \citep{Morton:2011, Fressin:2013},
-primarily due to two major factors.  First, the superior precision of
-the \kepler\ photometry enables detection of secondary stellar
-eclipses to a much lower level than ground-based surveys; and second,
-the relatively small pixels and stable pointing of the
-\kepler\ telescope has enabled the identification of many spatially
-distinct blended eclipsing binaries by means of detailed pixel-level
-analysis \citep{Bryson:2013}.
-
-Ground-based surveys prior to \kepler\ often had a false-positive rate
-of 30 to 40~percent. \dfmtodo{(because of shit?) Because of giant pixels.
-See references in Morton and Johnson intro, probably}
-In the primary \kepler\ Mission, this number was significantly lower:
-the false positive rate was only 5 to 10~percent \citep{Morton:2011}.
-Such improvement was enabled by the relatively small pixels, stable
-pointing, and high precision of the \kepler\ spacecraft.
-In \kepler\ data, false positives can be reliably separated from
-planet candidates by looking for differences in the position of the
-centroid of light during transit events with respect to the
-out-of-transit data \dfmtodo{(e.g. citation)}, variations in the depth of
-alternating transits \dfmtodo{(e.g. citation)}, and evidence for ellipsoidal
-variations between transits \dfmtodo{(e.g. citation)}.
-
-In \KT, the precision of these tests is lower and they must be applied with
-care.
-There are typically only a handful of transits, meaning differences between
-``odd'' and ``even'' transits must be large to create a significant
-difference.
-Searching for ellipsoidal variations is hindered by the short time baseline
-and the increased photometric uncertainty in \KT\ data.
-Centroid variations are feasible in \KT\ but must be treated differently than
-in the original \kepler\ mission where this effect was generally measured
-using difference imaging \citep{Batalha:2010}.
-
-To obtain an initial assessment of the astrophysical false positive rate in
-our catalog of planet candidates, we test for significant centroid offsets
-using the machinery that we have already established for modeling the
-systematic trends in the data.
-This is only the first word and a more complete characterization of our
-catalog's reliability is forthcoming (Montet, Foreman-Mackey, \etal\ in
-preparation).
+primarily due to three major factors.  First, the superior precision
+of the \kepler\ photometry enables detection of secondary stellar
+eclipses, odd-even transit depth variations, and ellipsoidal
+variations \citep{Batalha:2010} to a much lower level than
+ground-based surveys. Second, the relatively small pixels and stable
+pointing of the \kepler\ telescope has enabled the identification of
+many spatially distinct blended eclipsing binaries by means of
+detailed pixel-level analysis \citep{Bryson:2013} to identify shifts
+in the center of light during transits.  And finally, \kepler\ is
+sensitive to much smaller planets than ground-based surveys, and it
+turns out that small planets are much more common than hot Jupiters.
+
+In \KT, the precision of these tests is lower and they must be applied
+with care.  There are typically only a handful of transits, meaning
+differences between ``odd'' and ``even'' transits must be large to
+create a significant difference. Searching for ellipsoidal variations
+is hindered by the short time baseline and the increased photometric
+uncertainty in \KT\ data.  Centroid variations are feasible in
+\KT\ but must be treated differently than in the original
+\kepler\ mission where this effect was generally measured using
+difference imaging \citep{Batalha:2010}.
+
+To do first-pass vetting for blended EBs among our catalog of
+planetary candidates, we test for significant centroid offsets using
+the machinery that we have already established for modeling the
+systematic trends in the data, inspired by the methods used to vet
+\kepler\ candidates \citep{Bryson:2013}.  This is only an initial vetting step
+and a more complete characterization of our catalog's reliability is
+forthcoming (Montet, Foreman-Mackey, \etal\ in preparation).
 
@@
 In practice, the precision of the centroid measurements isn't sufficient to
-robustly reject many candidates but two candidates---EPIC 201202105 and EPIC
+robustly reject many candidates, but two candidates---EPIC 201202105 and EPIC
 201632708---have offsets large enough that we remove them from our final
 catalog.
+
+A quick \emph{a priori} estimate of the background blended ecipsing
+binary rate serves as a good sanity check.  A query to the TRILEGAL
+(TRIdimensional modeL of thE GALaxy, \citet{Girardi:2005}) galaxy
+line-of-sight simulation software reveals that the typical density of
+field stars along the line of sight to the C1 field is about
+$7.8\times 10^{-4}$\,arcsec$^{-2}$.  This gives a probability of about
+0.16 that a background star might be blended within a 8\,arcsec radius
+(two pixels) from a target star.  Allowing that something close to
+$\sim$10\% of stars might host close binary companions within the
+period range accessible by this survey, this gives a probability of
+0.016 that a blended binary star might be chance-aligned within two
+pixels of any given target star.  Noting that the average number of
+planets per star with periods less than 30 days is about 0.25
+\citep{Fressin:2013}, we can roughly estimate that we expect $<$10\%
+of our candidates to be caused by nearby contaminating EBs.  This
+estimate suggests that such astrophsycial false positives should be
+rare in our sample, consistent with our detection of 2/36 candidates
+with clear centroid offsets.
 

### 2015-02-16 ms.tex
coordinates

--- 2015-02-16 ms.tex
@@
 in the original \kepler\ mission where this effect was generally measured
-using difference imaging \citep{Batalha:2010}.
+using difference imaging \dfmtodo{(cite)}.
 
@@
 of the spacecraft and we can, in fact, model it identically.
-In our analysis, (\eqalt{linear-model}), we model the light curve as a linear
+Previously (\eqalt{linear-model}), we modeled the light curve as a linear
 combination of ELCs and a simple box transit model at a given period, phase,
@@
 numbers are computed as the 0.16, 0.5, and 0.84 posterior sample quantiles.
+The coordinates are retrieved directly from the EPIC.
 \tablabel{cand}}

### 2015-02-16 ms.tex
fpp text in

--- 2015-02-16 ms.tex
@@
 in the center of light during transits.  And finally, \kepler\ is
-sensitive to much smaller planets than ground-based surveys, and it
-turns out that small planets are much more common than hot Jupiters.
-
-In \KT, the precision of these tests is lower and they must be applied
+sensitive to much smaller planets than ground-based surveys, and small
+planets are much more common than the Jupiter-sized planets able to be
+detected from the ground.
+
+In \KT, the precision of the photometric tests used to vet for such
+false positives  is lower and they must be applied
 with care.  There are typically only a handful of transits, meaning
@@
 \kepler\ mission where this effect was generally measured using
-difference imaging \citep{Batalha:2010}.
+difference imaging \citep{Batalha:2010, Bryson:2013}.
 
@@
 0.16 that a background star might be blended within a 8\,arcsec radius
-(two pixels) from a target star.  Allowing that something close to
-$\sim$10\% of stars might host close binary companions within the
-period range accessible by this survey, this gives a probability of
-0.016 that a blended binary star might be chance-aligned within two
-pixels of any given target star.  Noting that the average number of
-planets per star with periods less than 30 days is about 0.25
-\citep{Fressin:2013}, we can roughly estimate that we expect $<$10\%
-of our candidates to be caused by nearby contaminating EBs.  This
-estimate suggests that such astrophsycial false positives should be
-rare in our sample, consistent with our detection of 2/36 candidates
-with clear centroid offsets.
+(two pixels) from a target star.  Allowing that $\sim$10\% of stars
+might host close binary companions within the period range accessible
+by this survey, this gives a probability of 0.016 that a blended
+binary star might be chance-aligned within two pixels of any given
+target star.  Noting that the average number of planets per star with
+periods less than 30 days is about 0.25 \citep{Fressin:2013}, we can
+roughly estimate that we expect $<$10\% of our candidates to be caused
+by nearby contaminating EBs.  This estimate suggests that such
+astrophsycial false positives should be rare in our sample, consistent
+with our detection of 2/36 candidates with clear centroid offsets.
 

### 2015-02-16 ms.tex
kepler team acknowledgement
typos in FP

--- 2015-02-16 ms.tex
@@
 Ground-based transit surveys have experienced false-positive rates
-well over 50\%.  For example, \citet{Latham:2009} reported eight
+well over 50~percent.  For example, \citet{Latham:2009} reported eight
 eclipsing binaries and one transiting planet among the sample of
@@
 
-A quick \emph{a priori} estimate of the background blended ecipsing
+A quick \emph{a priori} estimate of the background blended eclipsing
 binary rate serves as a good sanity check.  A query to the TRILEGAL
@@
 $7.8\times 10^{-4}$\,arcsec$^{-2}$.  This gives a probability of about
-0.16 that a background star might be blended within a 8\,arcsec radius
+0.16 that a background star might be blended within a 8~arcsec radius
 (two pixels) from a target star.  Allowing that something close to
@@
 of our candidates to be caused by nearby contaminating EBs.  This
-estimate suggests that such astrophsycial false positives should be
+estimate suggests that such astrophysical false positives should be
 rare in our sample, consistent with our detection of 2/36 candidates
@@
 
-The remaining signals are caused by eclipsing binaries (EBs) with visible
-secondary eclipses.
+The remaining signals are caused by EBs with visible secondary eclipses.
 In most cases, the search reports the secondary eclipse as a candidate and in

### 2015-02-16 ms.tex
K2 facility

--- 2015-02-16 ms.tex
@@
 by nearby contaminating EBs.  This estimate suggests that such
-astrophsycial false positives should be rare in our sample, consistent
+astrophysical false positives should be rare in our sample, consistent
 with our detection of 2/36 candidates with clear centroid offsets.
@@
 \kepler\ mission is provided by the NASA Science Mission directorate.
+We are grateful to the entire \kepler\ team, past and present.
+Their tireless efforts were all essential to the tremendous success of the mission
+and the successes of \KT, present and future.
 These data were obtained from the Mikulski Archive for Space Telescopes
@@
 
-{\it Facilities:} \facility{Kepler}
+{\it Facilities:} \facility{Kepler}, \facility{K2}
 

### 2015-02-16 ms.tex
K2 is not a AAS-approved facility keyword. We could petition for it to be, but it is not currently. See http://aas.org/aastex/facility-keywords
What else can we use this for?

@@
 
+Additionally, while we apply this systematics model simultaneously with a 
+transiting planet model to search for planet candidates, this scheme is 
+not restricted to planet searches.
+Any astrophysical event that could be observed in the \KT\ data could be 
+searched for in the same way. 
+By modeling a set of ELCs with any arbitrary data model, events in the \KT\
+data that appear similar to that data model could be identified. 
+Such a technique may be useful in searching for astrophysical events such as
+ellipsoidal variations induced by orbiting companions,
+stellar activity,
+microlensing events, especially in the upcoming Campaign 9,
+or
+active galactic nuclei variability.
+
 A substantial caveat to the reliability of all existing transiting exoplanet
@@
 
-{\it Facilities:} \facility{Kepler}, \facility{K2}
+{\it Facilities:} \facility{Kepler}
 

### 2015-02-16 ms.tex
small typo

--- 2015-02-16 ms.tex
@@
 combination of the 150 ELCs but, at this point, we combine this with a
-realistic light curve model \citet{ma, kipping-ld}.
+realistic light curve model \citep{ma, kipping-ld}.
 Even though we have no constraints on the stellar parameters, we also sample
@@
 The flexible systematics model we employ is a 150-parameter linear combination
-of PCA components derived from the full set of 21,703 stellar lightcurves.
+of PCA components derived from the full set of 21,703 stellar light curves.
 That is, it presumes that the systematics afflicting each star are shared in

### 2015-02-16 ms.tex
tdm

--- 2015-02-16 ms.tex
@@
 of the spacecraft \citep{Vanderburg:2014, Aigrain:2015, Crossfield:2015}.
-In our analysis, we don't do any further preprocessing of the light curves
+In our analysis, we do not do any further preprocessing of the light curves
 because, as we describe in the next \sectionname, we fit raw photometric light
@@
 Ground-based transit surveys have experienced false-positive rates
-well over 50~percent.  For example, \citet{Latham:2009} reported eight
+well over 50\%.  For example, \citet{Latham:2009} reported eight
 eclipsing binaries and one transiting planet among the sample of
@@
 
-A quick \emph{a priori} estimate of the background blended eclipsing
+A quick \emph{a priori} estimate of the background blended ecipsing
 binary rate serves as a good sanity check.  A query to the TRILEGAL
@@
 by nearby contaminating EBs.  This estimate suggests that such
-astrophysical false positives should be rare in our sample, consistent
+astrophsycial false positives should be rare in our sample, consistent
 with our detection of 2/36 candidates with clear centroid offsets.
@@
 
-The remaining signals are caused by EBs with visible secondary eclipses.
+The remaining signals are caused by eclipsing binaries (EBs) with visible
+secondary eclipses.
 In most cases, the search reports the secondary eclipse as a candidate and in
@@
 \kepler\ mission is provided by the NASA Science Mission directorate.
-We are grateful to the entire \kepler\ team, past and present.
-Their tireless efforts were all essential to the tremendous success of the mission
-and the successes of \KT, present and future.
 These data were obtained from the Mikulski Archive for Space Telescopes

### 2015-02-16 ms.tex
adding centroid offset figure

--- 2015-02-16 ms.tex
@@
 of the spacecraft \citep{Vanderburg:2014, Aigrain:2015, Crossfield:2015}.
-In our analysis, we do not do any further preprocessing of the light curves
+In our analysis, we don't do any further preprocessing of the light curves
 because, as we describe in the next \sectionname, we fit raw photometric light
@@
 catalog.
+\Fig{offsets} shows the in-transit centroid offset measured for EPIC
+201202105 and compares it to the distribution of out-of-transit offset
+amplitudes.
 
@@
 astrophysical false positives should be rare in our sample, consistent
-with our detection of 2/36 candidates with clear centroid offsets.
+with our detection of only 2 candidates with clear centroid offsets.
 
@@
 \begin{center}
+\includegraphics{figures/offsets.pdf}
+\end{center}
+\caption{%
+The estimated in-transit centroid offset for EPIC 201202105 (green line)
+compared to the distribution of 1000 centroid offests computed for randomly
+assigned phases (black histogram).
+The in-transit measurement is 3-$\sigma$ larger than the median out-of-transit
+offset so it is rejected from the final catalog.
+\figlabel{offsets}}
+\end{figure}
+
+\begin{figure}[p]
+\begin{center}
 \includegraphics{figures/completeness.pdf}

### 2015-02-16 ms.tex
a few more words about offsets

@@
 robustly reject many candidates, but two candidates---EPIC 201202105 and EPIC
-201632708---have offsets large enough that we remove them from our final
-catalog.
-\Fig{offsets} shows the in-transit centroid offset measured for EPIC
-201202105 and compares it to the distribution of out-of-transit offset
+201632708---have offsets 3-$\sigma$ above the median out-of-transit offset
+amplitude so they are removed from the final catalog.
+For example, \Fig{offsets} shows the in-transit centroid offset measured for
+EPIC 201202105 and compares it to the distribution of out-of-transit offset
 amplitudes.

### 2015-02-16 ms.tex
adding tfa citation

@@
 Other data-driven approaches have been developed and applied to the \kepler\
-data \citep[for example,][]{pdc1, pdc2, arc, dun} but they have yet to be
-generalized to \KT.
+data \citep[for example,][]{pdc1, pdc2, arc, dun} and ground-based surveys
+\citep[for example,][]{hat} but they have yet to be generalized to \KT.
 

### 2015-02-16 ms.tex
comments from Ruth

@@
 We apply this method to the full Campaign~1 dataset and report a list of 36
-planet candidates transiting 31 stars, along with a analysis of the pipeline
+planet candidates transiting 31 stars, along with an analysis of the pipeline
 performance and detection efficiency based on artificial signal injections
@@
 as][]{petigura1, petigura2, roberto, dressing}.
-These efforts have been hugely successful especially in the field of exoplanet
-population inference because, thanks to their relative simplicity, the
-efficiency and behavior of these pipelines can be quantified empirically.
+These efforts have been hugely successful, especially in the field of
+exoplanet population inference because, thanks to their relative simplicity,
+the efficiency and behavior of these pipelines can be quantified empirically.
 The work described in this \paper\ is built on many of the same principles as
-the previous projects built for studying \kepler\ data but our main
+the previous projects developed for studying \kepler\ data but our main
 intellectual contribution is a computationally tractable framework for
@@
 excellent.
-If, however, we were to apply this systematics model alone (without a simultaneous fit
-of the exoplanet transit model) to a light curve with
+If, however, we were to apply this systematics model alone (without a
+simultaneous fit of the exoplanet transit model) to a light curve with
 transits, we would be at risk of over-fitting and decreasing the amplitude of
@@
 Gaussian, the likelihood function for the depth under the periodic model can
-also be computed analytically; it is a product of Gaussian which itself is a
+also be computed analytically; it is a product of Gaussians which itself is a
 Gaussian
@@
 \end{eqnarray}
-Note that this result is \emph{marginalized} over the parameters of the
+Note that this result has been \emph{marginalized} over the parameters of the
 systematics model.
@@
 brightness variations can be extremely non-linear.
-Furthermore, because when the pointing is moving fast there is effectively
-a smearing of the point-spread function, there are effects keyed to the
-time derivative of the Euler angles as well.
+Furthermore, because when the pointing is moving fast there is a smearing of
+the point-spread function, there are effects keyed to the time derivative of
+the Euler angles as well.
 The large number (150) of linear coefficients gives the linear model the
@@
 produces corrected light curves.
-For us, a systematics-corrected light curve is not really a thing.
+% For us, a systematics-corrected light curve is not really a thing.
 
@@
 properties.
-\dfmtodo{For example, let's do the Crossfield planets here. The results are
-consistent. Boom.}
 

### 2015-02-16 ms.tex
typo; note on short period planets

@@
 an initial list of 65,109 candidates.
-The vast majority of these signals are not induced by a transiting planet;
+The vast majority of these signals are not induced by a transiting planet:
 there are many false positives.
@@
 (\eqalt{indtran}) breaks down at these short periods.
-Therefore, we discard all signals with periods shorter than 4 days.
+Therefore, we discard all signals with periods shorter than 4 days,
+acknowledging this will cause us to miss some planets \citep{SanchisOjeda14}.
 After these cuts, 741 candidates remain; we examine these signals by hand.

### 2015-02-16 ms.tex
a few typos... ready to submit!

--- 2015-02-16 ms.tex
@@
 To quantify the performance and detection efficiency of our pipeline, we test
-(in \sect{perform}) the recovery and false alarm rate of synthetic transit
+(in \sect{perform}) the recovery of synthetic transit
 signals, spanning a large range of physical parameters, injected into real
@@
 Finally, in \sect{results}, we present a catalog of 36 planet candidates
-orbiting 31 stars in the publicly available \KT\ Campaign~1 dataset.
+orbiting 31 stars from the publicly available \KT\ Campaign~1 dataset.
 
@@
 from MAST\footnote{\url{https://archive.stsci.edu/k2/}}.
-We extract photometry using fixed approximately circular, binary apertures of
+We extract photometry using fixed, approximately circular, binary apertures of
 varying sizes centered on the predicted location of the target star based on
@@
 Instead, we can compute the values on this grid approximately, but at very
-high precision, using a two-step procedure that is much more computationally
-efficient.
+high precision, using a two-step procedure that is much more efficient.
 
@@
 of the spacecraft and we can, in fact, model it identically.
-In our analysis, (\eqalt{linear-model}), we model the light curve as a linear
+In our analysis, we model the light curve as a linear
 combination of ELCs and a simple box transit model at a given period, phase,
-and duration.
+and duration (\eqalt{linear-model}).
 Under this model, the maximum likelihood depth can be computed analytically.
@@
 binary rate serves as a good sanity check.  A query to the TRILEGAL
-(TRIdimensional modeL of thE GALaxy, \citet{Girardi:2005}) galaxy
+\citep[TRIdimensional modeL of thE GALaxy,][]{Girardi:2005} galaxy
 line-of-sight simulation software reveals that the typical density of
-field stars along the line of sight to the C1 field is about
+field stars along the line of sight to the Campaign 1 field is about
 $7.8\times 10^{-4}$\,arcsec$^{-2}$.  This gives a probability of about
@@
 The two candidates transiting EPIC 201367065 were previously published
-\citep{Crossfield:2015} but, to our knowledge, the remaining list is currently
-unpublished.
-The third planet published by \citet{Crossfield:2015} is found as the third
-signal for that target by our pipeline but it falls just below our
-signal-to-noise cut so we left it out of the catalog for consistency.
+\citep{Crossfield:2015} and the third planet in that system is found as the
+third signal by our pipeline but it falls just below the signal-to-noise cut
+so it is left out of the catalog for consistency.
 This suggests that a less conservative cut in signal-to-noise and more
@@
 
+We model the raw aperture photometry as a linear combination of 150 ELCs and
+a transit model.
 Formally, this can be written for the light curve of the $k$-th star as
@@
 \bvec{A} &=& \left (\begin{array}{cccccc}
-    x_{1,1} & x_{2,1} & \cdots & x_{J,1} & 1 & m_\bvec{\theta}(t_1) \\
-    x_{1,2} & x_{2,2} & \cdots & x_{J,2} & 1 & m_\bvec{\theta}(t_2) \\
+    x_{1,1} & x_{2,1} & \cdots & x_{150,1} & 1 & m_\bvec{\theta}(t_1) \\
+    x_{1,2} & x_{2,2} & \cdots & x_{150,2} & 1 & m_\bvec{\theta}(t_2) \\
     && \vdots &&&\\
-    x_{1,N} & x_{2,N} & \cdots & x_{J,N} & 1 & m_\bvec{\theta}(t_N)
+    x_{1,N} & x_{2,N} & \cdots & x_{150,N} & 1 & m_\bvec{\theta}(t_N)
 \end{array}\right )

### 2015-02-16 publish.py

@@ -1,0 +1,44 @@
+#!/usr/bin/env python
+# -*- coding: utf-8 -*-
+
+from __future__ import division, print_function
+import os
+import re
+import shutil
+from datetime import date
+from itertools import imap
+from subprocess import check_call
+
+datestamp = date.today().strftime("%m%d")
+TMPDIR = "fore" + datestamp
+outfn = TMPDIR+".tar"
+tex = open("ms.tex", "r").read()
+
+try:
+    os.makedirs(TMPDIR)
+except os.error:
+    pass
+
+
+def rename(fn):
+    a, b = os.path.split(fn)
+    return os.path.split(a)[1] + "-" + b, fn
+
+
+def find_figures(tex):
+    return re.findall("includegraphics(?:.*?){(.*)}", tex)
+
+
+for a, b in imap(rename, find_figures(tex)):
+    shutil.copyfile(b, os.path.join(TMPDIR, a))
+    tex = tex.replace(b, a)
+
+shutil.copyfile("tab-cand.tex", os.path.join(TMPDIR, "tab-cand.tex"))
+shutil.copyfile("ms.bbl", os.path.join(TMPDIR, "ms.bbl"))
+open(os.path.join(TMPDIR, "ms.tex"), "w").write(tex)
+check_call(" ".join(["cd", TMPDIR+";",
+                     "tar", "-cf", os.path.join("..", outfn), "*"]),
+           shell=True)
+shutil.rmtree(TMPDIR)
+
+print("Wrote file: '{0}'".format(outfn))

### 2015-02-16 ms.tex
removing dupe ref
Defined Caltech Affiliation

@@
                           4 Washington Place, New York, NY, 10003, USA}
-\altaffiltext{\caltech}  {California Institute of Technology, Pasadena, CA,
+\altaffiltext{\caltech}  {Cahill Center for Astronomy and Astrophysics,
+                          California Institute of Technology, Pasadena, CA,
                           91125, USA}
@@
 Therefore, we discard all signals with periods shorter than 4 days,
-acknowledging this will cause us to miss some planets \citep{SanchisOjeda14}.
+acknowledging this will cause us to miss some planets \citep{roberto}.
 After these cuts, 741 candidates remain; we examine these signals by hand.

### 2015-03-10 ms.tex
adding more acknowledgements

@@
 It is a pleasure to thank
+Eric Agol (UW),
 Ruth Angus (Oxford),
-Tom Barclay (Ames), and
+Tom Barclay (Ames),
+Zach Berta-Thompson (MIT),
+G\'eza Kov\'acs (Konkoly Observatory),
+Laura Kreidberg (Chicago),
+Erik Petigura (Berkeley),
+Roberto Sanchis Ojeda (Berkeley),
+and
 Andrew Vanderburg (Harvard)

### 2015-03-15 ms.tex
adding some references and a new figure

@@
 \newcommand{\hoggtodo}[1]{\todo{HOGG}{blue}{#1}}
+
+\definecolor{mygreen}{rgb}{0, 0.50196, 0}
+\newcommand{\response}[1]{{\color{mygreen} {\bf #1}}}
 
@@
 
-The noise floor for \kepler\ data is often quoted as 15 parts per million (ppm) per
-six hours of observations \citep{Gilliland:2011}.
+The noise floor for \kepler\ data is often quoted as 15 parts per million
+(ppm) per six hours of observations \citep{Gilliland:2011}.
 Although they generally do not interfere with searches for transiting
@@
 One of the most serious of these is spacecraft pointing: If the detector
-flat-field is not known with very high accuracy, then tiny changes to the relative
-illumination of pixels caused by a star's motion in the focal plane will lead
-to changes in the measured or inferred brightness of the star.
+flat-field is not known with very high accuracy, then tiny changes to the
+relative illumination of pixels caused by a star's motion in the focal plane
+will lead to changes in the measured or inferred brightness of the star.
 
@@
 exhibit far greater pointing variations---and substantially more
-pointing-induced variations in photometry---than the original \kepler\ Mission data.
+pointing-induced variations in photometry---than the original \kepler\ Mission
+data.
 This makes good data-analysis techniques even more valuable.
@@
 the spacecraft, but is not nearly as accurate as required to make
-pointing-insensitive photometric measurements at the relevant level of precision.
+pointing-insensitive photometric measurements at the relevant level of
+precision.
 In principle direct inference of the flat-field might be possible;
@@
 then ``de-trend'' using the mean prediction from that model.
-Other data-driven approaches have been developed and applied to the \kepler\
-data \citep[for example,][]{pdc1, pdc2, arc, dun} and ground-based surveys
-\citep[for example,][]{hat} but they have yet to be generalized to \KT.
+Other data-driven approaches have been developed and applied to the data from
+space missions \citep[for example,][]{Ofir:2010, Stumpe:2012, Smith:2012,
+Petigura:2013, Wang:2015} and ground-based surveys \citep[for
+example,][]{Kovacs:2005, Tamuz:2005, Berta:2012} but they have yet to be
+generalized to \KT.
 
@@
 
-The alternative to this approach is to \emph{simultaneously fit} both the systematics
-and the transit signals.
-Simultaneous fitting can push the detection limits to lower signal-to-noise while
-robustly accounting for uncertainties about the systematic trends.
+The alternative to this approach is to \emph{simultaneously fit} both the
+systematics and the transit signals.
+Simultaneous fitting can push the detection limits to lower signal-to-noise
+while robustly accounting for uncertainties about the systematic trends.
 In particular, it permits us to \emph{marginalize} over choices in the noise
@@
 to our confidence in the detection.
-This marginalization ensures that any conclusions we come to about the exoplanet
-properties are conservative, given the freedom of the systematics model.
+This marginalization ensures that any conclusions we come to about the
+exoplanet properties are conservative, given the freedom of the systematics
+model.
 
@@
 the dominant modes.
-The search for planets proceeds by modeling the data as a linear combination of
-150 of these basis vectors and a transit model.
+The search for planets proceeds by modeling the data as a linear combination
+of 150 of these basis vectors and a transit model.
 Our method builds on the ideas behind previous data-driven de-trending
 procedures such as the \kepler\ pipeline pre-search data conditioning
-\citep[\pdc;][]{pdc1, pdc2}, but (because of our simultaneous fitting
-approach) we can use a much more flexible systematics model without worrying
-about over-fitting.
+\citep[\pdc;][]{Stumpe:2012, Smith:2012}, but (because of our simultaneous
+fitting approach) we can use a much more flexible systematics model without
+worrying about over-fitting.
 
@@
 They will also deliver input data for next-generation population inferences
-\citep{dfm}, especially for the population of planets around cool stars
-\citep[for example,][]{dressing}.
+\citep{Foreman-Mackey:2014}, especially for the population of planets around
+cool stars \citep[for example,][]{Dressing:2015}.
 
@@
 search algorithms applied to publicly available datasets \citep[such
-as][]{petigura1, petigura2, roberto, dressing}.
+as][]{Petigura:2013a, Petigura:2013, Sanchis-Ojeda:2014, Dressing:2015}.
 These efforts have been hugely successful, especially in the field of
@@
 Following \citet{Vanderburg:2014}, we choose the aperture size with the
-minimum CDPP \citep{cdpp} with a 6 hour window.\footnote{Note that although we
-chose a specific aperture for each star, photometry for every aperture radius
-is available online: \datareleaseurl.}
+minimum CDPP \citep{Christiansen:2012} with a 6 hour window.\footnote{Note
+that although we chose a specific aperture for each star, photometry for every
+aperture radius is available online: \datareleaseurl.}
 
@@
 on a large set of (filtered) light curves and extracting the top few ($\sim 4$)
-components \citep{pdc1, pdc2}.
+components \citep{Stumpe:2012, Smith:2012}.
 Similarly, we ran PCA on the full set of our own generated \KT\ Campaign~1
 light curves to determine a basis of representative trends but, unlike \pdc,
-we retain and use a large number of these components ($150$).
+we retain and use a larger number of these components ($150$).
 For clarity, we will refer to our basis as a set of ``eigen light curves''
@@
 
+\response{Blah blah}
+
+\begin{figure}[p]
+\begin{center}
+\includegraphics{figures/pca.pdf}
+\end{center}
+\caption{%
+The top 10 eigen light curves (ELCs) generated by running principal component
+analysis on all the aperture photometry from Campaign~1.
+\figlabel{pca}}
+\end{figure}
+
 \section{Joint transit \& variability model}
@@
 other standard procedures is that no de-trending is necessary.
-Instead, we can fit for the noise (or trends) and exoplanet signals simultaneously.
+Instead, we can fit for the noise (or trends) and exoplanet signals
+simultaneously.
 This is theoretically appealing because it will be more sensitive to low
 signal-to-noise transits.
-The main reason for this is that the signal is never precisely orthogonal to the
-systematics and any de-trending will over-fit.
-This will, in turn, decrease the amplitude of the
-signal and distort its shape.
-In order to reduce this effect, most procedures use a very rigid model for
-the trends.
-For \KT, this rigidity has been implemented by
-effectively asserting that centroid measurements contain
-all of the information needed to describe the trends \citep{Vanderburg:2014,
-Aigrain:2015, Crossfield:2015}.
+The main reason for this is that the signal is never precisely orthogonal to
+the systematics and any de-trending will over-fit.
+This will, in turn, decrease the amplitude of the signal and distort its
+shape.
+In order to reduce this effect, most procedures use a very rigid model for the
+trends.
+For \KT, this rigidity has been implemented by effectively asserting that
+centroid measurements contain all of the information needed to describe the
+trends \citep{Vanderburg:2014, Aigrain:2015, Crossfield:2015}.
 In the \kepler\ pipeline, this is implemented by allowing only a small number
 of PCA components to contribute to the fit in the \pdc\ procedure.
-Instead, we will use a large number of ELCs---a very flexible model---and
-use a simultaneous fitting and marginalization to avoid over-fitting.
+Instead, we will use a large number of ELCs---a very flexible model---and use
+a simultaneous fitting and marginalization to avoid over-fitting.
 
@@
 other sources of PSF modulation.
-Each of these effects will be imprinted in the light
-curves of many stars with varying amplitudes and signs as a result of the
-varying flat field and PSF.
+Each of these effects will be imprinted in the light curves of many stars with
+varying amplitudes and signs as a result of the varying flat field and PSF.
 Therefore, while it is hard to write down a physical generative model for the
@@
 using only empirical centroids \citep{Vanderburg:2014, Armstrong:2014,
-Aigrain:2015,
-Crossfield:2015}, but our more flexible model should capture a wider range of
-effects, including those related to PSF and temperature.
+Aigrain:2015, Crossfield:2015}, but our more flexible model should capture a
+wider range of effects, including those related to PSF and temperature.
 For example, \Fig{corr} shows the application of our model---with 150
@@
 
-In our pipeline we simultaneously fit for the transit
-signal and the trends using a rigid model for the signal and a relatively
-flexible model for the systematic noise.
+In our pipeline we simultaneously fit for the transit signal and the trends
+using a rigid model for the signal and a relatively flexible model for the
+systematic noise.
 Specifically, we model the light curve as being generated by linear
@@
 depth \emph{marginalizing out the systematics model}.
-The signal-to-noise of this depth measurement can then be used as a quality
-of fit metric or candidate selection scalar.
-This computation is expensive but, as described in the following \sectionname s, it
-is possible to scale the method to a \KT-size dataset.
+The signal-to-noise of this depth measurement can then be used as a quality of
+fit metric or candidate selection scalar.
+This computation is expensive but, as described in the following \sectionname
+s, it is possible to scale the method to a \KT-size dataset.
 
@@
 (computationally expensive) generalization of the ``Box Least Squares''
-\citep[\project{BLS};][]{bls} method to a more sophisticated description of
-the noise and systematics.
+\citep[\project{BLS};][]{Kovacs:2002} method to a more sophisticated
+description of the noise and systematics.
 Therefore, any existing search pipeline based on \project{BLS} could, in
@@
 might be required for computational tractability.
+
+\begin{figure}[p]
+\begin{center}
+\includegraphics{figures/corr.pdf}
+\end{center}
+\caption{%
+A demonstration of the ELC fit to the aperture photometry for EPIC 201374602.
+\emph{Top:} The black points show the aperture photometry and the green line
+is the maximum likelihood linear combination of ELCs.
+The estimated 6-hour precision of the raw photometry is 264 ppm.
+\emph{Bottom:} The points show the residuals of the data away from the ELC
+prediction.
+The 6-hour precision of this light curve is 31 ppm.
+Note that although we show a ``de-trended'' light curve to give a qualitative
+understanding of the model, this is not a product of the analysis.
+In this search for transits, \emph{the data are never de-trended}.
+\figlabel{corr}}
+\end{figure}
+
+\begin{figure}[p]
+\begin{center}
+\includegraphics{figures/performance.pdf}
+\end{center}
+\caption{%
+Performance?
+\figlabel{performance}}
+\end{figure}
 
@@
 The result is a generalization of the \project{BLS} frequency spectrum
-\citep{bls} to a light curve model that includes both a transit and the
+\citep{Kovacs:2002} to a light curve model that includes both a transit and the
 trends.
@@
 Therefore, we discard all signals with periods shorter than 4 days,
-acknowledging this will cause us to miss some planets \citep{roberto}.
+acknowledging this will cause us to miss some planets
+\citep{Sanchis-Ojeda:2014}.
 After these cuts, 741 candidates remain; we examine these signals by hand.
@@
 {\item Draw the number of transiting planets based on the observed
-multiplicity distribution of KOIs \citep{kois}.}
+multiplicity distribution of KOIs \citep{Burke:2014}.}
 {\item Sample---from the distributions listed in
@@
 {\item Based on the chosen physical parameters, simulate the light curve,
-taking limb darkening and integration time into account \citep{ma,
-kipping-int}, and multiply it into the raw aperture photometry.}
+taking limb darkening and integration time into account \citep{Mandel:2002,
+Kipping:2010}, and multiply it into the raw aperture photometry.}
 \end{enumerate}
@@
 curve.
-To do this fit, we use Markov Chain Monte Carlo \citep[MCMC;][]{emcee} to
+To do this fit, we use Markov Chain Monte Carlo
+\citep[MCMC;][]{Foreman-Mackey:2013} to
 sample from the posterior probability for the stellar and planetary
@@
 combination of the 150 ELCs but, at this point, we combine this with a
-realistic light curve model \citep{ma, kipping-ld}.
+realistic light curve model \citep{Mandel:2002, Kipping:2013a}.
 Even though we have no constraints on the stellar parameters, we also sample
@@
 can still be executed efficiently---using optimized linear algebra algorithms
-\citep[][Foreman-Mackey et al.\ in preparation]{fastgp}---inside the search
-loop.
+\citep[][Foreman-Mackey et al.\ in preparation]{Ambikasaran:2014}---inside the
+search loop.
 
@@
 There has been some work on automated vetting algorithms using supervised
-classification algorithms \citep{vetting, jenkins} but these methods rely on
-hand classified examples for training and the performance is not yet
-competitive with human classification.
+classification algorithms \citep{McCauliff:2014, Jenkins:2014} but these
+methods rely on hand classified examples for training and the performance is
+not yet competitive with human classification.
 
@@
 \begin{center}
-\includegraphics{figures/pca.pdf}
-\end{center}
-\caption{%
-The top 10 eigen light curves (ELCs) generated by running principal component
-analysis on all the aperture photometry from Campaign~1.
-\figlabel{pca}}
-\end{figure}
-
-\begin{figure}[p]
-\begin{center}
-\includegraphics{figures/corr.pdf}
-\end{center}
-\caption{%
-A demonstration of the ELC fit to the aperture photometry for EPIC 201374602.
-\emph{Top:} The black points show the aperture photometry and the green line
-is the maximum likelihood linear combination of ELCs.
-The estimated 6-hour precision of the raw photometry is 264 ppm.
-\emph{Bottom:} The points show the residuals of the data away from the ELC
-prediction.
-The 6-hour precision of this light curve is 31 ppm.
-Note that although we show a ``de-trended'' light curve to give a qualitative
-understanding of the model, this is not a product of the analysis.
-In this search for transits, \emph{the data are never de-trended}.
-\figlabel{corr}}
-\end{figure}
-
-\begin{figure}[p]
-\begin{center}
 \includegraphics{figures/linear.pdf}
@@
 EPIC 201613023.
-This is the generalization of the \project{BLS} spectrum \citep{bls} to this
+This is the generalization of the \project{BLS} spectrum \citep{Kovacs:2002} to this
 simultaneous model of the transit and the systematic trends.
@@
 The distribution of physical parameters for the injected signals.
-The eccentricity distribution is based on \citet{kipping-ecc} and the
-limb darkening parameterization is given by \citet{kipping-ld}.
+The eccentricity distribution is based on \citet{Kipping:2013} and the
+limb darkening parameterization is given by \citet{Kipping:2013a}.
 \tablabel{dist}}

### 2015-03-16 ms.tex
adding figure describing overfitting

@@
 This basis of trends was found by running Principal Component Analysis (PCA)
-on a large set of (filtered) light curves and extracting the top few ($\sim 4$)
-components \citep{Stumpe:2012, Smith:2012}.
+on a large set of (filtered) light curves and extracting the top few ($\sim
+4$) components \citep{Stumpe:2012, Smith:2012}.
 Similarly, we ran PCA on the full set of our own generated \KT\ Campaign~1
@@
 The top ten ELCs for Campaign~1 are shown in \Fig{pca}.
-
-\response{Blah blah}
 
@@
 
+\response{%
+The choice to use 150 basis functions is largely arbitrary and we make no
+claims of optimality.
+This value was chosen as a trade-off between the computational cost of the
+search---the cost scales as the third power of the size of the basis---and the
+predictive power of the model.
+In some preliminary experiments, we found that using a larger basis did, as
+expected, lead to a marginally higher sensitivity to small transit signals
+but the gain wasn't sufficient to justify the added cost.
+}
+
 \begin{figure}[p]
@@
 \figlabel{corr}}
-\end{figure}
-
-\begin{figure}[p]
-\begin{center}
-\includegraphics{figures/performance.pdf}
-\end{center}
-\caption{%
-Performance?
-\figlabel{performance}}
 \end{figure}
@@
 
+\begin{figure}[p]
+\begin{center}
+\includegraphics{figures/performance.pdf}
+\end{center}
+\caption{%
+Performance?
+\figlabel{performance}}
+\end{figure}
+
 \section{Results}

### 2015-03-17 ms.tex
moving figures and some responses

@@
 \citep[\pdc;][]{Stumpe:2012, Smith:2012}, but (because of our simultaneous
-fitting approach) we can use a much more flexible systematics model without
-worrying about over-fitting.
+fitting approach) we can use a much more flexible systematics model
+\response{while being less prone to over-fitting}.
 
@@
 
-The key insight in our transit search method that sets it apart from the
-other standard procedures is that no de-trending is necessary.
+The key insight in our transit search method that sets it apart from most
+standard procedures is that no de-trending is necessary.
 Instead, we can fit for the noise (or trends) and exoplanet signals
 simultaneously.
-This is theoretically appealing because it will be more sensitive to low
-signal-to-noise transits.
-The main reason for this is that the signal is never precisely orthogonal to
-the systematics and any de-trending will over-fit.
+This is theoretically appealing because it should be more sensitive to low
+signal-to-noise transits \response{and similar methods have been shown to be
+effective for finding transits in ground-based surveys \citep{Berta:2012}}.
+The main motivation for this model is that the signal is never precisely
+orthogonal to the systematics and any de-trending will over-fit.
 This will, in turn, decrease the amplitude of the signal and distort its
 shape.
-In order to reduce this effect, most procedures use a very rigid model for the
-trends.
+In order to reduce these effects, most de-trending procedures use a very rigid
+model for the systematics.
 For \KT, this rigidity has been implemented by effectively asserting that
@@
 excellent.
-If, however, we were to apply this systematics model alone (without a
-simultaneous fit of the exoplanet transit model) to a light curve with
-transits, we would be at risk of over-fitting and decreasing the amplitude of
-the signal.
+
+If we were to apply this systematics model alone (without a simultaneous fit
+of the exoplanet transit model) to a light curve with transits, we would be at
+risk of over-fitting and decreasing the amplitude of the signal.
+\response{\Fig{overfitting} demonstrates this effect on a synthetic transit
+injected into the light curve of a typical bright star.
+The middle two panels in this Figure show the light curve de-trended using 10
+and 150 ELCs respectively.
+When only 10 ELCs are used, the measured transit depth is relatively robust
+but this model is clearly not sufficient for removing the majority of the
+systematic trends.
+The model with 150 ELCs does an excellent job of removing the systematics but
+it also distorts the transit shape and decreases the measured transit depth,
+hence reducing the signal strength in the \project{BLS} spectrum
+\citep{Kovacs:2002}.}
 
@@
 s, it is possible to scale the method to a \KT-size dataset.
+\response{The bottom panel of \Fig{overfitting} shows the application of this
+joint transit--systematics model to the synthetic transit discussed
+previously.
+When the joint model is used, the correct transit depth is measured---the
+transit is not distorted---but the systematics are also well-described by the
+model.}
 
@@
 \figlabel{corr}}
+\end{figure}
+
+\begin{figure}[p]
+\begin{center}
+\includegraphics[width=0.5\textwidth]{figures/overfitting.pdf}
+\end{center}
+\caption{%
+\response{%
+A comparison between de-trending using different numbers of ELCs and a
+simultaneous fit of the systematics and transit model.
+\emph{(a)} The raw photometry for EPIC 201374602 with a synthetic transit
+injected at 65 days. In all plots, the photometry is measured in
+parts-per-thousand (ppt).
+\emph{(b)} The black points show the photometry de-trended using a linear
+combination of 10 ELCs and the green line shows the true transit model.
+The maximum likelihood transit depth is computed following \project{BLS}
+\citep{Kovacs:2002}.
+While some of the systematics are removed by this model, there is still a lot
+of residual noise.
+\emph{(c)} The same plot as panel \emph{(b)} but using 150 ELCs to de-trend.
+This model removes the majority of the systematics but also distorts the
+transit and weakens the signal; it reduces the measured transit depth.
+\emph{(d)} The final panel shows the results of simultaneously fitting for
+the transit and the systematics using 150 ELCs.
+The maximum likelihood depth is computed as described in \app{math}.
+Like panel \emph{(c)}, this model removes most of the systematics but does
+not distort the transit or reduce the measured transit depth.
+}
+\figlabel{overfitting}}
 \end{figure}
@@
 
+\begin{figure}[p]
+\begin{center}
+\includegraphics{figures/linear.pdf}
+\end{center}
+\caption{%
+The maximum likelihood transit depth as a function of transit time as computed
+in the linear search of the light curve of EPIC 201613023.
+After the periodic search and vetting this target is found to have a planet
+candidate with a period of 8.3~days.
+The first transit occurs at 7.4~days on this plot.
+\figlabel{linear}}
+\end{figure}
+
 \paragraph{Periodic search}
@@
 signal-to-noise transits.
+
+\begin{figure}[p]
+\begin{center}
+\includegraphics{figures/periodic.pdf}
+\end{center}
+\caption{%
+The signal-to-noise spectrum as a function of period for the light curve of
+EPIC 201613023.
+This is the generalization of the \project{BLS} spectrum \citep{Kovacs:2002} to this
+simultaneous model of the transit and the systematic trends.
+To compute this spectrum, the results of the linear search (\fig{linear})
+were used as described in \sect{search}.
+The top peak (at a period of 8.3~days) is indicated with a green dot.
+Iterating the periodic search found no other transit signals above the
+signal-to-noise threshold.
+\figlabel{periodic}}
+\end{figure}
 
@@
 
+\begin{figure}[p]
+\begin{center}
+\includegraphics{figures/de-trended.pdf}
+\end{center}
+\caption{%
+The maximum likelihood ``de-trended'' light curve for EPIC 201613023
+evaluated at the planet candidate's period, phase, duration, and depth.
+The transit times are indicated by the green ticks below the light curve.
+This Figure is only generated for qualitative hand vetting and in the search
+procedure, the model is always marginalized over any choices about the
+systematic trends.
+\figlabel{de-trended}}
+\end{figure}
+
+\begin{figure}[p]
+\begin{center}
+\includegraphics{figures/folded.pdf}
+\end{center}
+\caption{%
+The maximum likelihood prediction for the light curve of EPIC 201613023 (see
+also \fig{de-trended}) folded on the 8.3~day period of this planet candidate.
+The points are color-coded by time and the median \emph{a posteriori} transit
+model is overplotted as a black line.
+\figlabel{folded}}
+\end{figure}
+
 \paragraph{Astrophysical false positives}
@@
 and a more complete characterization of our catalog's reliability is
-forthcoming (Montet, Foreman-Mackey, \etal\ in preparation).
+forthcoming (Montet, \etal\ in preparation).
 
@@
 
+\begin{figure}[p]
+\begin{center}
+\includegraphics[width=0.4\textwidth]{figures/centroid.pdf}
+\includegraphics[width=0.4\textwidth]{figures/centroid-2.pdf}
+\end{center}
+\caption{%
+The centroid motion for EPIC 201613023.
+\emph{Left:} The measured $x$ and $y$ pixel coordinates as a function of time.
+\emph{Right:} The pixel coordinates color-coded by time.
+As identified by \citet{Vanderburg:2014}, the centroid motions fall in a
+slowly time variable locus.
+If the centroid coordinates in transit are inconsistent with the
+out-of-transit motions, the candidate is likely to be an astrophysical false
+positive.
+\figlabel{centroid}}
+\end{figure}
+
+\begin{figure}[p]
+\begin{center}
+\includegraphics{figures/offsets.pdf}
+\end{center}
+\caption{%
+The estimated in-transit centroid offset for EPIC 201202105 (green line)
+compared to the distribution of 1000 centroid offests computed for randomly
+assigned phases (black histogram).
+The in-transit measurement is 3-$\sigma$ larger than the median out-of-transit
+offset so it is rejected from the final catalog.
+\figlabel{offsets}}
+\end{figure}
+
 \section{Performance}
@@
 \begin{center}
+\includegraphics{figures/completeness.pdf}
+\end{center}
+\caption{%
+The detection efficiency of the search procedure as a function of the
+physical transit parameters computed empirically by
+injecting synthetic transit signals into the raw light curves and measuring
+the fraction that are successfully recovered.
+These tests were performed on the entire set of stars so these numbers are
+marginalized over all the stellar properties, including magnitude.
+\figlabel{completeness}}
+\end{figure}
+
+\begin{figure}[p]
+\begin{center}
+\includegraphics{figures/completeness-mag.pdf}
+\end{center}
+\caption{%
+Like \fig{completeness}, the empirically measured detection efficiency of the
+search procedure as a function of stellar magnitude as reported by the EPIC.
+This never reaches 90~percent because these numbers are marginalized over the
+range of physical parameters shown in \fig{completeness}.
+Even for the brightest stars, the long period, small transits cannot be
+detected.
+\figlabel{completeness-mag}}
+\end{figure}
+
+\begin{figure}[p]
+\begin{center}
 \includegraphics{figures/performance.pdf}
@@
 cool stars.
+
+\begin{figure}[p]
+\begin{center}
+\includegraphics{figures/candidates.pdf}
+\end{center}
+\caption{%
+The \emph{a posteriori} distribution of planet candidates in the catalog.
+The error bars indicate the 0.16 and 0.84 posterior sample quantiles for the
+radius ratios.
+\figlabel{candidates}}
+\end{figure}
 
@@
 
-\begin{figure}[p]
-\begin{center}
-\includegraphics{figures/linear.pdf}
-\end{center}
-\caption{%
-The maximum likelihood transit depth as a function of transit time as computed
-in the linear search of the light curve of EPIC 201613023.
-After the periodic search and vetting this target is found to have a planet
-candidate with a period of 8.3~days.
-The first transit occurs at 7.4~days on this plot.
-\figlabel{linear}}
-\end{figure}
-
-\begin{figure}[p]
-\begin{center}
-\includegraphics{figures/periodic.pdf}
-\end{center}
-\caption{%
-The signal-to-noise spectrum as a function of period for the light curve of
-EPIC 201613023.
-This is the generalization of the \project{BLS} spectrum \citep{Kovacs:2002} to this
-simultaneous model of the transit and the systematic trends.
-To compute this spectrum, the results of the linear search (\fig{linear})
-were used as described in \sect{search}.
-The top peak (at a period of 8.3~days) is indicated with a green dot.
-Iterating the periodic search found no other transit signals above the
-signal-to-noise threshold.
-\figlabel{periodic}}
-\end{figure}
-
-\begin{figure}[p]
-\begin{center}
-\includegraphics{figures/de-trended.pdf}
-\end{center}
-\caption{%
-The maximum likelihood ``de-trended'' light curve for EPIC 201613023
-evaluated at the planet candidate's period, phase, duration, and depth.
-The transit times are indicated by the green ticks below the light curve.
-This Figure is only generated for qualitative hand vetting and in the search
-procedure, the model is always marginalized over any choices about the
-systematic trends.
-\figlabel{de-trended}}
-\end{figure}
-
-\begin{figure}[p]
-\begin{center}
-\includegraphics{figures/folded.pdf}
-\end{center}
-\caption{%
-The maximum likelihood prediction for the light curve of EPIC 201613023 (see
-also \fig{de-trended}) folded on the 8.3~day period of this planet candidate.
-The points are color-coded by time and the median \emph{a posteriori} transit
-model is overplotted as a black line.
-\figlabel{folded}}
-\end{figure}
-
-\begin{figure}[p]
-\begin{center}
-\includegraphics[width=0.4\textwidth]{figures/centroid.pdf}
-\includegraphics[width=0.4\textwidth]{figures/centroid-2.pdf}
-\end{center}
-\caption{%
-The centroid motion for EPIC 201613023.
-\emph{Left:} The measured $x$ and $y$ pixel coordinates as a function of time.
-\emph{Right:} The pixel coordinates color-coded by time.
-As identified by \citet{Vanderburg:2014}, the centroid motions fall in a
-slowly time variable locus.
-If the centroid coordinates in transit are inconsistent with the
-out-of-transit motions, the candidate is likely to be an astrophysical false
-positive.
-\figlabel{centroid}}
-\end{figure}
-
-\begin{figure}[p]
-\begin{center}
-\includegraphics{figures/offsets.pdf}
-\end{center}
-\caption{%
-The estimated in-transit centroid offset for EPIC 201202105 (green line)
-compared to the distribution of 1000 centroid offests computed for randomly
-assigned phases (black histogram).
-The in-transit measurement is 3-$\sigma$ larger than the median out-of-transit
-offset so it is rejected from the final catalog.
-\figlabel{offsets}}
-\end{figure}
-
-\begin{figure}[p]
-\begin{center}
-\includegraphics{figures/completeness.pdf}
-\end{center}
-\caption{%
-The detection efficiency of the search procedure as a function of the
-physical transit parameters computed empirically by
-injecting synthetic transit signals into the raw light curves and measuring
-the fraction that are successfully recovered.
-These tests were performed on the entire set of stars so these numbers are
-marginalized over all the stellar properties, including magnitude.
-\figlabel{completeness}}
-\end{figure}
-
-\begin{figure}[p]
-\begin{center}
-\includegraphics{figures/completeness-mag.pdf}
-\end{center}
-\caption{%
-Like \fig{completeness}, the empirically measured detection efficiency of the
-search procedure as a function of stellar magnitude as reported by the EPIC.
-This never reaches 90~percent because these numbers are marginalized over the
-range of physical parameters shown in \fig{completeness}.
-Even for the brightest stars, the long period, small transits cannot be
-detected.
-\figlabel{completeness-mag}}
-\end{figure}
-
-\begin{figure}[p]
-\begin{center}
-\includegraphics{figures/candidates.pdf}
-\end{center}
-\caption{%
-The \emph{a posteriori} distribution of planet candidates in the catalog.
-The error bars indicate the 0.16 and 0.84 posterior sample quantiles for the
-radius ratios.
-\figlabel{candidates}}
-\end{figure}
-
 \clearpage

### 2015-03-17 ms.tex
fixing #27

@@
 \newcommand{\BIC}{{\ensuremath{\mathrm{BIC}}}}
-\newcommand{\TIC}{{\ensuremath{\mathrm{TIC}}}}
 \newcommand{\T}{\ensuremath{\mathrm{T}}}
@@
 To emphasize that $K$ and $N$ are tuning parameters of the method, we
-rewrite the BIC as something that we'll call the ``TIC''
+rewrite this equation as
 \begin{eqnarray}
-\TIC &=&
+-\frac{1}{2}\,\BIC &=&
     \ln p(\{\flux\}_n\,|\,\period,\,\phase,\,\duration) -
@@
 over \phase\ and \duration\ subject to the constraint that
-$\TIC_\mathrm{const} > \TIC_\mathrm{var}$ and requiring that the signal have
+$\BIC_\mathrm{const} < \BIC_\mathrm{var}$ and requiring that the signal have
 at least two observed transits.
@@
 candidate by comparing the peak height to a robust estimate of variance in
-\TIC\ values across period.
+\BIC\ values across period.
 This is not the same criterion used to select the initial three peaks but we
@@
 Zach Berta-Thompson (MIT),
+Daniel Bramich (QEERI, Qatar),
 G\'eza Kov\'acs (Konkoly Observatory),

### 2015-03-17 ms.tex
a bit more responding...

@@
 Specifically, we must evaluate the likelihood function for the light curve of
-star $n$ given a period \period, reference transit time \phase, and duration
-\duration
+star $n$ given a period \period, reference transit time \phase, duration
+\duration, \response{and depth \depth}
 \begin{eqnarray}\eqlabel{full-likelihood}
@@
 where $\transittime_m(\period,\,\phase)$ is the time of the $m$-th
-transit given the period $\period$ and reference time $\phase$.
+transit given the period $\period$ and reference time $\phase$, and
+\response{$M(\period,\,\phase)$ is the total number of transits in the dataset
+for the given \period\ and \phase}.
 \Eq{indtran} can be efficiently computed for many periods and phases if we
@@
 \end{eqnarray}
-Then, we can use these results as a look-up table to approximately evaluate
-the full likelihood in
-\eq{full-likelihood}.
-
-In the remainder of this \sectionname, we give more details about each step of the
-search procedure.
+Then, we can use these results as a look-up table\response{---with
+nearest-neighbor interpolation---}to approximately evaluate the full
+likelihood in \eq{full-likelihood}.
+
+In the remainder of this \sectionname, we give more details about each step of
+the search procedure.
 In summary, it breaks into three main steps: linear
@@
 
-In the period search step, we use the lookup table generated by the linear
-search to compute the likelihood from \eq{indtran} on a three dimensional
-grid in period \period, reference time \phase, and duration \duration.
-At each point, we compute the likelihood of a model where the transit depth
-varies between transits and the ``correct'' simpler model where the transit
-depth is constant.
+\response{%
+In the period search step, the table of likelihood functions generated in the
+linear search step are used to compute the likelihood of the periodic model
+(\eqalt{indtran}) on a three dimensional grid in period \period, reference
+time \phase, and duration \duration.
+At each point in this grid, the likelihood function for each transit depth is
+chosen as the nearest point calculated in the linear search.
+If the time spacing of the linear search is sufficiently fine, this will give
+a good approximation of the correct periodic likelihood.}
+For each periodic model, we compute the likelihood of a model where the
+transit depth varies between transits and the ``correct'' simpler model where
+the transit depth is constant.
 The variable depth likelihood is given by the product of amplitudes from the
@@
 The result is a generalization of the \project{BLS} frequency spectrum
-\citep{Kovacs:2002} to a light curve model that includes both a transit and the
-trends.
+\citep{Kovacs:2002} to a light curve model that includes both a transit and
+the trends.
 For example, \fig{periodic} shows the spectrum for a planet candidate
@@
 EPIC 201613023.
-This is the generalization of the \project{BLS} spectrum \citep{Kovacs:2002} to this
-simultaneous model of the transit and the systematic trends.
+This is the generalization of the \project{BLS} spectrum \citep{Kovacs:2002}
+to this simultaneous model of the transit and the systematic trends.
 To compute this spectrum, the results of the linear search (\fig{linear})
@@
 
+\response{%
+While we argue that the most relevant quantity to use to quantify the
+performance of a transit search pipeline is the efficiency with which it
+discovers transits, it is also useful to consider some other standard metrics.
+In particular, while de-trended light curves are never used at any stage of
+the analysis, our method does make a prediction for the systematics model and
+we can measure the relative precision of the residuals away from this model.
+These residuals are what would be used as de-trended light curves if that was
+the goal.
+\Fig{performance} shows, as a function of the \kepler\ magnitude reported in
+the EPIC, the 6-hour CDPP \citep{Christiansen:2012} for each light curve after
+subtracting the best fit linear combination of 150 ELCs.
+}
+
 \begin{figure}[p]
@@
 \caption{%
-Performance?
+\response{%
+The 6-hour CDPP \citep{Christiansen:2012} for each light curve in Campaign 1
+after subtracting the best fit linear combination of 150 ELCs.
+For each star, the precision is plotted as a function of the \kepler\
+magnitude reported in the EPIC.
+The ``outliers'' in the bottom right corner of the plot are caused by a
+bright star within the photometric aperture and the points in the top left
+corner of the plot are variable stars where the major trends in the light
+curve are not caused by systematic effects, making the ELC model a bad fit.}
 \figlabel{performance}}

### 2015-04-15 ms.tex
added citation to Desert (2015)

@@
 ground-based surveys, the primary \kepler\ Mission saw a much lower
-false positive rate of only 5-10\% \citep{Morton:2011, Fressin:2013},
+false positive rate of only 5-10\% \citep{Morton:2011, Fressin:2013,
+Desert:2015},
 primarily due to three major factors.  First, the superior precision

### 2015-04-19 ms.tex
adding response to referee
addressing #29
a few words in the discussion

@@
 choose a threshold of 15.
+\response{In absolute value, this threshold is somewhat higher than the
+standard signal-to-noise threshold used when searching for transits in the
+\kepler\ light curves \citep[for example][]{Petigura:2013} but given the
+larger amplitude of the systematic noise in the \KT\ light curves, it is not
+surprising that a higher threshold is required to produce a manageable list of
+candidates for hand vetting.
+That being said, it is likely that a reduction in this threshold would yield
+more discoveries at the cost of a larger set of hand classifications.}
+
 We also find that the signals with periods $\lesssim 4$ days are strongly
@@
 That is, it presumes that the systematics afflicting each star are shared in
-some way across other stars.
-It is our belief---although not a strict assumption of our model---that these
+some way across other stars \response{while the astrophysical signals are
+causally unconnected}.
+\response{This assumption means that, while there is no formal guarantee that
+the basis contains no astrophysical signals, it is unlikely that the top
+components will be contaminated.}
+It is our belief---although not a strict assumption of our model---that the
 systematics are caused primarily by pointing drifts, or movements of the
@@
 \begin{center}
-\small
+\footnotesize
 \include{tab-cand}

### 2015-04-19 ms.tex
finishing response to referee

@@
 three-dimensional grid of periodic signals.
-Then, we run a peak detection algorithm on this grid that discards signals
-with substantially varying transit depths.
+Then, we run a peak detection algorithm on this grid \response{that is robust
+to signals with substantially varying transit depths}.
 These transit candidates are then passed along for machine and human {\bf
@@
 for helpful contributions to the ideas and code presented here.
+We also thank the anonymous referee for comments that improved the
+manuscript.
 DFM, DWH, and DW were partially supported by the National Science Foundation

### 2015-04-20 ms.tex
added santerne citation

@@
 ground-based surveys, the primary \kepler\ Mission saw a much lower
-false positive rate of only 5-10\% \citep{Morton:2011, Fressin:2013,
-Desert:2015},
+false positive rate of only 5-10\% \citep{Morton:2011, Fressin:2013},
 primarily due to three major factors.  First, the superior precision
@@
 planets are much more common than the Jupiter-sized planets able to be
-detected from the ground.
+detected from the ground.  We note that while \citet{Santerne:2012} reported
+a $\sim$35\% observational false positive rate, that study was exclusively 
+focused on short-period, large candidates, among which false positives
+are expected to be more likely.  \citet{Desert:2015} has observationally confirmed 
+a low false positive rate for the majority of \kepler\ candidate parameter
+space.
 

### 2015-04-22 ms.tex
nothing

@@
 planets are much more common than the Jupiter-sized planets able to be
-detected from the ground.  We note that while \citet{Santerne:2012} reported
-a $\sim$35\% observational false positive rate, that study was exclusively 
-focused on short-period, large candidates, among which false positives
-are expected to be more likely.  \citet{Desert:2015} has observationally confirmed 
-a low false positive rate for the majority of \kepler\ candidate parameter
-space.
+detected from the ground.
+\response{We note that while \citet{Santerne:2012} reported a $\sim$35\%
+observational false positive rate, that study was exclusively focused on
+short-period, large candidates, among which false positives are expected to be
+more likely.
+\citet{Desert:2015} has observationally confirmed a low false positive rate
+for the majority of \kepler\ candidate parameter space.}
 
@@
 microlensing events, especially in the upcoming Campaign 9,
-or
-active galactic nuclei variability.
+or active galactic nuclei variability.
 

### 2015-05-01 ms.tex
comments from scholkopf

@@
 % Notation for this paper.
-\newcommand{\flux}{{\ensuremath{f}}}
-\newcommand{\ferr}{{\ensuremath{\sigma_\flux}}}
+\newcommand{\flux}{{\ensuremath{\bvec{f}}}}
+\newcommand{\ferr}{{\ensuremath{\sigma_f}}}
 \newcommand{\attime}{{\ensuremath{t}}}
@@
                           Princeton, NJ, 08544, USA}
-\altaffiltext{\mpis}     {Max Planck Institute for Intelligent Systems
+\altaffiltext{\mpis}     {Max Planck Institute for Intelligent Systems,
                           Spemannstrasse 38, 72076 T\"ubingen, Germany}
@@
 the focal plane.
+For a rigorous theoretical analysis of this problem, see Sch\"olkpf
+\etal\ (ICML, in press).
 To capitalize on this, the \pdc\ component of the \kepler\ pipeline
@@
 For example, \Fig{corr} shows the application of our model---with 150
-ELCs---to a light curve with no known transit signals and the precision is
-excellent.
+ELCs---to a light curve with no known transit signals and the photometric
+precision is excellent.
 
@@
 function---conditioned on a specific period, phase, and duration---for the
-depth \emph{marginalizing out the systematics model}.
+depth \emph{marginalizing out the parameters of the systematics model}.
 The signal-to-noise of this depth measurement can then be used as a quality of
@@
 \caption{%
-A demonstration of the ELC fit to the aperture photometry for EPIC 201374602.
+A demonstration of the eigen light curve (ELC) fit to the aperture photometry
+for EPIC 201374602.
 \emph{Top:} The black points show the aperture photometry and the green line
@@
 understanding of the model, this is not a product of the analysis.
-In this search for transits, \emph{the data are never de-trended}.
+In this search for transits, \emph{the data are only de-trended for the
+purpose of visualization}.
 \figlabel{corr}}
@@
 \emph{(a)} The raw photometry for EPIC 201374602 with a synthetic transit
-injected at 65 days. In all plots, the photometry is measured in
-parts-per-thousand (ppt).
+injected at 65 days.
+% In all plots, the photometry is measured in parts-per-thousand (ppt).
 \emph{(b)} The black points show the photometry de-trended using a linear
 combination of 10 ELCs and the green line shows the true transit model.
-The maximum likelihood transit depth is computed following \project{BLS}
-\citep{Kovacs:2002}.
+In this panel and the next, the maximum likelihood transit depth is computed
+following \project{BLS} \citep{Kovacs:2002}.
 While some of the systematics are removed by this model, there is still a lot
@@
 the transit and the systematics using 150 ELCs.
-The maximum likelihood depth is computed as described in \app{math}.
+The maximum likelihood depth (marginalized over the ELC weights) is computed
+as described in \app{math}.
 Like panel \emph{(c)}, this model removes most of the systematics but does
@@
 
-Specifically, we must evaluate the likelihood function for the light curve of
-star $n$ given a period \period, reference transit time \phase, duration
-\duration, \response{and depth \depth}
+Specifically, we must evaluate the likelihood function for the light curve
+$\flux_n$ of star $n$ given a period \period, reference transit time \phase,
+duration \duration, \response{and depth \depth}
 \begin{eqnarray}\eqlabel{full-likelihood}
-p(\{\flux\}_n\,|\,\period,\,\phase,\,\duration,\,\depth) \quad.
+p(\flux_n\,|\,\period,\,\phase,\,\duration,\,\depth) \quad.
 \end{eqnarray}
@@
 \begin{eqnarray}\eqlabel{indtran}
-p(\{\flux\}_n\,|\,\period,\,\phase,\,\duration,\,\depth) &=&
+p(\flux_n\,|\,\period,\,\phase,\,\duration,\,\depth) &=&
 \prod_{m=1}^{M(\period,\,\phase)}
-    p(\{\flux\}_n\,|\,\transittime_m(\period,\,\phase),\,\duration,\,
+    p(\flux_n\,|\,\transittime_m(\period,\,\phase),\,\duration,\,
                     \depth)
@@
 \begin{eqnarray}\eqlabel{singletransit}
-\left \{ p(\{\flux\}_n\,|\,\transittime_l,\,\duration_k,\,\depth)
+\left \{ p(\flux_n\,|\,\transittime_l,\,\duration_k,\,\depth)
 \right\}_{l=1,\,k=1}^{L,\,K} \quad.
@@
 and duration.
-Since the model is linear, the likelihood function for the depth (marginalized
-over the model of the systematics) is a Gaussian with analytic amplitude $L$,
-mean $\bar{\depth}$, and variance $\delta\bar{\depth}^2$, all derived and given in
-\app{math}.
+Since the model is linear and the uncertainties are assumed Gaussian, the
+likelihood function for the depth (marginalized over the model of the
+systematics) is a Gaussian with analytic amplitude $L$, mean $\bar{\depth}$,
+and variance $\delta\bar{\depth}^2$, all derived and given in \app{math}.
 In the linear search, we save these three numbers on a
@@
 At each point in this grid, the likelihood function for each transit depth is
-chosen as the nearest point calculated in the linear search.
+chosen as the nearest point (without interpolation) calculated in the linear
+search.
 If the time spacing of the linear search is sufficiently fine, this will give
@@
 \begin{eqnarray}
-p_\mathrm{var}(\{\flux\}_n\,|\,\period,\,\phase,\,\duration) &=&
+p_\mathrm{var}(\flux_n\,|\,\period,\,\phase,\,\duration) &=&
 \prod_{m=1}^{M(\period,\,\phase)} L_m \quad.
@@
 \begin{eqnarray}
-p_\mathrm{const}(\{\flux\}_n\,|\,\period,\,\phase,\,\duration) &=&
+p_\mathrm{const}(\flux_n\,|\,\period,\,\phase,\,\duration) &=&
 \prod_{m=1}^{M(\period,\,\phase)}
@@
 -\frac{1}{2}\,\BIC &=&
-    \ln p(\{\flux\}_n\,|\,\period,\,\phase,\,\duration)
+    \ln p(\flux_n\,|\,\period,\,\phase,\,\duration)
     - \frac{K}{2} \ln N
@@
 -\frac{1}{2}\,\BIC &=&
-    \ln p(\{\flux\}_n\,|\,\period,\,\phase,\,\duration) -
+    \ln p(\flux_n\,|\,\period,\,\phase,\,\duration) -
         \frac{J\,\alpha}{2}
@@
 systematic trends in the data, inspired by the methods used to vet
-\kepler\ candidates \citep{Bryson:2013}.  This is only an initial vetting step
-and a more complete characterization of our catalog's reliability is
-forthcoming (Montet, \etal\ in preparation).
+\kepler\ candidates \citep{Bryson:2013}.
+If any of the candidates have substantial centroid offsets in phase with their
+transits, this indicates that the signal is likely caused by a background or
+foreground transit of an eclipsing binary and we, therefore, remove it from
+the final candidate list.
+This is only an initial vetting step and a more complete characterization of
+our catalog's reliability is forthcoming (Montet, \etal\ in preparation).
 
@@
 reference transit time within 6~hours of the injected signal, we count that
-injection as recovered.
+injection as necovered.
 The detection efficiency of the search is given approximately by the fraction
@@
 fraction of recovered signals as a function of the physical parameters of the
-injection and the magnitude of the star in the \kepler\ bandpass as reported
+injection, and the magnitude of the star in the \kepler\ bandpass as reported
 in the Ecliptic Plane Input Catalog
@@
 Like \fig{completeness}, the empirically measured detection efficiency of the
-search procedure as a function of stellar magnitude as reported by the EPIC.
+search procedure as a function of stellar magnitude as reported by the
+Ecliptic Plane Input Catalog.
 This never reaches 90~percent because these numbers are marginalized over the
@@
 For each star, the precision is plotted as a function of the \kepler\
-magnitude reported in the EPIC.
+magnitude reported in the Ecliptic Plane Input Catalog.
 The ``outliers'' in the bottom right corner of the plot are caused by a
@@
 some way across other stars \response{while the astrophysical signals are
-causally unconnected}.
+causally unconnected (Sch\"olkopf \etal\ ICML in press)}.
 \response{This assumption means that, while there is no formal guarantee that
@@
 angles---not 150 amplitudes.
-However, because (as the pointing drifts) each star sees it's own unique
+However, because (as the pointing drifts) each star sees its own unique
 local patch of flat-field variations, the mapping from pointing drifts to
@@
 \end{eqnarray}
-is the list aperture fluxes for star $k$ observed at $N$ times
+is the list of aperture fluxes for star $k$ observed at $N$ times
 \begin{eqnarray}
